---
title: "BaselineCharacteristics"
author: "LJS"
date: "2025-05-12"
output: html_document
---


#Libraries 

```{r setup, include=FALSE}

library("rlang") #toolbox
library("readr") #toolbox
library("dplyr") #data manipulation
library("here") #toolbox
library("tidyverse") #data manipulation
library("tidytext") #data manipulation
library("knitr") #rmarkdown
library("htmltools") #rmarkdown
library("markdown") #rmarkdown
library("httpuv") #rmarkdown
library("NCmisc") #toolbox
library("stringr") #data manipulation
library("vtable") #summary tables
library("gtsummary") #summary tables

```


# Face Responses in Childhood (FRIC) project

This script reports demographic and motion characteristics of final sample.

Structure:
- Section I: Read and tidy up data
- Section II: Demographic characteristics
- Section III: Correlation between motion and age


## Section I: Read and tidy up data

```{r}

# Covariates

participants <- read_tsv(here("raw_data/covariates", "participants.tsv"), col_names=TRUE)
colnames(participants)[which(names(participants) == "participant_id")] <- "ID"

## Remove the word "pixar" and trim extra whitespace

participants$ID <- gsub("[sub-pixar-]","", participants$ID)
participants$ID <- trimws(participants$ID)

## Create child or adult lists

adult_list <- row.names(participants)[which(participants[["Child_Adult"]] == "adult")]
child_MRIvariables <- read_csv(here("processed_data", "child_MRIvariables.csv"), col_names=TRUE)
child_list <- child_MRIvariables$ID
participants_list <- c(adult_list, child_list)

## Final sample

participants_filtered <- participants %>%
  filter(ID %in% participants_list)

# Add motion to final sample covariates

motion <- read_tsv(here("raw_data/motion", "outlier_info.tsv"), col_names=TRUE)
colnames(motion)[which(names(motion) == "subject")] <- "ID"

## Remove the word "pixar" and trim extra whitespace

motion$ID <- gsub("[sub-pixar-]","", motion$ID)
motion$ID <- trimws(motion$ID)
participants_filtered <- merge(participants_filtered, motion, by="ID")

# Ensure variables are treated as numeric

participants_filtered$ID <- as.factor(participants_filtered$ID)
participants_filtered$Age <- as.numeric(participants_filtered$Age)
participants_filtered$MeanFD <- as.numeric(participants_filtered$MeanFD)
participants_filtered$Gender <- as.factor(participants_filtered$Gender)

```


## Section II: Demographic characteristics

### General sample

#### Number of participants per age group

```{r}

# Create a frequency table for the 'AgeGroup' column

age_group_frequency <- table(participants_filtered$AgeGroup)

# Print the frequency table

print(age_group_frequency)

```

#### Check data distribution for reporting

```{r}

shapiro.test(participants_filtered$Age)
hist(participants_filtered$Age) 
shapiro.test(participants_filtered$MeanFD)
hist(participants_filtered$MeanFD) 

```

#### Create table

```{r}

targetdata <- participants_filtered[,c(2,4,5,24)]
table_dem <- tbl_summary(
  data      = targetdata,
  by        = Child_Adult,
  statistic = list(
    c("Age", "MeanFD") ~ "{mean} ({sd}); {median} ({min}, {max})"
  ),
  digits    = all_continuous() ~ 3,
  missing   = "no",               # hide missing row entirely
  include   = everything()
)
table_dem

```

#### Correlation between motion and age

```{r}

children_filtered <- participants_filtered %>%
  filter(ID %in% child_list)
cor_result <- cor.test(children_filtered$Age, children_filtered$MeanFD, method = "spearman", use = "complete.obs")
n <- sum(complete.cases(children_filtered$Age, children_filtered$MeanFD))
rho <- round(cor_result$estimate, 2)
p <- if (cor_result$p.value < 0.001) {
  format(cor_result$p.value, scientific = TRUE, digits = 4)
} else {
  sprintf("%.3f", cor_result$p.value)
}

df <- n - 2

```

##### Create footnote text, add and save table

```{r}

# Convert gtsummary table to tibble

table_dem <- as_tibble(table_dem)
colnames(table_dem) <- c(
  "Characteristic",
  "Adults (N=33)",
  "Children (N=117)"
)

# Add footnote as final row

table_dem <- bind_rows(
  table_dem,
  tibble(
    Characteristic = footnote_text,
    `Adults (N=33)` = NA,
    `Children (N=117)` = NA
  )
)

# Save
write.csv(
  table_dem,
  here("results/demographics", "Sample_characteristics.csv"),
  row.names = FALSE
)

```

### Lateralisation analyses samples

#### p<0.05

##### Tidy up data

```{r}

children_filtered <- participants_filtered %>%
  filter(ID %in% child_list) %>%
  left_join(
    child_MRIvariables %>%
      select(ID, lateralisation_index_0.05 = colnames(child_MRIvariables)[230]),
    by = "ID"
  ) %>%
  filter(!is.na(lateralisation_index_0.05))

```

##### Create table

```{r}

targetdata <- children_filtered[,c(2,5,24)]
table_dem <- tbl_summary(
  data      = targetdata,
  statistic = list(
    c("Age", "MeanFD") ~ "{mean} ({sd}); {median} ({min}, {max})"
  ),
  digits    = all_continuous() ~ 3,
  missing   = "no",               # hide missing row entirely
  include   = everything()
)
table_dem

```

##### Save table

```{r}

table_dem <- as_tibble(table_dem)
write.csv(table_dem, here("results/demographics", "Sample_characteristics_LI_0.05.csv"), row.names=FALSE)

```

#### p<0.10

##### Tidy up data

```{r}

children_filtered <- participants_filtered %>%
  filter(ID %in% child_list) %>%
  left_join(
    child_MRIvariables %>%
      select(ID, lateralisation_index_0.10 = colnames(child_MRIvariables)[231]),
    by = "ID"
  ) %>%
  filter(!is.na(lateralisation_index_0.10))

```

##### Create table

```{r}

targetdata <- children_filtered[,c(2,5,24)]
table_dem <- tbl_summary(
  data      = targetdata,
  statistic = list(
    c("Age", "MeanFD") ~ "{mean} ({sd}); {median} ({min}, {max})"
  ),
  digits    = all_continuous() ~ 3,
  missing   = "no",               # hide missing row entirely
  include   = everything()
)
table_dem

```

##### Save table

```{r}

table_dem <- as_tibble(table_dem)
write.csv(table_dem, here("results/demographics", "Sample_characteristics_LI_0.10.csv"), row.names=FALSE)

```


```{r}

markdownToHTML("FRIC_BaselineCharacteristics.Rmd",output ="FRIC_BaselineCharacteristics.html")

```

