---
title: "FRIC_DevelopmentalChange"
author: "LJS"
date: "2025-01-14"
output: html_document
---


# Libraries 

```{r setup, include=FALSE}

library("rlang") #toolbox
library("readr") #toolbox
library("dplyr") #data manipulation
library("purrr") #data manipulation
library("tidyr") #data manipulation
library("here") #toolbox
library("tidyverse") #data manipulation
library("ggpubr") #plotting
library("tidytext") #data manipulation
library("knitr") #rmarkdown
library("htmltools") #rmarkdown
library("markdown") #rmarkdown
library("httpuv") #rmarkdown
library("NCmisc") #toolbox
library("stringr") #data manipulation
library("reshape") #data manipulation
library("reshape2") #data manipulation
library("lme4") #regression models
library("lmerTest") #regression models
library("broom.mixed") #save regression results
library("car") #VIF
library("VIM") #visualise missing data
library("gridExtra") #combine plots
library("patchwork") #combine plots

```


# Face Responses in Childhood (FRIC) project

This script characterises age-related changes in functional maturity, response magnitude to face/scene events and functional connectivity of FFA, MMPFC, STS and amygdala, as well as age-related changes in lateralisation of face response in FFA.

Structure:
- Section I: Functional maturity measure (fm) i.e., similarity between children’s and adults’ timecourses’
- Section II: Magnitude of responses of each ROI at face/scene events
- Section III: Age effects on functional connectivity (fx) between regions
- Section IV: Age effects on lateralisation of face response (non-preregistered)


## Section I: Functional maturity measure (fm) i.e., similarity between children’s and adults’ timecourses’

### Read and tidy up data

```{r}

# Covariates

participants <- read_tsv(here("raw_data/covariates", "participants.tsv"), col_names=TRUE)
colnames(participants)[which(names(participants) == "participant_id")] <- "ID"

## Remove the word "pixar" and trim extra whitespace

participants$ID <- gsub("[sub-pixar-]","", participants$ID)
participants$ID <- trimws(participants$ID)

# Motion

motion <- read_tsv(here("raw_data/motion", "outlier_info.tsv"), col_names=TRUE)
colnames(motion)[which(names(motion) == "subject")] <- "ID"

## Remove the word "pixar" and trim extra whitespace

motion$ID <- gsub("[sub-pixar-]","", motion$ID)
motion$ID <- trimws(motion$ID)

# Fm

child_fm <- read_csv(here("processed_data", "child_MRIvariables.csv"), col_names=TRUE)
child_fm <- child_fm[,c(1:9)]

## Reshape the dataset to long format

long_data <- child_fm %>%
  pivot_longer(cols = starts_with("zscored_fm_"), 
               names_to = c("hemisphere", "region"), 
               names_pattern = "zscored_fm_(l|r)(.*)",  # Capture hemisphere and region
               values_to = "fm") %>%
  mutate(hemisphere = ifelse(hemisphere == "l", "left", "right"))  # Convert l/r to left/right

# Merge age, motion and fm data

fm_data <- merge(long_data, participants[,c(1:2)], by="ID")
fm_data <- merge(fm_data, motion[,c(4,6)], by="ID")
colnames(fm_data) <- c("ID", "hemisphere", "region", "fm", "age", "meanFD")

# Ensure categorical variables are treated as factors

fm_data$ID <- as.factor(fm_data$ID)
fm_data$hemisphere <- as.factor(fm_data$hemisphere)
fm_data$region <- as.factor(fm_data$region)

# Scale predictors

fm_data[, c("age", "meanFD")] <- scale(fm_data[, c("age", "meanFD")])

```

### Models

With interaction effects

```{r}

# FFA

fm_data_FFA <- subset(fm_data, region == "FFA")
model_FFA <- lmer(fm ~ age*hemisphere + meanFD + (1 | ID), data = fm_data_FFA)
summary_FFA <- tidy(model_FFA)

# MMPFC

fm_data_MMPFC <- subset(fm_data, region == "MMPFC")
model_MMPFC <- lmer(fm ~ age*hemisphere + meanFD + (1 | ID), data = fm_data_MMPFC)
summary_MMPFC <- tidy(model_MMPFC)

# Amygdala

fm_data_amygdala <- subset(fm_data, region == "amygdala")
model_amygdala <- lmer(fm ~ age*hemisphere + meanFD + (1 | ID), data = fm_data_amygdala)
summary_amygdala <- tidy(model_amygdala)

# STS

fm_data_STS <- subset(fm_data, region == "STS")
model_STS <- lmer(fm ~ age*hemisphere + meanFD + (1 | ID), data = fm_data_STS)
summary_STS <- tidy(model_STS)

# Summary

all_summaries <- bind_rows(
  summary_FFA %>% mutate(region = "FFA"),
  summary_MMPFC %>% mutate(region = "MMPFC"),
  summary_amygdala %>% mutate(region = "amygdala"),
  summary_STS %>% mutate(region = "STS")
)
view(all_summaries)

```

Since interaction effects are non-sig, repeat models without interaction effects

```{r}

# FFA

fm_data_FFA <- subset(fm_data, region == "FFA")
model_FFA <- lmer(fm ~ age + hemisphere + meanFD + (1 | ID), data = fm_data_FFA)
summary_FFA <- tidy(model_FFA)

# MMPFC

fm_data_MMPFC <- subset(fm_data, region == "MMPFC")
model_MMPFC <- lmer(fm ~ age + hemisphere + meanFD + (1 | ID), data = fm_data_MMPFC)
summary_MMPFC <- tidy(model_MMPFC)

# Amygdala

fm_data_amygdala <- subset(fm_data, region == "amygdala")
model_amygdala <- lmer(fm ~ age + hemisphere + meanFD + (1 | ID), data = fm_data_amygdala)
summary_amygdala <- tidy(model_amygdala)

# STS

fm_data_STS <- subset(fm_data, region == "STS")
model_STS <- lmer(fm ~ age + hemisphere + meanFD + (1 | ID), data = fm_data_STS)
summary_STS <- tidy(model_STS)

# Save results

all_summaries <- bind_rows(
  summary_FFA %>% mutate(region = "FFA"),
  summary_MMPFC %>% mutate(region = "MMPFC"),
  summary_amygdala %>% mutate(region = "amygdala"),
  summary_STS %>% mutate(region = "STS")
) %>%
  mutate(
    estimate = round(estimate, 2),
    std.error = round(std.error, 2),
    statistic = round(statistic, 2),
    df = round(df, 0),
    p.value = if_else(
      p.value < 0.001,
      format(p.value, scientific = TRUE, digits = 4),
      sprintf("%.3f", p.value)
    )
  )

write.csv(all_summaries, here("results/RQ1", "Fm_age.csv"), row.names = FALSE)

```

### Model plots

Age and functional maturity

```{r}

# Data wrangling

data_plot <- fm_data
data_plot$age <- NULL
data_plot$meanFD <- NULL
data_plot <- merge(data_plot, participants[,c(1:2)], by="ID")
colnames(data_plot) <- c("ID", "hemisphere", "region", "fm", "age")
data_plot_FFA <- subset(data_plot, region == "FFA")
data_plot_STS <- subset(data_plot, region == "STS")
data_plot_MMPFC <- subset(data_plot, region == "MMPFC")
data_plot_amygdala <- subset(data_plot, region == "amygdala")

# Colours

custom_colours_amygdala <- c("#E1AA9F", "#D34835")
custom_colours_MMPFC <- c("#87BACF", "#578CAD")
custom_colours_FFA <- c("#C39EDA", "#652975")
custom_colours_STS <- c("#FFF865", "#FFCE1B")

# FFA plot

plot_FFA <- ggplot(data_plot_FFA, aes(x = age, y = fm, color = hemisphere)) +
  geom_point(alpha = 0.8, size = 2.5, shape = 19) +  
  geom_smooth(method = "lm", se = FALSE, linetype = "solid", linewidth = 2) +  
  scale_color_manual(values = custom_colours_FFA) +  
  labs(title = "",
       x = "Age",
       y = "Functional maturity",
       color = "FFA Hemisphere") +
  theme_minimal() +
  theme(
    legend.position = "bottom",
    legend.text = element_text(size = 16),
    legend.title = element_text(size = 14, face = "bold"),
    axis.text = element_text(size = 12),   
    axis.title = element_text(size = 14, face = "bold"),
    strip.text = element_text(size = 14, face = "bold"),
    strip.background = element_blank(),
    axis.line.x = element_blank(),
    plot.title = element_text(hjust = 0.5, size = 14, face = "bold")) +   
  coord_cartesian(ylim = c(-3, 3)) +
  annotate(
    "text",
    x = Inf, y = -Inf,
    label = "Age effect: \nβ(SE)=0.26(0.07), p<0.001",  
    hjust = 1.05,
    vjust = -0.5,
    size = 4,
    color = "black"
)

# MMPFC plot

plot_MMPFC <- ggplot(data_plot_MMPFC, aes(x = age, y = fm, color = hemisphere)) +
  geom_point(alpha = 0.8, size = 2.8, shape = 19) +  
  geom_smooth(method = "lm", se = FALSE, linetype = "solid", linewidth = 2) +  
  scale_color_manual(values = custom_colours_MMPFC) +  
  labs(title = "",
       x = "Age",
       y = "",
       color = "MMPFC Hemisphere") +
  theme_minimal() +
  theme(
    legend.position = "bottom",
    legend.text = element_text(size = 16),
    legend.title = element_text(size = 14, face = "bold"),
    axis.text = element_text(size = 12),   
    axis.title = element_text(size = 14, face = "bold"),
    strip.text = element_text(size = 14, face = "bold"),
    strip.background = element_blank(),
    axis.line.x = element_blank(),
    axis.text.y = element_blank(),
    plot.title = element_text(hjust = 0.5, size = 14, face = "bold")) +   
  coord_cartesian(ylim = c(-3, 3))  +
  annotate(
    "text",
    x = Inf, y = -Inf,
    label = "Age effect: \nβ(SE)=0.35(0.07), p<0.001",
    hjust = 1.05,
    vjust = -0.5,
    size = 4,
    color = "black"
)

# Amygdala plot

plot_amygdala <- ggplot(data_plot_amygdala, aes(x = age, y = fm, color = hemisphere)) +
  geom_point(alpha = 0.8, size = 2.8, shape = 19) +  
  geom_smooth(method = "lm", se = FALSE, linetype = "solid", linewidth = 2) +  
  scale_color_manual(values = custom_colours_amygdala) +  
  labs(
    title = "",
    x = "Age",
    y = "",
    color = "Amygdala Hemisphere"
  ) +
  theme_minimal() +
  theme(
    legend.position = "bottom",
    legend.text = element_text(size = 16),
    legend.title = element_text(size = 14, face = "bold"),
    axis.text = element_text(size = 12),   
    axis.title = element_text(size = 14, face = "bold"),
    strip.text = element_text(size = 14, face = "bold"),
    strip.background = element_blank(),
    axis.line.x = element_blank(),
    axis.text.y = element_blank(),
    plot.title = element_text(hjust = 0.5, size = 14, face = "bold")
  ) +   
  coord_cartesian(ylim = c(-3, 3)) +
  annotate(
    "text",
    x = Inf, y = -Inf,
    label = "Age effect: \nβ(SE)=0.20(0.08), p=0.016",
    hjust = 1.05,
    vjust = -0.5,
    size = 4,
    color = "black"
)

# STS plot

plot_STS <- ggplot(data_plot_STS, aes(x = age, y = fm, color = hemisphere)) +
  geom_point(alpha = 0.8, size = 2.5, shape = 19) +  
  geom_smooth(method = "lm", se = FALSE, linetype = "solid", linewidth = 2) +  
  scale_color_manual(values = custom_colours_STS) +  
  labs(title = "",
       x = "Age",
       y = "",
       color = "STS Hemisphere") +
  theme_minimal() +
  theme(
    legend.position = "bottom",
    legend.text = element_text(size = 16),
    legend.title = element_text(size = 14, face = "bold"),
    axis.text = element_text(size = 12),   
    axis.title = element_text(size = 14, face = "bold"),
    strip.text = element_text(size = 14, face = "bold"),
    strip.background = element_blank(),
    axis.line.x = element_blank(),
    plot.title = element_text(hjust = 0.5, size = 14, face = "bold")) +   
  coord_cartesian(ylim = c(-3, 3)) +
  annotate(
    "text",
    x = Inf, y = -Inf,
    label = "Age effect: \nβ(SE)=0.24(0.07), p<0.001",
    hjust = 1.05,
    vjust = -0.5,
    size = 4,
    color = "black"
)

# Combine and save plots

fm_age <- (plot_FFA | plot_MMPFC | plot_amygdala | plot_STS) +  
  plot_annotation(title = "Functional maturity across Age") &  
  theme(plot.title = element_text(hjust = 0.5, size = 16, face = "bold"))
fm_age  
ggsave(here("results/figures", "Fm_age.png"), plot = fm_age, width = 17, height = 5, units = "in", dpi = 300)

```


## Section II: Magnitude of responses of each ROI at face/scene events

### Read data

```{r}

# Events magnitude

child_eventsmagnitude <- read_csv(here("processed_data", "child_MRIvariables.csv"), col_names=TRUE)
child_eventsmagnitude <- child_eventsmagnitude[,c(1, 10:201)]

# Reshape the dataset to long format

long_data <- child_eventsmagnitude %>%
  pivot_longer(
    cols = -ID,  # Exclude the ID column
    names_to = c("region", "event"),  # Split names into region and event
    names_pattern = "([lr]?[^_]+)_(F\\d{2}|S\\d{2})",  # Match region and event
    values_to = "value"  # The name of the new column for values
  ) %>%
  mutate(
    hemisphere = if_else(grepl("^l", region), "left", "right"),  # Add hemisphere based on region prefix
    region = gsub("^[lr]", "", region)  # Remove hemisphere prefix from region
  ) %>%
  pivot_wider(
    names_from = "event",  # Make "event" column headers
    values_from = "value"  # Fill the values for each event
  )
long_data <- long_data %>%
  select(ID, hemisphere, region, F01, F02, F03, F04, F05, F06, F07, F08, F09, F10, F11, F12, 
         S01, S02, S03, S04, S05, S06, S07, S08, S09, S10, S11, S12) 

# Merge age, motion and fm data

eventsmagnitude_data <- merge(long_data, participants[,c(1:2)], by="ID")
eventsmagnitude_data <- merge(eventsmagnitude_data, motion[,c(4,6)], by="ID")
colnames(eventsmagnitude_data) <- c("ID", "hemisphere", "region", "F01", "F02", "F03", "F04", "F05", "F06", "F07", "F08", "F09", "F10", "F11", "F12", "S01", "S02", "S03", "S04", "S05", "S06", "S07", "S08", "S09", "S10", "S11", "S12", "age", "meanFD")

# Scale predictors

eventsmagnitude_data[, c("age", "meanFD")] <- scale(eventsmagnitude_data[, c("age", "meanFD")])

# Ensure categorical variables are treated as factors

eventsmagnitude_data$ID <- as.factor(eventsmagnitude_data$ID)
eventsmagnitude_data$hemisphere <- as.factor(eventsmagnitude_data$hemisphere)
eventsmagnitude_data$region <- as.factor(eventsmagnitude_data$region)

```

### Models

FFA

```{r}

# Read data

eventsmagnitude_data_FFA <- subset(eventsmagnitude_data, region == "FFA")

## Face events

### Models with interaction effects

events <- paste0("F", sprintf("%02d", 1:12))
model_summaries <- list()
for (event in events) {
  #### Create the formula dynamically
  formula <- as.formula(paste(event, "~ age*hemisphere + meanFD + (1 | ID)"))
  
  #### Fit the model
  model <- lmer(formula, data = eventsmagnitude_data_FFA)
  
  #### Summarise the model
  summary_tidy <- tidy(model)
  
  #### Store the summary in the list with the event name as the key
  model_summaries[[event]] <- summary_tidy
}
summaries_FFA_face_events <- do.call(rbind, lapply(names(model_summaries), function(event) {
  model_summaries[[event]] %>% mutate(event = event)  # Add the event name to each summary
}))
summaries_FFA_face_events$region <- "FFA"
summaries_FFA_face_events <- summaries_FFA_face_events %>%
  mutate(sig = case_when(
    p.value < 0.001 ~ "***",
    p.value < 0.01  ~ "**",
    p.value < 0.05  ~ "*",
    TRUE            ~ ""
  ))

### Interaction effects are non-sig for all events, repeat models without interaction effects for all events

model_summaries <- list()
for (event in events) {
  #### Create the formula dynamically
  formula <- as.formula(paste(event, "~ age + hemisphere + meanFD + (1 | ID)"))
  
  #### Fit the model
  model <- lmer(formula, data = eventsmagnitude_data_FFA)
  
  #### Summarise the model
  summary_tidy <- tidy(model)
  
  #### Store the summary in the list with the event name as the key
  model_summaries[[event]] <- summary_tidy
}
summaries_FFA_face_events <- do.call(rbind, lapply(names(model_summaries), function(event) {
  model_summaries[[event]] %>% mutate(event = event)  #add the event name to each summary
}))
summaries_FFA_face_events$region <- "FFA"
summaries_FFA_face_events$p.value <- as.numeric(summaries_FFA_face_events$p.value)
summaries_FFA_face_events <- summaries_FFA_face_events %>%
  mutate(sig = case_when(
    p.value < 0.004 ~ "significant after correction",
    TRUE            ~ ""
  ))

## Scene events

### Models with interaction effects

events <- paste0("S", sprintf("%02d", 1:12))  #generates S01, S02, ..., S12
model_summaries <- list()
for (event in events) {
  #### Create the formula dynamically
  formula <- as.formula(paste(event, "~ age*hemisphere + meanFD + (1 | ID)"))
  
  #### Fit the model
  model <- lmer(formula, data = eventsmagnitude_data_FFA)
  
  #### Summarise the model
  summary_tidy <- tidy(model)
  
  #### Store the summary in the list with the event name as the key
  model_summaries[[event]] <- summary_tidy
}
summaries_FFA_scene_events <- do.call(rbind, lapply(names(model_summaries), function(event) {
  model_summaries[[event]] %>% mutate(event = event)  #add the event name to each summary
}))
summaries_FFA_scene_events$region <- "FFA"
summaries_FFA_scene_events <- summaries_FFA_scene_events %>%
  mutate(sig = case_when(
    p.value < 0.001 ~ "***",
    p.value < 0.01  ~ "**",
    p.value < 0.05  ~ "*",
    TRUE            ~ ""
  ))

### Interaction effects are non-sig for all events, repeat models without interaction effects for all events

model_summaries <- list()

for (event in events) {
  #### Create the formula dynamically
  formula <- as.formula(paste(event, "~ age + hemisphere + meanFD + (1 | ID)"))
  
  #### Fit the model
  model <- lmer(formula, data = eventsmagnitude_data_FFA)
  
  #### Summarise the model
  summary_tidy <- tidy(model)
  
  #### Store the summary in the list with the event name as the key
  model_summaries[[event]] <- summary_tidy
}
summaries_FFA_scene_events <- do.call(rbind, lapply(names(model_summaries), function(event) {
  model_summaries[[event]] %>% mutate(event = event)  #add the event name to each summary
}))
summaries_FFA_scene_events$region <- "FFA"
summaries_FFA_scene_events$p.value <- as.numeric(summaries_FFA_scene_events$p.value)
summaries_FFA_scene_events <- summaries_FFA_scene_events %>%
  mutate(sig = case_when(
    p.value < 0.004 ~ "significant after correction",
    TRUE            ~ ""
  ))

```

MMPFC

```{r}

# Read data

eventsmagnitude_data_MMPFC <- subset(eventsmagnitude_data, region == "MMPFC")

## Face events

### Models with interaction effects

events <- paste0("F", sprintf("%02d", 1:12))
model_summaries <- list()

for (event in events) {
  #### Create the formula dynamically
  formula <- as.formula(paste(event, "~ age*hemisphere + meanFD + (1 | ID)"))
  
  #### Fit the model
  model <- lmer(formula, data = eventsmagnitude_data_MMPFC)
  
  #### Summarise the model
  summary_tidy <- tidy(model)
  
  #### Store the summary in the list with the event name as the key
  model_summaries[[event]] <- summary_tidy
}
summaries_MMPFC_face_events <- do.call(rbind, lapply(names(model_summaries), function(event) {
  model_summaries[[event]] %>% mutate(event = event)  #add the event name to each summary
}))
summaries_MMPFC_face_events$region <- "MMPFC"
summaries_MMPFC_face_events <- summaries_MMPFC_face_events %>%
  mutate(sig = case_when(
    p.value < 0.001 ~ "***",
    p.value < 0.01  ~ "**",
    p.value < 0.05  ~ "*",
    TRUE            ~ ""
  ))

### Interaction effects are non-sig for all events but F05, F07, F10 and F12, repeat models without interaction effects for all events but F05, F06, F07, F10 and F12

events <- c("F01", "F02", "F03", "F04", "F06", "F08", "F09", "F11")
model_summaries <- list()

for (event in events) {
  #### Create the formula dynamically
  formula <- as.formula(paste(event, "~ age + hemisphere + meanFD + (1 | ID)"))
  
  #### Fit the model
  model <- lmer(formula, data = eventsmagnitude_data_MMPFC)
  
  #### Summarise the model
  summary_tidy <- tidy(model)
  
  #### Store the summary in the list with the event name as the key
  model_summaries[[event]] <- summary_tidy
}
summaries_MMPFC_face_events <- do.call(rbind, lapply(names(model_summaries), function(event) {
  model_summaries[[event]] %>% mutate(event = event)  #add the event name to each summary
}))
model_MMPFC_F05 <- lmer(F05 ~ age*hemisphere + meanFD + (1 | ID), data = eventsmagnitude_data_MMPFC)
summary_MMPFC_F05 <- tidy(model_MMPFC_F05)              
summary_MMPFC_F05 <- summary_MMPFC_F05 %>% mutate(event = "F05")
model_MMPFC_F07 <- lmer(F07 ~ age*hemisphere + meanFD + (1 | ID), data = eventsmagnitude_data_MMPFC)
summary_MMPFC_F07 <- tidy(model_MMPFC_F07)              
summary_MMPFC_F07 <- summary_MMPFC_F07 %>% mutate(event = "F07")
model_MMPFC_F10 <- lmer(F10 ~ age*hemisphere + meanFD + (1 | ID), data = eventsmagnitude_data_MMPFC)
summary_MMPFC_F10 <- tidy(model_MMPFC_F10)              
summary_MMPFC_F10 <- summary_MMPFC_F10 %>% mutate(event = "F10")
model_MMPFC_F12 <- lmer(F12 ~ age*hemisphere + meanFD + (1 | ID), data = eventsmagnitude_data_MMPFC)
summary_MMPFC_F12 <- tidy(model_MMPFC_F12)              
summary_MMPFC_F12 <- summary_MMPFC_F12 %>% mutate(event = "F12")
summaries_MMPFC_face_events <- bind_rows(summaries_MMPFC_face_events, summary_MMPFC_F05, summary_MMPFC_F07, summary_MMPFC_F10, summary_MMPFC_F12)
summaries_MMPFC_face_events$region <- "MMPFC"
summaries_MMPFC_face_events$p.value <- as.numeric(summaries_MMPFC_face_events$p.value)
summaries_MMPFC_face_events <- summaries_MMPFC_face_events %>%
  mutate(sig = case_when(
    p.value < 0.004 ~ "significant after correction",
    TRUE            ~ ""
  ))

## Scene events

### Models with interaction effects

events <- paste0("S", sprintf("%02d", 1:12))  #generates S01, S02, ..., S12
model_summaries <- list()

for (event in events) {
  #### Create the formula dynamically
  formula <- as.formula(paste(event, "~ age*hemisphere + meanFD + (1 | ID)"))
  
  #### Fit the model
  model <- lmer(formula, data = eventsmagnitude_data_MMPFC)
  
  #### Summarise the model
  summary_tidy <- tidy(model)
  
  #### Store the summary in the list with the event name as the key
  model_summaries[[event]] <- summary_tidy
}
summaries_MMPFC_scene_events <- do.call(rbind, lapply(names(model_summaries), function(event) {
  model_summaries[[event]] %>% mutate(event = event)  # Add the event name to each summary
}))
summaries_MMPFC_scene_events$region <- "MMPFC"
summaries_MMPFC_scene_events <- summaries_MMPFC_scene_events %>%
  mutate(sig = case_when(
    p.value < 0.001 ~ "***",
    p.value < 0.01  ~ "**",
    p.value < 0.05  ~ "*",
    TRUE            ~ ""
  ))

### Interaction effects are non-sig for all events, repeat models without interaction effects for all events

model_summaries <- list()

for (event in events) {
  #### Create the formula dynamically
  formula <- as.formula(paste(event, "~ age + hemisphere + meanFD + (1 | ID)"))
  
  #### Fit the model
  model <- lmer(formula, data = eventsmagnitude_data_MMPFC)
  
  #### Summarise the model
  summary_tidy <- tidy(model)
  
  #### Store the summary in the list with the event name as the key
  model_summaries[[event]] <- summary_tidy
}
summaries_MMPFC_scene_events <- do.call(rbind, lapply(names(model_summaries), function(event) {
  model_summaries[[event]] %>% mutate(event = event)  #add the event name to each summary
}))
summaries_MMPFC_scene_events$region <- "MMPFC"
summaries_MMPFC_scene_events$p.value <- as.numeric(summaries_MMPFC_scene_events$p.value)
summaries_MMPFC_scene_events <- summaries_MMPFC_scene_events %>%
  mutate(sig = case_when(
    p.value < 0.004 ~ "significant after correction",
    TRUE            ~ ""
  ))

```

Amygdala

```{r}

# Read data

eventsmagnitude_data_amygdala <- subset(eventsmagnitude_data, region == "amygdala")

## Face events

### Models with interaction effects

events <- paste0("F", sprintf("%02d", 1:12))
model_summaries <- list()

for (event in events) {
  #### Create the formula dynamically
  formula <- as.formula(paste(event, "~ age*hemisphere + meanFD + (1 | ID)"))
  
  #### Fit the model
  model <- lmer(formula, data = eventsmagnitude_data_amygdala)
  
  #### Summarise the model
  summary_tidy <- tidy(model)
  
  #### Store the summary in the list with the event name as the key
  model_summaries[[event]] <- summary_tidy
}

summaries_amygdala_face_events <- do.call(rbind, lapply(names(model_summaries), function(event) {
  model_summaries[[event]] %>% mutate(event = event)  # Add the event name to each summary
}))

summaries_amygdala_face_events$region <- "amygdala"
summaries_amygdala_face_events <- summaries_amygdala_face_events %>%
  mutate(sig = case_when(
    p.value < 0.001 ~ "***",
    p.value < 0.01  ~ "**",
    p.value < 0.05  ~ "*",
    TRUE            ~ ""
  ))

### Interaction effects are non-sig for all events but F04, repeat models without interaction effects for all events but F04

events <- c("F01", "F02", "F03", "F05", "F06", "F07", "F08", "F09", "F10", "F11", "F12")

model_summaries <- list()

for (event in events) {
  #### Create the formula dynamically
  formula <- as.formula(paste(event, "~ age + hemisphere + meanFD + (1 | ID)"))
  
  #### Fit the model
  model <- lmer(formula, data = eventsmagnitude_data_amygdala)
  
  #### Summarise the model
  summary_tidy <- tidy(model)
  
  #### Store the summary in the list with the event name as the key
  model_summaries[[event]] <- summary_tidy
}

summaries_amygdala_face_events <- do.call(rbind, lapply(names(model_summaries), function(event) {
  model_summaries[[event]] %>% mutate(event = event)  # Add the event name to each summary
}))
model_amygdala_F04 <- lmer(F04 ~ age*hemisphere + meanFD + (1 | ID), data = eventsmagnitude_data_amygdala)
summary_amygdala_F04 <- tidy(model_amygdala_F04)              
summary_amygdala_F04 <- summary_amygdala_F04 %>% mutate(event = "F04")
summaries_amygdala_face_events <- bind_rows(summaries_amygdala_face_events, summary_amygdala_F04)
summaries_amygdala_face_events$region <- "amygdala"
summaries_amygdala_face_events$p.value <- as.numeric(summaries_amygdala_face_events$p.value)
summaries_amygdala_face_events <- summaries_amygdala_face_events %>%
  mutate(sig = case_when(
    p.value < 0.004 ~ "significant after correction",
    TRUE            ~ ""
  ))

## Scene events

### Models with interaction effects

events <- paste0("S", sprintf("%02d", 1:12))  #generates S01, S02, ..., S12
model_summaries <- list()

for (event in events) {
  #### Create the formula dynamically
  formula <- as.formula(paste(event, "~ age*hemisphere + meanFD + (1 | ID)"))
  
  #### Fit the model
  model <- lmer(formula, data = eventsmagnitude_data_amygdala)
  
  #### Summarise the model
  summary_tidy <- tidy(model)
  
  #### Store the summary in the list with the event name as the key
  model_summaries[[event]] <- summary_tidy
}

summaries_amygdala_scene_events <- do.call(rbind, lapply(names(model_summaries), function(event) {
  model_summaries[[event]] %>% mutate(event = event)  #add the event name to each summary
}))

summaries_amygdala_scene_events$region <- "amygdala"
summaries_amygdala_scene_events <- summaries_amygdala_scene_events %>%
  mutate(sig = case_when(
    p.value < 0.001 ~ "***",
    p.value < 0.01  ~ "**",
    p.value < 0.05  ~ "*",
    TRUE            ~ ""
  ))

### Interaction effects are non-sig for all events, repeat models without interaction effects for all events

model_summaries <- list()

for (event in events) {
  # Create the formula dynamically
  formula <- as.formula(paste(event, "~ age + hemisphere + meanFD + (1 | ID)"))
  
  # Fit the model
  model <- lmer(formula, data = eventsmagnitude_data_amygdala)
  
  # Summarise the model
  summary_tidy <- tidy(model)
  
  # Store the summary in the list with the event name as the key
  model_summaries[[event]] <- summary_tidy
}

summaries_amygdala_scene_events <- do.call(rbind, lapply(names(model_summaries), function(event) {
  model_summaries[[event]] %>% mutate(event = event)  # Add the event name to each summary
}))

summaries_amygdala_scene_events$region <- "amygdala"
summaries_amygdala_scene_events$p.value <- as.numeric(summaries_amygdala_scene_events$p.value)
summaries_amygdala_scene_events <- summaries_amygdala_scene_events %>%
  mutate(sig = case_when(
    p.value < 0.004 ~ "significant after correction",
    TRUE            ~ ""
  ))

```

STS

```{r}

# Read data

eventsmagnitude_data_STS <- subset(eventsmagnitude_data, region == "STS")

## Face events

### Models with interaction effects

events <- paste0("F", sprintf("%02d", 1:12))
model_summaries <- list()
for (event in events) {
  #### Create the formula dynamically
  formula <- as.formula(paste(event, "~ age*hemisphere + meanFD + (1 | ID)"))
  
  #### Fit the model
  model <- lmer(formula, data = eventsmagnitude_data_STS)
  
  #### Summarise the model
  summary_tidy <- tidy(model)
  
  #### Store the summary in the list with the event name as the key
  model_summaries[[event]] <- summary_tidy
}
summaries_STS_face_events <- do.call(rbind, lapply(names(model_summaries), function(event) {
  model_summaries[[event]] %>% mutate(event = event)  # Add the event name to each summary
}))
summaries_STS_face_events$region <- "STS"
summaries_STS_face_events <- summaries_STS_face_events %>%
  mutate(sig = case_when(
    p.value < 0.001 ~ "***",
    p.value < 0.01  ~ "**",
    p.value < 0.05  ~ "*",
    TRUE            ~ ""
  ))

### Interaction effects are non-sig for all events but F09, repeat models without interaction effects for all events but F09

events <- c("F01", "F02", "F03", "F04", "F05", "F06", "F07", "F08", "F10", "F11", "F12")

model_summaries <- list()
for (event in events) {
  #### Create the formula dynamically
  formula <- as.formula(paste(event, "~ age + hemisphere + meanFD + (1 | ID)"))
  
  #### Fit the model
  model <- lmer(formula, data = eventsmagnitude_data_STS)
  
  #### Summarise the model
  summary_tidy <- tidy(model)
  
  #### Store the summary in the list with the event name as the key
  model_summaries[[event]] <- summary_tidy
}
summaries_STS_face_events <- do.call(rbind, lapply(names(model_summaries), function(event) {
  model_summaries[[event]] %>% mutate(event = event)  #add the event name to each summary
}))
model_STS_F09 <- lmer(F09 ~ age*hemisphere + meanFD + (1 | ID), data = eventsmagnitude_data_STS)
summary_STS_F09 <- tidy(model_STS_F09)              
summary_STS_F09 <- summary_STS_F09 %>% mutate(event = "F09")
summaries_STS_face_events <- bind_rows(summaries_STS_face_events, summary_STS_F09)
summaries_STS_face_events$region <- "STS"
summaries_STS_face_events$p.value <- as.numeric(summaries_STS_face_events$p.value)
summaries_STS_face_events <- summaries_STS_face_events %>%
  mutate(sig = case_when(
    p.value < 0.004 ~ "significant after correction",
    TRUE            ~ ""
  ))

## Scene events

### Models with interaction effects

events <- paste0("S", sprintf("%02d", 1:12))  #generates S01, S02, ..., S12
model_summaries <- list()
for (event in events) {
  #### Create the formula dynamically
  formula <- as.formula(paste(event, "~ age*hemisphere + meanFD + (1 | ID)"))
  
  #### Fit the model
  model <- lmer(formula, data = eventsmagnitude_data_STS)
  
  #### Summarise the model
  summary_tidy <- tidy(model)
  
  #### Store the summary in the list with the event name as the key
  model_summaries[[event]] <- summary_tidy
}
summaries_STS_scene_events <- do.call(rbind, lapply(names(model_summaries), function(event) {
  model_summaries[[event]] %>% mutate(event = event)  #add the event name to each summary
}))
summaries_STS_scene_events$region <- "STS"
summaries_STS_scene_events <- summaries_STS_scene_events %>%
  mutate(sig = case_when(
    p.value < 0.001 ~ "***",
    p.value < 0.01  ~ "**",
    p.value < 0.05  ~ "*",
    TRUE            ~ ""
  ))

### Interaction effects are non-sig for all events but S02 and S08, repeat models without interaction effects for all events except S02 and S08

events <- c("S01", "S03", "S04", "S05", "S06", "S07", "S09", "S10", "S11", "S12")
model_summaries <- list()
for (event in events) {
  #### Create the formula dynamically
  formula <- as.formula(paste(event, "~ age + hemisphere + meanFD + (1 | ID)"))
  
  #### Fit the model
  model <- lmer(formula, data = eventsmagnitude_data_STS)
  
  #### Summarise the model
  summary_tidy <- tidy(model)
  
  #### Store the summary in the list with the event name as the key
  model_summaries[[event]] <- summary_tidy
}
summaries_STS_scene_events <- do.call(rbind, lapply(names(model_summaries), function(event) {
  model_summaries[[event]] %>% mutate(event = event)  #add the event name to each summary
}))
model_STS_S02 <- lmer(S02 ~ age*hemisphere + meanFD + (1 | ID), data = eventsmagnitude_data_STS)
summary_STS_S02 <- tidy(model_STS_S02)              
summary_STS_S02 <- summary_STS_S02 %>% mutate(event = "S02")
model_STS_S08 <- lmer(S08 ~ age*hemisphere + meanFD + (1 | ID), data = eventsmagnitude_data_STS)
summary_STS_S08 <- tidy(model_STS_S08)              
summary_STS_S08 <- summary_STS_S08 %>% mutate(event = "S08")
summaries_STS_scene_events <- bind_rows(summaries_STS_scene_events, summary_STS_S02, summary_STS_S08)
summaries_STS_scene_events$region <- "STS"
summaries_STS_scene_events$p.value <- as.numeric(summaries_STS_scene_events$p.value)
summaries_STS_scene_events <- summaries_STS_scene_events %>%
  mutate(sig = case_when(
    p.value < 0.004 ~ "significant after correction",
    TRUE            ~ ""
  ))

```

Save results

```{r}

all_summaries <- bind_rows(
  summaries_FFA_face_events,
  summaries_FFA_scene_events,
  summaries_MMPFC_face_events,
  summaries_MMPFC_scene_events,
  summaries_amygdala_face_events,
  summaries_amygdala_scene_events,
  summaries_STS_face_events,
  summaries_STS_scene_events
)
all_summaries$p.value <- as.numeric(all_summaries$p.value)
event_order <- c(
  "F01","F09","F11","F04","F10","F12","F07","F08","F06","F05","F02","F03",
  "S07","S02","S03","S04","S12","S11","S10","S06","S08","S05","S09","S01"
)

all_summaries <- all_summaries %>%
  mutate(
    across(c(estimate, std.error, statistic, df), ~ round(.x, 2)),
    p.value = if_else(p.value < 0.001,
                      format(p.value, scientific = TRUE, digits = 4),
                      sprintf("%.3f", p.value)),
    event = factor(event, levels = event_order)
  ) %>%
  arrange(region, event)

write.csv(all_summaries, here("results/RQ1", "Eventmagnitude_age.csv"), row.names = FALSE)

```

### Model plots

Timecourses and events

```{r}

#   Data wrangling

TCs_total <- read_csv(here("processed_data", "TCs_total.csv"), col_names=TRUE)
data_plot <- merge(TCs_total, participants[,c(1,3,4)], by="ID")
data_plot <- data_plot %>%
  filter(Child_Adult == "child")
data_plot$Child_Adult <- NULL
data_plot <- data_plot %>%
  group_by(time, AgeGroup) %>%
  summarise(
    avg_lamygdala = mean(lamygdala, na.rm = TRUE),
    avg_ramygdala = mean(ramygdala, na.rm = TRUE),
    avg_lFFA = mean(lFFA, na.rm = TRUE),
    avg_rFFA = mean(rFFA, na.rm = TRUE),
    avg_lMMPFC = mean(lMMPFC, na.rm = TRUE),
    avg_rMMPFC = mean(rMMPFC, na.rm = TRUE), 
    avg_lSTS = mean(lSTS, na.rm = TRUE),
    avg_rSTS = mean(rSTS, na.rm = TRUE), .groups = "drop"
  )

avg_adult_TCs_trad_fROIs <- read.csv(here("raw_data/timecourses", "TCs_trad_adult_fROIs.csv"), header = TRUE, dec = ".", sep = ",")
avg_adult_TCs_trad_fROIs <- avg_adult_TCs_trad_fROIs %>%
  mutate(time = time - 1)
TCs_amygdala <- read.csv(here("raw_data/timecourses", "TCs_amygdala.csv"), header = TRUE, dec = ".", sep = ",")
TCs_amygdala$sub <- gsub("[pixar]", "", TCs_amygdala$sub)
TCs_amygdala$sub <- trimws(TCs_amygdala$sub)
TCs_amygdala$run <- NULL
colnames(TCs_amygdala) <- c("time", "ID", "lamygdala", "ramygdala")
adult_list <- row.names(participants)[which(participants[["Child_Adult"]] == "adult")]
adult_TCs_amygdala <- TCs_amygdala %>%
  filter(ID %in% adult_list)
avg_adult_TCs_amygdala <- adult_TCs_amygdala %>%
  group_by(time) %>%
  summarise(
    avg_lamygdala = mean(lamygdala, na.rm = TRUE),
    avg_ramygdala = mean(ramygdala, na.rm = TRUE)
  )
avg_adult_TCs <- merge(avg_adult_TCs_amygdala, avg_adult_TCs_trad_fROIs, by="time")
avg_adult_TCs$AgeGroup <- "adult"
avg_adult_TCs <- avg_adult_TCs[, c("time", "AgeGroup", "avg_lamygdala", "avg_ramygdala", "avg_lFFA", "avg_rFFA", "avg_lMMPFC", "avg_rMMPFC", "avg_lSTS", "avg_rSTS")]
data_plot <- rbind(data_plot, avg_adult_TCs)
colnames(data_plot) <- c("time", "AgeGroup", "lamygdala", "ramygdala", "lFFA", "rFFA", "lMMPFC", "rMMPFC", "lSTS", "rSTS")

data_plot <- data_plot %>%
  pivot_longer(
    cols = c(lamygdala, ramygdala, lFFA, rFFA, lMMPFC, rMMPFC, lSTS, rSTS),
    names_to = "Temp",
    values_to = "value"
  ) %>%
  ## Separate the "Temp" column into "Hemisphere" and "Region"
  mutate(
    hemisphere = if_else(str_starts(Temp, "l"), "left", "right"),
    region = case_when(
      str_detect(Temp, "amygdala") ~ "amygdala",
      str_detect(Temp, "FFA") ~ "FFA",
      str_detect(Temp, "MMPFC") ~ "MMPFC",
      str_detect(Temp, "STS") ~ "STS",
      TRUE ~ NA_character_
    )
  ) %>%
  select(-Temp)  #drop the temporary column

data_plot_FFA <- subset(data_plot, region == "FFA")
data_plot_MMPFC <- subset(data_plot, region == "MMPFC")
data_plot_amygdala <- subset(data_plot, region == "amygdala")
data_plot_STS <- subset(data_plot, region == "STS")

events_TRs <- read_csv(here("processed_data", "events_TRs.csv"), col_names=TRUE)
events_TRs <- events_TRs[,c(1:3)]
custom_colours <- c("#D34835", "#DDA86A", "#83AC66", "#87BACF", "#6989F3", "#652975")

# FFA Timecourses, including events

## Plot

Plot_FFA <- ggplot(data_plot_FFA) +
  geom_line(aes(x = time, y = value, color = AgeGroup, group = AgeGroup), size = 1.2, alpha = 1) +
  geom_hline(yintercept = 0, color = "grey", size = 0.8) +
  geom_text(data = data_plot_FFA[data_plot_FFA$time %in% c(0, 5, 10, 15, 20, 25, 30, 35, 40, 45, 50, 55, 60, 65, 70, 75, 80, 85, 90, 95, 100, 105, 110, 115, 120, 125, 130, 135, 140, 145, 150, 155, 160, 165, 170),], 
            aes(x = time, y = -0.07, label = time), vjust = 0, size = 3, color = "black", angle = 90) +
  facet_wrap(~ hemisphere, scales = "free_y") +
  theme_classic() +
  scale_color_manual(values = custom_colours) +
  scale_y_continuous(limits = c(-1.5, 1.5)) +
  scale_x_continuous(
    breaks = c(0, 5, 10, 15, 20, 25, 30, 35, 40, 45, 50, 55, 60, 65, 70, 75, 80, 85, 90, 95, 100, 105, 110, 115, 120, 125, 130, 135, 140, 145, 150, 155, 160, 165, 170), 
    labels = NULL
  ) +
  labs(
    title = "FFA",
    y = "Response magnitude",
    color = "Age group"
  ) +
  theme(
    strip.text = element_text(size = 16),
    strip.background = element_blank(),
    legend.position = "bottom",
    axis.title.x = element_text(size = 16),
    axis.title.y = element_text(size = 16),
    axis.text.x = element_text(size = 16),
    axis.text.y = element_text(size = 16),
    axis.ticks.x = element_blank(),
    axis.line.x = element_blank(),
    plot.title = element_text(hjust = 0.5, size = 16, face = "bold"),
    axis.line.y = element_line(linewidth = 0.8, color = "black"),
    legend.text = element_text(size = 16),
    legend.title = element_text(size = 16, face = "bold")
  )

## Add the shaded rectangles for events

Plot_FFA <- Plot_FFA + 
  geom_rect(data = events_TRs, 
            aes(xmin = onset, xmax = end, ymin = -1.5, ymax = 1.5, fill = trial_type), 
            alpha = 0.3, color = NA) +
  scale_fill_manual(values = c("faces" = "#F9B6C7", "scenes" = "#3B7D23")) +
  guides(fill = guide_legend(title = "Event type"), title.theme = element_text(face = "bold"))

print(Plot_FFA)

# MMPFC Timecourses, including events

Plot_MMPFC <- ggplot(data_plot_MMPFC) +
  geom_line(aes(x = time, y = value, color = AgeGroup, group = AgeGroup), size = 1.2, alpha = 1) +
  geom_hline(yintercept = 0, color = "grey", size = 0.8) +
  geom_text(data = data_plot_MMPFC[data_plot_MMPFC$time %in% c(0, 5, 10, 15, 20, 25, 30, 35, 40, 45, 50, 55, 60, 65, 70, 75, 80, 85, 90, 95, 100, 105, 110, 115, 120, 125, 130, 135, 140, 145, 150, 155, 160, 165, 170),], 
            aes(x = time, y = -0.07, label = time), vjust = 0, size = 3, color = "black", angle = 90) +
  facet_wrap(~ hemisphere, scales = "free_y") +
  theme_classic() +
  scale_color_manual(values = custom_colours) +
  scale_y_continuous(limits = c(-1.5, 1.5)) +
  scale_x_continuous(
    breaks = c(0, 5, 10, 15, 20, 25, 30, 35, 40, 45, 50, 55, 60, 65, 70, 75, 80, 85, 90, 95, 100, 105, 110, 115, 120, 125, 130, 135, 140, 145, 150, 155, 160, 165, 170),
    labels = NULL
  ) +
  labs(
    title = "MMPFC",
    y = "Response magnitude",
    color = "Age group"
  ) +
  theme(
    strip.text = element_text(size = 16),
    strip.background = element_blank(),
    legend.position = "bottom",
    axis.title.x = element_text(size = 16),
    axis.title.y = element_text(size = 16),
    axis.text.x = element_text(size = 16),
    axis.text.y = element_text(size = 16),
    axis.ticks.x = element_blank(),
    axis.line.x = element_blank(),
    plot.title = element_text(hjust = 0.5, size = 16, face = "bold"),
    axis.line.y = element_line(linewidth = 0.8, color = "black"),
    legend.text = element_text(size = 16),
    legend.title = element_text(size = 16, face = "bold")
  )

## Add the shaded rectangles for events

Plot_MMPFC <- Plot_MMPFC + 
  geom_rect(data = events_TRs, 
            aes(xmin = onset, xmax = end, ymin = -1.5, ymax = 1.5, fill = trial_type), 
            alpha = 0.3, color = NA) +
  scale_fill_manual(values = c("faces" = "#F9B6C7", "scenes" = "#3B7D23")) +
  guides(fill = guide_legend(title = "Event type"), title.theme = element_text(face = "bold"))

## Get the 10th "faces" event (pink box)

pink_boxes <- events_TRs[events_TRs$trial_type == "faces",]
tenth_pink_box <- pink_boxes[10,]  #get the 10th pink box

## Adjust the y position for the asterisk to stay within the valid range

Plot_MMPFC <- Plot_MMPFC +
  geom_text(data = tenth_pink_box, 
            aes(x = (onset + end) / 2 - 1, y = 1.40, label = "*"),  # Adjust y to fit within plot limits
            size = 8, color = "black", fontface = "bold", vjust = 0)

print(Plot_MMPFC)

# Amygdala Timecourses, including events

Plot_amygdala <- ggplot(data_plot_amygdala) +
  geom_line(aes(x = time, y = value, color = AgeGroup, group = AgeGroup), size = 1.2, alpha = 1) +
  geom_hline(yintercept = 0, color = "grey", size = 0.8) +
  geom_text(data = data_plot_amygdala[data_plot_amygdala$time %in% c(0, 5, 10, 15, 20, 25, 30, 35, 40, 45, 50, 55, 60, 65, 70, 75, 80, 85, 90, 95, 100, 105, 110, 115, 120, 125, 130, 135, 140, 145, 150, 155, 160, 165, 170),], 
            aes(x = time, y = -0.07, label = time), vjust = 0, size = 3, color = "black", angle = 90) +
  facet_wrap(~ hemisphere, scales = "free_y") +
  theme_classic() +
  scale_color_manual(values = custom_colours) +
  scale_y_continuous(limits = c(-1.5, 1.5)) +
  scale_x_continuous(
    breaks = c(0, 5, 10, 15, 20, 25, 30, 35, 40, 45, 50, 55, 60, 65, 70, 75, 80, 85, 90, 95, 100, 105, 110, 115, 120, 125, 130, 135, 140, 145, 150, 155, 160, 165, 170),
    labels = NULL
  ) +
  labs(
    title = "Amygdala",
    y = "Response magnitude",
    color = "Age group"
  ) +
  theme(
    strip.text = element_text(size = 16),
    strip.background = element_blank(),
    legend.position = "bottom",
    axis.title.x = element_text(size = 16),
    axis.title.y = element_text(size = 16),
    axis.text.x = element_text(size = 16),
    axis.text.y = element_text(size = 16),
    axis.ticks.x = element_blank(),
    axis.line.x = element_blank(),
    plot.title = element_text(hjust = 0.5, size = 16, face = "bold"),
    axis.line.y = element_line(linewidth = 0.8, color = "black"),
    legend.text = element_text(size = 16),
    legend.title = element_text(size = 16, face = "bold")
  )

Plot_amygdala <- Plot_amygdala + 
  geom_rect(data = events_TRs, 
            aes(xmin = onset, xmax = end, ymin = -1.5, ymax = 1.5, fill = trial_type), 
            alpha = 0.3, color = NA) +
  scale_fill_manual(values = c("faces" = "#F9B6C7", "scenes" = "#3B7D23")) +
  guides(fill = guide_legend(title = "Event type"), title.theme = element_text(face = "bold"))

print(Plot_amygdala)

# STS Timecourses, including events

Plot_STS <- ggplot(data_plot_STS) +
  geom_line(aes(x = time, y = value, color = AgeGroup, group = AgeGroup), size = 1.2, alpha = 1) +
  geom_hline(yintercept = 0, color = "grey", size = 0.8) +
  geom_text(data = data_plot_STS[data_plot_STS$time %in% c(0, 5, 10, 15, 20, 25, 30, 35, 40, 45, 50, 55, 60, 65, 70, 75, 80, 85, 90, 95, 100, 105, 110, 115, 120, 125, 130, 135, 140, 145, 150, 155, 160, 165, 170),], 
            aes(x = time, y = -0.07, label = time), vjust = 0, size = 3, color = "black", angle = 90) +
  facet_wrap(~ hemisphere, scales = "free_y") +
  theme_classic() +
  scale_color_manual(values = custom_colours) +
  scale_y_continuous(limits = c(-1.5, 1.5)) +
  scale_x_continuous(
    breaks = c(0, 5, 10, 15, 20, 25, 30, 35, 40, 45, 50, 55, 60, 65, 70, 75, 80, 85, 90, 95, 100, 105, 110, 115, 120, 125, 130, 135, 140, 145, 150, 155, 160, 165, 170),
    labels = NULL
  ) +
  labs(
    title = "STS",
    y = "Response magnitude",
    color = "Age group"
  ) +
  theme(
    strip.text = element_text(size = 16),
    strip.background = element_blank(),
    legend.position = "bottom",
    axis.title.x = element_text(size = 16),
    axis.title.y = element_text(size = 16),
    axis.text.x = element_text(size = 16),
    axis.text.y = element_text(size = 16),
    axis.ticks.x = element_blank(),
    axis.line.x = element_blank(),
    plot.title = element_text(hjust = 0.5, size = 16, face = "bold"),
    axis.line.y = element_line(linewidth = 0.8, color = "black"),
    legend.text = element_text(size = 16),
    legend.title = element_text(size = 16, face = "bold")
  )

Plot_STS <- Plot_STS + 
  geom_rect(data = events_TRs, 
            aes(xmin = onset, xmax = end, ymin = -1.5, ymax = 1.5, fill = trial_type), 
            alpha = 0.3, color = NA) +
  scale_fill_manual(values = c("faces" = "#F9B6C7", "scenes" = "#3B7D23")) +
  guides(fill = guide_legend(title = "Event type"), title.theme = element_text(face = "bold"))

## Get the 10th "faces" event (pink box)

pink_boxes <- events_TRs[events_TRs$trial_type == "faces",]
fifth_pink_box <- pink_boxes[5,]  #get the 10th pink box

## Adjust the y position for the asterisk to stay within the valid range

Plot_STS <- Plot_STS +
  geom_text(data = fifth_pink_box, 
            aes(x = (onset + end) / 2 - 1, y = 1.40, label = "*"),  # Adjust y to fit within plot limits
            size = 8, color = "black", fontface = "bold", vjust = 0)

print(Plot_STS)

# Save plots

ggsave(here("results/figures", "TCs_FFA.png"), plot = Plot_FFA, width = 15, height = 5, units = "in", dpi = 300)
ggsave(here("results/figures", "TCs_MMPFC.png"), plot = Plot_MMPFC, width = 15, height = 5, units = "in", dpi = 300)
ggsave(here("results/figures", "TCs_amygdala.png"), plot = Plot_amygdala, width = 15, height = 5, units = "in", dpi = 300)
ggsave(here("results/figures", "TCs_STS.png"), plot = Plot_STS, width = 15, height = 5, units = "in", dpi = 300)

```

Age and response magnitude of MMPFC and STS to face events

Histogram

```{r}

# Data wrangling

data_plot <- merge(long_data, participants[,c(1,3)], by="ID")
data_plot$ID <- as.factor(data_plot$ID)
data_plot$hemisphere <- as.factor(data_plot$hemisphere)
data_plot$region <- as.factor(data_plot$region)
data_plot_MMPFC <- subset(data_plot, region == "MMPFC")
data_plot_STS <- subset(data_plot, region == "STS")

# Colours

custom_colours <- c("#D34835", "#DDA86A", "#83AC66", "#87BACF", "#6989F3", "#652975")

# Make individual plots for MMPFC and STS and events with significant age associations

## General plotting function

generate_plot <- function(data, feature, subtitle, show_legend = TRUE, y_label = NULL, legend_pos = "bottom") {
  summary_data <- data %>%
    filter(!is.na(.data[[feature]]) & !is.na(AgeGroup)) %>%
    group_by(hemisphere, AgeGroup) %>%
    summarise(
      mean_value = mean(.data[[feature]], na.rm = TRUE),
      se_value   = sd(.data[[feature]], na.rm = TRUE) / sqrt(n()),
      .groups = "drop"
    )
  ggplot(summary_data, aes(x = as.factor(AgeGroup), y = mean_value, fill = as.factor(AgeGroup))) +
    geom_bar(stat = "identity", position = "stack", width = 1, alpha = 1) +
    geom_errorbar(aes(ymin = mean_value - se_value, ymax = mean_value + se_value), width = 0) +
    geom_hline(yintercept = 0, linetype = "solid", size = 1, color = "black") +
    scale_fill_manual(values = custom_colours) +
    labs(title = subtitle, x = "Age Group", y = y_label, fill = "Age Group") +
    facet_wrap(~hemisphere) +
    coord_cartesian(ylim = c(-1, 1)) +
    theme_classic() +
    theme(
      strip.text      = element_text(size = 14, face = "bold"),
      strip.background= element_blank(),
      legend.position = ifelse(show_legend, legend_pos, "right"),
      legend.text     = element_text(size = 16),
      legend.title    = element_text(size = 14, face = "bold"),
      axis.title      = element_text(size = 14, face = "bold"),
      axis.text       = element_text(size = 12),
      axis.title.x    = element_blank(),
      axis.text.x     = element_blank(),
      axis.ticks.x    = element_blank(),
      axis.line.x     = element_blank(),
      plot.title      = element_text(hjust = 0.5, size = 14, face = "bold"),
      axis.line.y     = element_line(size = 0.8, color = "black")
    )
}

## Generate plots with one reusable function

plot_F05 <- generate_plot(data_plot_MMPFC, "F05", "MMPFC response to F05", show_legend = TRUE, y_label = "Response magnitude")
plot_F10 <- generate_plot(data_plot_MMPFC, "F10", "STS response to F10", show_legend = TRUE)

## Combine plots with a common centered title and shared legend

final_plot <- (plot_F05 | plot_F10 ) +  
  plot_layout(ncol = 2, guides = "collect") +
  plot_annotation(
    title = ""
  ) &
  theme(
    legend.position = "bottom",
    legend.text = element_text(size = 12),
    legend.title = element_text(size = 12),
    plot.title = element_text(size = 14, hjust = 0.5, face = "bold")
  )

# Save plot

ggsave(here("results/figures", "Event_age_histogram.png"), plot = final_plot, width = 7, height = 5, units = "in", dpi = 300)

```


## Section III: Age effects on functional connectivity (Fx) between regions

### Read data

```{r}

# Covariates

participants <- read_tsv(here("raw_data/covariates", "participants.tsv"), col_names=TRUE)
colnames(participants)[which(names(participants) == "participant_id")] <- "ID"

## Remove the word "pixar" and trim extra whitespace

participants$ID <- gsub("[sub-pixar-]","", participants$ID)
participants$ID <- trimws(participants$ID)

# Motion

motion <- read_tsv(here("raw_data/motion", "outlier_info.tsv"), col_names=TRUE)
colnames(motion)[which(names(motion) == "subject")] <- "ID"

## Remove the word "pixar" and trim extra whitespace

motion$ID <- gsub("[sub-pixar-]","", motion$ID)
motion$ID <- trimws(motion$ID)

# Child fMRI variables

child_MRIvariables <- read_csv(here("processed_data", "child_MRIvariables.csv"), col_names=TRUE)

# Complete dataset

child_MRIvariables <- child_MRIvariables[,c(1, 202:229)]
child_MRIvariables <- merge(child_MRIvariables, participants[,c(1:2)], by="ID")
child_MRIvariables <- merge(child_MRIvariables, motion[,c(4,6)], by="ID")
child_MRIvariables <- child_MRIvariables %>%
  rename_with(~ sub("^zscored_", "", .x), starts_with("zscored_"))
child_MRIvariables[, c("Age", "MeanFD")] <- scale(child_MRIvariables[, c("Age", "MeanFD")])

```

### Plot correlations between regions by age

```{r}

# Read data

TCs_total <- read_csv(here("processed_data", "TCs_total.csv"), col_names = TRUE)
TCs_total$time <- as.numeric(as.character(TCs_total$time))
data_plot <- merge(TCs_total, participants[, c("ID", "AgeGroup")], by = "ID")
data_plot <- data_plot %>%
  filter(AgeGroup != "Adult")

# Rename timecourse columns

data_plot <- data_plot %>%
  rename_with(~ c("left amygdala", "right amygdala", "left FFA", "right FFA", "left MMPFC", "right MMPFC", "left STS", "right STS"),
              .cols = c("lamygdala", "ramygdala", "lFFA", "rFFA", "lMMPFC", "rMMPFC", "lSTS", "rSTS"))

# Define regions of interest

regions <- c("left amygdala", "right amygdala", "left FFA", "right FFA", "left MMPFC", "right MMPFC", "left STS", "right STS")

# Calculate correlation matrices per AgeGroup

age_groups <- unique(data_plot$AgeGroup)

correlation_by_agegroup <- map_df(age_groups, function(age) {
  group_data <- data_plot[data_plot$AgeGroup == age, ]

  seg1 <- group_data[group_data$time >= 1 & group_data$time <= 82, ]
  seg2 <- group_data[group_data$time >= 87 & group_data$time <= 168, ]

  mat1 <- cor(seg1[, regions], use = "pairwise.complete.obs")
  mat2 <- cor(seg2[, regions], use = "pairwise.complete.obs")
  mat_avg <- (mat1 + mat2) / 2

  # Replace amygdala correlation with full-time tc version
  amyg_cor <- cor(group_data[, c("left amygdala", "right amygdala")], use = "pairwise.complete.obs")[1, 2]
  mat_avg["left amygdala", "right amygdala"] <- amyg_cor
  mat_avg["right amygdala", "left amygdala"] <- amyg_cor

  tibble(AgeGroup = age, cor_matrix = list(mat_avg))
})

# Convert matrices to long format for ggplot2

data_plot <- correlation_by_agegroup %>%
  mutate(cor_matrix = map(cor_matrix, ~ melt(.x, varnames = c("Region1", "Region2")))) %>%
  unnest(cor_matrix)

data_plot <- data_plot %>%
  filter(Region1 != Region2)

# Order factor levels for consistent axis order

region_levels <- regions
data_plot$Region1 <- factor(data_plot$Region1, levels = region_levels)
data_plot$Region2 <- factor(data_plot$Region2, levels = region_levels)

# Identify upper triangle entries (for displaying numbers only)

data_plot <- data_plot %>%
  mutate(is_upper = as.numeric(Region1) < as.numeric(Region2))

# Plot heatmap

heatmap_plot <- ggplot(data_plot, aes(x = Region1, y = Region2, fill = value)) +
  geom_tile() +
  geom_tile(data = data_plot %>% filter(is_upper), fill = "white", color = NA) +
  geom_text(data = data_plot %>% filter(is_upper), 
    aes(label = sprintf("%.2f", value)), size = 2.8) + 
  facet_wrap(~ AgeGroup, nrow=1) + 
  scale_fill_gradient2(
    low = "#D34835", high = "#87BACF", mid = "white", 
    midpoint = 0, limit = c(-0.80, 0.80), 
    name = "Correlation",
    breaks = c(-0.80, -0.40, 0, 0.40, 0.80),
    labels = c("-0.80", "-0.40", "0.00", "0.40", "0.80")
  ) +
  theme_minimal() +
  labs(
    title = "",
    x = "",
    y = ""
  ) +
  theme(
    legend.position = "right",
    axis.text.x = element_text(angle = 45, hjust = 1, face = "bold", color = "darkgrey", size = 13),
    axis.text.y = element_text(face = "bold", color = "darkgrey", size = 13),
    strip.text = element_text(size = 14),
    plot.title = element_text(hjust = 0.5, size = 19),
    plot.title.position = "plot"
  )

# Display the plot

print(heatmap_plot)

# Save plot

ggsave(here("results/figures", "Fx_AgeGroup.png"), plot = heatmap_plot, width = 13, height = 4, units = "in", dpi = 300)

```

### Descriptive statistics: Mean FFA Fx values with ROIs (non-preregistered)

```{r}

# Read data

TCs_total <- read_csv(here("processed_data", "TCs_total.csv"), col_names = TRUE)
TCs_total$time <- as.numeric(as.character(TCs_total$time))
data_plot <- merge(TCs_total, participants[, c("ID", "AgeGroup")], by = "ID")
data_plot <- data_plot %>%
  filter(AgeGroup != "Adult")

# Rename ROI columns

data_plot <- data_plot %>%
  rename_with(
    ~ c("left amygdala", "right amygdala",
        "left FFA", "right FFA",
        "left MMPFC", "right MMPFC",
        "left STS", "right STS"),
    .cols = c("lamygdala", "ramygdala",
              "lFFA", "rFFA",
              "lMMPFC", "rMMPFC",
              "lSTS", "rSTS")
  )

# Define ROIs

regions <- c("left amygdala", "right amygdala",
             "left FFA", "right FFA",
             "left MMPFC", "right MMPFC",
             "left STS", "right STS")

# Compute subject-level correlation matrices

cor_subject <- data_plot %>%
  group_by(ID) %>%
  group_map(~ {
    
    seg1 <- .x %>% filter(time >= 1 & time <= 82)
    seg2 <- .x %>% filter(time >= 87 & time <= 168)
    
    mat1 <- cor(seg1[, regions], use = "pairwise.complete.obs")
    mat2 <- cor(seg2[, regions], use = "pairwise.complete.obs")
    mat_avg <- (mat1 + mat2) / 2
    
    # Replace amygdala correlation with full-time tc version
    amyg_cor <- cor(.x[, c("left amygdala", "right amygdala")], use = "pairwise.complete.obs")[1,2]
    mat_avg["left amygdala", "right amygdala"] <- amyg_cor
    mat_avg["right amygdala", "left amygdala"] <- amyg_cor
    
    mat_avg
  })

# Convert all matrices to long format

cor_long <- map_dfr(cor_subject, ~ as.data.frame(as.table(.x)) %>%
                       setNames(c("Region1", "Region2", "r")))

# Exclude diagonal (self-correlations)

cor_long <- cor_long %>%
  filter(Region1 != Region2)

# Filter for left/right FFA and compute summary + t-tests

cor_summary_with_t <- cor_long %>%
  filter(Region1 %in% c("right FFA", "left FFA")) %>%
  group_by(Region1, Region2) %>%
  summarise(
    mean_r = mean(r, na.rm = TRUE),
    sd_r   = sd(r, na.rm = TRUE),
    n      = n(),
    t_test = list(t.test(r, mu = 0, na.rm = TRUE)),
    .groups = "drop"
  ) %>%
  mutate(
    mean_sd = sprintf("%.2f (%.2f)", mean_r, sd_r),
    t_test  = map(t_test, broom::tidy)
  ) %>%
  unnest(t_test) %>%
  mutate(
    p.value = ifelse(p.value < 0.001,
                     format(p.value, scientific = TRUE, digits = 4),
                     sprintf("%.3f", p.value)),
    t_stat  = sprintf("%.2f", statistic),
    df      = sprintf("%.0f", parameter)
  ) %>%
  select(Region1, Region2, mean_sd, t_stat, df, p.value) %>%
  arrange(Region1, Region2)

# View final table

cor_summary_with_t

# Save the table

write_csv(cor_summary_with_t, here("results/RQ1", "FFA_fx_descriptive_table.csv"))

```


### Models (models including STS were not pre-registered)

#### Primary models 

Linear models

```{r}

model_rlFFA <- lm(fx_rFFA_lFFA ~ Age + MeanFD, data = child_MRIvariables)
summary(model_rlFFA)

```

Linear-mixed-effect models

```{r}

# Make long data for rest of the models: 

long_data <- child_MRIvariables %>%
  pivot_longer(
    cols = starts_with("fx_"),
    names_to = c("Region1", "Region2"),
    names_pattern = "fx_(.+)_(.+)",
    values_to = "zscored_value"
  )
long_data <- long_data %>%
  mutate(
    Hemisphere = ifelse(grepl("^r", Region2), "right", "left"),
    Region2 = sub("^[rl]", "", Region2)
  )

# Models with interaction effects 

## rFFA and r/lMMPFC

model_data <- long_data %>%
  filter(Region1 == "rFFA" & Region2 == "MMPFC")
model_rFFA_rlMMPFC <- lmer(
  zscored_value ~ Age*Hemisphere + MeanFD + (1 | ID),
  data = model_data
)
summary(model_rFFA_rlMMPFC) 

## rFFA and r/lamygdala

model_data <- long_data %>%
  filter(Region1 == "rFFA" & Region2 == "amygdala")
model_rFFA_rlamygdala <- lmer(
  zscored_value ~ Age*Hemisphere + MeanFD + (1 | ID),
  data = model_data
)
summary(model_rFFA_rlamygdala) 

## rFFA and r/lSTS

model_data <- long_data %>%
  filter(Region1 == "rFFA" & Region2 == "STS")
model_rFFA_rlSTS <- lmer(
  zscored_value ~ Age*Hemisphere + MeanFD + (1 | ID),
  data = model_data
)
summary(model_rFFA_rlSTS) 

# No interaction effects are significant except for rFFA and r/lMMPFC, so models are run without interaction effects except for rFFA and r/lMMPFC

## rFFA and r/lMMPFC

model_data <- long_data %>%
  filter(Region1 == "rFFA" & Region2 == "MMPFC")
model_rFFA_rlMMPFC <- lmer(
  zscored_value ~ Age*Hemisphere + MeanFD + (1 | ID),
  data = model_data
)
summary(model_rFFA_rlMMPFC)

## rFFA and r/lamygdala

model_data <- long_data %>%
  filter(Region1 == "rFFA" & Region2 == "amygdala")
model_rFFA_rlamygdala <- lmer(
  zscored_value ~ Age + Hemisphere + MeanFD + (1 | ID),
  data = model_data
)
summary(model_rFFA_rlamygdala)

## rFFA and r/lSTS

model_data <- long_data %>%
  filter(Region1 == "rFFA" & Region2 == "STS")
model_rFFA_rlSTS <- lmer(
  zscored_value ~ Age + Hemisphere + MeanFD + (1 | ID),
  data = model_data
)
summary(model_rFFA_rlSTS)

```

#### Secondary models 

Linear models

```{r}

# rlMMPFC

model_rlMMPFC <- lm(fx_lMMPFC_rMMPFC ~ Age + MeanFD, data = child_MRIvariables)
summary(model_rlMMPFC)

# rlamygdala

model_rlamygdala <- lm(fx_lamygdala_ramygdala ~ Age + MeanFD, data = child_MRIvariables)
summary(model_rlamygdala)

# rlSTS

model_rlSTS <- lm(fx_lSTS_rSTS ~ Age + MeanFD, data = child_MRIvariables)
summary(model_rlSTS)

```

Linear-mixed-effect models

```{r}

# Models with interaction effects 

## lFFA and r/lMMPFC

model_data <- long_data %>%
  filter(Region1 == "lFFA" & Region2 == "MMPFC")
model_lFFA_rlMMPFC <- lmer(
  zscored_value ~ Age*Hemisphere + MeanFD + (1 | ID),
  data = model_data
)
summary(model_lFFA_rlMMPFC)

## lFFA and r/lamygdala

model_data <- long_data %>%
  filter(Region1 == "lFFA" & Region2 == "amygdala")
model_lFFA_rlamygdala <- lmer(
  zscored_value ~ Age*Hemisphere + MeanFD + (1 | ID),
  data = model_data
)
summary(model_lFFA_rlamygdala)

## lFFA and r/lSTS

model_data <- long_data %>%
  filter(Region1 == "lFFA" & Region2 == "STS")
model_lFFA_rlSTS <- lmer(
  zscored_value ~ Age*Hemisphere + MeanFD + (1 | ID),
  data = model_data
)
summary(model_lFFA_rlSTS) 

## rMMPFC and r/lamygdala

model_data <- long_data %>%
  filter(Region1 == "rMMPFC" & Region2 == "amygdala")
model_rMMPFC_rlamygdala <- lmer(
  zscored_value ~ Age*Hemisphere + MeanFD + (1 | ID),
  data = model_data
)
summary(model_rMMPFC_rlamygdala)

## rMMPFC and r/lSTS

model_data <- long_data %>%
  filter(Region1 == "rMMPFC" & Region2 == "STS")
model_rMMPFC_rlSTS <- lmer(
  zscored_value ~ Age*Hemisphere + MeanFD + (1 | ID),
  data = model_data
)
summary(model_rMMPFC_rlSTS)

## lMMPFC and r/lamygdala

model_data <- long_data %>%
  filter(Region1 == "lMMPFC" & Region2 == "amygdala")
model_lMMPFC_rlamygdala <- lmer(
  zscored_value ~ Age*Hemisphere + MeanFD + (1 | ID),
  data = model_data
)
summary(model_lMMPFC_rlamygdala)

## lMMPFC and r/lSTS

model_data <- long_data %>%
  filter(Region1 == "lMMPFC" & Region2 == "STS")
model_lMMPFC_rlSTS <- lmer(
  zscored_value ~ Age*Hemisphere + MeanFD + (1 | ID),
  data = model_data
)
summary(model_lMMPFC_rlSTS)

## ramygdala and r/lSTS

model_data <- long_data %>%
  filter(Region1 == "ramygdala" & Region2 == "STS")
model_ramygdala_rlSTS <- lmer(
  zscored_value ~ Age*Hemisphere + MeanFD + (1 | ID),
  data = model_data
)
summary(model_ramygdala_rlSTS)

## lamygdala and r/lSTS

model_data <- long_data %>%
  filter(Region1 == "lamygdala" & Region2 == "STS")
model_lamygdala_rlSTS <- lmer(
  zscored_value ~ Age*Hemisphere + MeanFD + (1 | ID),
  data = model_data
)
summary(model_lamygdala_rlSTS)

# No interaction effects are significant, so models are run without interaction effects 

## lFFA and r/lMMPFC

model_data <- long_data %>%
  filter(Region1 == "lFFA" & Region2 == "MMPFC")
model_lFFA_rlMMPFC <- lmer(
  zscored_value ~ Age + Hemisphere + MeanFD + (1 | ID),
  data = model_data
)
summary(model_lFFA_rlMMPFC)

## lFFA and r/lamygdala

model_data <- long_data %>%
  filter(Region1 == "lFFA" & Region2 == "amygdala")
model_lFFA_rlamygdala <- lmer(
  zscored_value ~ Age + Hemisphere + MeanFD + (1 | ID),
  data = model_data
)
summary(model_lFFA_rlamygdala)

## lFFA and r/lSTS

model_data <- long_data %>%
  filter(Region1 == "lFFA" & Region2 == "STS")
model_lFFA_rlSTS <- lmer(
  zscored_value ~ Age + Hemisphere + MeanFD + (1 | ID),
  data = model_data
)
summary(model_lFFA_rlSTS)

## rMMPFC and r/lamygdala

model_data <- long_data %>%
  filter(Region1 == "rMMPFC" & Region2 == "amygdala")
model_rMMPFC_rlamygdala <- lmer(
  zscored_value ~ Age + Hemisphere + MeanFD + (1 | ID),
  data = model_data
)
summary(model_rMMPFC_rlamygdala)

## rMMPFC and r/lSTS

model_data <- long_data %>%
  filter(Region1 == "rMMPFC" & Region2 == "STS")
model_rMMPFC_rlSTS <- lmer(
  zscored_value ~ Age + Hemisphere + MeanFD + (1 | ID),
  data = model_data
)
summary(model_rMMPFC_rlSTS)

## lMMPFC and r/lamygdala

model_data <- long_data %>%
  filter(Region1 == "lMMPFC" & Region2 == "amygdala")
model_lMMPFC_rlamygdala <- lmer(
  zscored_value ~ Age + Hemisphere + MeanFD + (1 | ID),
  data = model_data
)
summary(model_lMMPFC_rlamygdala)

## lMMPFC and r/lSTS

model_data <- long_data %>%
  filter(Region1 == "lMMPFC" & Region2 == "STS")
model_lMMPFC_rlSTS <- lmer(
  zscored_value ~ Age + Hemisphere + MeanFD + (1 | ID),
  data = model_data
)
summary(model_lMMPFC_rlSTS)

## ramygdala and r/lSTS

model_data <- long_data %>%
  filter(Region1 == "ramygdala" & Region2 == "STS")
model_ramygdala_rlSTS <- lmer(
  zscored_value ~ Age + Hemisphere + MeanFD + (1 | ID),
  data = model_data
)
summary(model_ramygdala_rlSTS)

## lamygdala and r/lSTS

model_data <- long_data %>%
  filter(Region1 == "lamygdala" & Region2 == "STS")
model_lamygdala_rlSTS <- lmer(
  zscored_value ~ Age + Hemisphere + MeanFD + (1 | ID),
  data = model_data
)
summary(model_lamygdala_rlSTS)

```

Save models

```{r}

# Create tidy summaries of all models

## Primary models

model_rlFFA_summary <- tidy(model_rlFFA) %>%
  mutate(Model = "rlFFA", Label = "Primary")

model_rFFA_rlMMPFC_summary <- tidy(model_rFFA_rlMMPFC, effects = "fixed") %>%
  mutate(Model = "rFFA_rlMMPFC", Label = "Primary")

model_rFFA_rlamygdala_summary <- tidy(model_rFFA_rlamygdala, effects = "fixed") %>%
  mutate(Model = "rFFA_rlamygdala", Label = "Primary")

model_rFFA_rlSTS_summary <- tidy(model_rFFA_rlSTS, effects = "fixed") %>%
  mutate(Model = "rFFA_rlSTS", Label = "Primary")

## Secondary models

model_lFFA_rlMMPFC_summary <- tidy(model_lFFA_rlMMPFC, effects = "fixed") %>%
  mutate(Model = "lFFA_rlMMPFC", Label = "Secondary")

model_lFFA_rlamygdala_summary <- tidy(model_lFFA_rlamygdala, effects = "fixed") %>%
  mutate(Model = "lFFA_rlamygdala", Label = "Secondary")

model_lFFA_rlSTS_summary <- tidy(model_lFFA_rlSTS, effects = "fixed") %>%
  mutate(Model = "lFFA_rlSTS", Label = "Secondary")

model_rlMMPFC_summary <- tidy(model_rlMMPFC) %>%
  mutate(Model = "rlMMPFC", Label = "Secondary")

model_rMMPFC_rlamygdala_summary <- tidy(model_rMMPFC_rlamygdala, effects = "fixed") %>%
  mutate(Model = "rMMPFC_rlamygdala", Label = "Secondary")

model_rMMPFC_rlSTS_summary <- tidy(model_rMMPFC_rlSTS, effects = "fixed") %>%
  mutate(Model = "rMMPFC_rlSTS", Label = "Secondary")

model_lMMPFC_rlamygdala_summary <- tidy(model_lMMPFC_rlamygdala, effects = "fixed") %>%
  mutate(Model = "lMMPFC_rlamygdala", Label = "Secondary")

model_lMMPFC_rlSTS_summary <- tidy(model_lMMPFC_rlSTS, effects = "fixed") %>%
  mutate(Model = "lMMPFC_rlSTS", Label = "Secondary")

model_rlamygdala_summary <- tidy(model_rlamygdala, effects = "fixed") %>%
  mutate(Model = "rlamygdala", Label = "Secondary")

model_ramygdala_rlSTS_summary <- tidy(model_ramygdala_rlSTS, effects = "fixed") %>%
  mutate(Model = "ramygdala_rlSTS", Label = "Secondary")

model_lamygdala_rlSTS_summary <- tidy(model_lamygdala_rlSTS, effects = "fixed") %>%
  mutate(Model = "lamygdala_rlSTS", Label = "Secondary")

model_rlSTS_summary <- tidy(model_rlSTS, effects = "fixed") %>%
  mutate(Model = "rlSTS", Label = "Secondary")

# Combine all summaries into one data frame

all_model_summaries <- bind_rows(
  model_rlFFA_summary,
  model_rFFA_rlMMPFC_summary,
  model_rFFA_rlamygdala_summary,
  model_rFFA_rlSTS_summary,
  model_lFFA_rlMMPFC_summary,
  model_lFFA_rlamygdala_summary,
  model_lFFA_rlSTS_summary,
  model_rlMMPFC_summary,
  model_lMMPFC_rlamygdala_summary,
  model_lMMPFC_rlSTS_summary,
  model_rMMPFC_rlamygdala_summary,
  model_rMMPFC_rlSTS_summary,
  model_rlamygdala_summary,
  model_lamygdala_rlSTS_summary,
  model_ramygdala_rlSTS_summary,
  model_rlSTS_summary
) %>%
  mutate(
    estimate = round(estimate, 2),
    std.error = round(std.error, 2),
    statistic = round(statistic, 2),
    df = round(df, 0),
    p.value = if_else(
      p.value < 0.001,
      format(p.value, scientific = TRUE, digits = 4),
      sprintf("%.3f", p.value)
    ))

# Save the combined summaries to a CSV file

write.csv(all_model_summaries, here("results/RQ1", "Fx_age.csv"), row.names = FALSE)

```

### Model plots

```{r}

# Data wrangling

data_plot <- read_csv(here("processed_data", "child_MRIvariables.csv"), col_names=TRUE)
data_plot <- data_plot[,c(1, 202:229)]
data_plot <- merge(data_plot, participants[,c(1:2)], by="ID")
data_plot <- merge(data_plot, motion[,c(4,6)], by="ID")
data_plot <- data_plot %>%
  rename_with(~ sub("^zscored_", "", .x), starts_with("zscored_"))
data_plot <- data_plot %>%
  pivot_longer(
    cols = starts_with("fx_"),
    names_to = c("Region1", "Region2"),
    names_pattern = "fx_(.+)_(.+)",
    values_to = "zscored_value"
  )
data_plot <- data_plot %>%
  mutate(
    Hemisphere = ifelse(grepl("^r", Region2), "right", "left"),
    Region2 = sub("^[rl]", "", Region2)
  )
data_plot_rFFA_MMPFC <- data_plot %>%
  filter(Region2 == "MMPFC", Region1 == "rFFA")
data_plot_lFFA_MMPFC <- data_plot %>%
  filter(Region2 == "MMPFC", Region1 == "lFFA")
data_plot_rFFA_amygdala <- data_plot %>%
  filter(Region2 == "amygdala", Region1 == "rFFA")
data_plot_lFFA_amygdala <- data_plot %>%
  filter(Region2 == "amygdala", Region1 == "lFFA")
data_plot_rFFA_STS <- data_plot %>%
  filter(Region2 == "STS", Region1 == "rFFA")
data_plot_lFFA_STS <- data_plot %>%
  filter(Region2 == "STS", Region1 == "lFFA")

# Colours

custom_colours_amygdala <- c("#E1AA9F", "#D34835")
custom_colours_MMPFC <- c("#87BACF", "#578CAD")
custom_colours_FFA <- c("#C39EDA", "#652975")
custom_colours_STS <- c("#FFF865", "#FFCE1B")


# Define a base theme to avoid repetition

base_theme <- theme_minimal() +
  theme(
    strip.text = element_text(size = 14, face = "bold"),
    strip.background = element_blank(),
    axis.line.x = element_blank(),
    axis.text = element_text(size = 12),
    axis.title = element_text(size = 14, face = "bold"),
    plot.title = element_text(size = 14, hjust = 0.5, face = "bold"),
    legend.text = element_text(size = 12),
    legend.title = element_text(size = 12, face = "bold")
  )

# Function to create ggplots efficiently

create_plot <- function(data, color_values, legend_title, x_label = "", y_label = "", legend_position = "none", remove_y_axis_labels = FALSE) {
  plot <- ggplot(data, aes(x = Age, y = zscored_value, color = Hemisphere)) +
    geom_point(alpha = 0.8, size = 2.8, shape = 19) +  
    geom_smooth(method = "lm", se = FALSE, linetype = "solid", linewidth = 2) +  
    scale_color_manual(values = color_values) +  
    labs(x = x_label, y = y_label, color = legend_title) +
    base_theme +
    theme(legend.position = legend_position) +
    coord_cartesian(ylim = c(-4, 3)) + 
    scale_x_continuous(breaks = c(3, 6, 9, 12))
  
  if (remove_y_axis_labels) {
    plot <- plot + theme(
      axis.title.y = element_blank(),
      axis.text.y = element_blank()
    )
  }

  return(plot)
}

# Create all plots using the function

plot_lFFA_MMPFC <- create_plot(data_plot_lFFA_MMPFC, custom_colours_MMPFC, "MMPFC Hemisphere", "", "Functional connectivity between\n left FFA and region")
plot_lFFA_amygdala <- create_plot(data_plot_lFFA_amygdala, custom_colours_amygdala, "Amygdala Hemisphere", "Age", legend_position = "bottom", remove_y_axis_labels = TRUE)
plot_lFFA_STS <- create_plot(data_plot_lFFA_STS, custom_colours_STS, "STS Hemisphere", "", legend_position = "bottom", remove_y_axis_labels = TRUE)
plot_rFFA_MMPFC <- create_plot(data_plot_rFFA_MMPFC, custom_colours_MMPFC, "MMPFC Hemisphere", "", "Functional connectivity between\n right FFA and region", legend_position = "bottom") +
  annotate(
    "text",
    x = Inf, y = -Inf,                        # bottom right corner
    label = "Age x Hemisphere (right) effect: \nβ(SE)=0.16(0.07), p=0.016",    # your annotation
    hjust = 1.05,      # slightly >1 for proper right alignment
    vjust = -0.5,      # nudges text up from bottom
    size = 4,
    color = "black"
)
plot_rFFA_amygdala <- create_plot(data_plot_rFFA_amygdala, custom_colours_amygdala, "Amygdala Hemisphere", "Age", remove_y_axis_labels = TRUE)
plot_rFFA_STS <- create_plot(data_plot_rFFA_STS, custom_colours_STS, "STS Hemisphere", "", remove_y_axis_labels = TRUE)

# Combine plots into a single row

fx_rFFA_age <- (
  plot_rFFA_MMPFC | plot_rFFA_amygdala | plot_rFFA_STS
) +
  plot_layout(
    ncol = 3, 
    widths = rep(1, 3),
    guides = "collect"
  ) +
  plot_annotation(
    title = "Functional Connectivity Across Age",
    theme = theme(
      plot.title = element_text(size = 14, hjust = 0.5, face = "bold")
    )
  ) &
  theme(legend.position = "bottom")
fx_rFFA_age

fx_lFFA_age <- (
  plot_lFFA_MMPFC | plot_lFFA_amygdala | plot_lFFA_STS ) +
  plot_layout(
    ncol = 3, 
    widths = rep(1, 3),
    guides = "collect"
  ) +
  plot_annotation(
    title = "Functional Connectivity Across Age",
    theme = theme(
      plot.title = element_text(size = 14, hjust = 0.5, face = "bold")
    )
  ) &
  theme(legend.position = "bottom")
fx_lFFA_age

# Save plots

ggsave(here("results/figures", "Fx_rFFA_age.png"), plot = fx_rFFA_age, width = 10, height = 5, units = "in", dpi = 300)
ggsave(here("results/figures", "Fx_lFFA_age.png"), plot = fx_lFFA_age, width = 10, height = 5, units = "in", dpi = 300)

```


## Section IV: Age effects on lateralisation of face response (non-preregistered)

### Descriptive statistics: Mean LI values

```{r}

# Read data

child_LI <- read_csv(here("processed_data", "child_MRIvariables.csv"), col_names=TRUE)
child_LI <- child_LI[,c(1, 230:231)]

# Define variables to analyse

li_columns <- c("lateralisation_index_0.05", "lateralisation_index_0.1")

# Compute sunnary + t-tests

li_summary <- li_columns %>%
  lapply(function(col_name) {
    values <- child_LI[[col_name]]
    
    # Compute mean and SD
    mean_val <- mean(values, na.rm = TRUE)
    sd_val   <- sd(values, na.rm = TRUE)
    
    # One-sample t-test against 0
    t_test <- t.test(values, mu = 0, na.rm = TRUE)
    
    # Format p-value
    p_val <- ifelse(t_test$p.value < 0.001,
                    format(t_test$p.value, scientific = TRUE, digits = 3),
                    sprintf("%.3f", t_test$p.value))
    
    # Create output row
    tibble(
      Measure   = col_name,
      mean_sd   = sprintf("%.2f (%.2f)", mean_val, sd_val),
      t_stat    = sprintf("%.2f", t_test$statistic),
      df        = sprintf("%.0f", t_test$parameter),
      p_value   = p_val
    )
  }) %>%
  bind_rows()  # Combine into a single table

# View final table

li_summary

# Save the table

write_csv(li_summary, here("results/RQ1", "LI_descriptive_table.csv"))

```

### Age effects on lateralisation of face response 

#### Read data

```{r}

# Covariates

participants <- read_tsv(here("raw_data/covariates", "participants.tsv"), col_names=TRUE)
colnames(participants)[which(names(participants) == "participant_id")] <- "ID"

## Remove the word "pixar" and trim extra whitespace

participants$ID <- gsub("[sub-pixar-]","", participants$ID)
participants$ID <- trimws(participants$ID)

# Motion

motion <- read_tsv(here("raw_data/motion", "outlier_info.tsv"), col_names=TRUE)
colnames(motion)[which(names(motion) == "subject")] <- "ID"

## Remove the word "pixar" and trim extra whitespace

motion$ID <- gsub("[sub-pixar-]","", motion$ID)
motion$ID <- trimws(motion$ID)

# Child fMRI variables

child_LI <- read_csv(here("processed_data", "child_MRIvariables.csv"), col_names=TRUE)

# Complete dataset

child_LI <- child_LI[,c(1, 230:231)]
child_LI <- merge(child_LI, participants[,c(1:2)], by="ID")
child_LI <- merge(child_LI, motion[,c(4,6)], by="ID")
child_LI <- child_LI %>%
  rename_with(~ sub("^zscored_", "", .x), starts_with("zscored_"))
child_LI[, c("lateralisation_index_0.05","lateralisation_index_0.1", "Age", "MeanFD")] <- scale(child_LI[, c("lateralisation_index_0.05","lateralisation_index_0.1", "Age", "MeanFD")])

```

#### Models

##### Threshold 0.05

```{r}

model_LI_0.05_age <- lm(lateralisation_index_0.05 ~ Age + MeanFD, data = child_LI)
summary_LI_0.05_age <- tidy(model_LI_0.05_age)

```

##### Threshold 0.1

```{r}

model_LI_0.1_age <- lm(lateralisation_index_0.1 ~ Age + MeanFD, data = child_LI)
summary_LI_0.1_age <- tidy(model_LI_0.1_age)

```

##### Save models

```{r}

all_summaries <- bind_rows(
  summary_LI_0.05_age %>% mutate(threshold = "0.05"),
  summary_LI_0.1_age %>% mutate(threshold = "0.1")
) %>%
  mutate(
    p.value    = as.numeric(p.value),                                   # ensure numeric
    estimate   = round(estimate, 2),
    std.error  = round(std.error, 2),
    statistic  = round(statistic, 2),
    p.value    = if_else(
      p.value < 0.001,
      format(p.value, scientific = TRUE, digits = 4),
      sprintf("%.3f", p.value)
    )
  )

write.csv(all_summaries, here("results/RQ1", "LI_age.csv"), row.names = FALSE)

```

#### Model plots

LI and age

```{r}

# Read data

child_LI <- read_csv(here("processed_data", "child_MRIvariables.csv"), col_names=TRUE)
child_LI <- child_LI[,c(1, 230:231)]
child_LI <- merge(child_LI, participants[,c(1:2)], by="ID")
child_LI <- merge(child_LI, motion[,c(4,6)], by="ID")
child_LI <- child_LI %>%
  rename_with(~ sub("^zscored_", "", .x), starts_with("zscored_"))

# LI of children at threshold p<0.05

## Plot
LI_age_children <- ggplot(
  child_LI,
  aes(x = Age, y = lateralisation_index_0.05)
) +
  geom_point(color = "#9463A7", alpha = 0.8, size = 2.9, shape = 19) +
  geom_smooth(method = "lm", se = FALSE, color = "#9463A7", linewidth = 2) +
  labs(
    title = "Lateralisation Index of FFA Across Age",
    x = "Age",
    y = "Lateralisation Index (p<0.05)"
  ) +
  theme_minimal() +
  theme(
    plot.title   = element_text(size = 16, face = "bold", hjust = 0.5),
    axis.title.x = element_text(size = 16, face = "bold"),
    axis.title.y = element_text(size = 16, face = "bold"),
    axis.text    = element_text(size = 12)
  )

ggsave(here("results/figures", "LI_0.05_age.png"), plot = LI_age_children, width = 5, height = 5, units = "in", dpi = 300)

# LI of children at threshold p<0.01

LI_age_children <- ggplot(
  child_LI,
  aes(x = Age, y = lateralisation_index_0.1)
) +
  geom_point(color = "#9463A7", alpha = 0.8, size = 2.9, shape = 19) +
  geom_smooth(method = "lm", se = FALSE, color = "#9463A7", linewidth = 2) +
  labs(
    title = "Lateralisation Index of FFA Across Age",
    x = "Age",
    y = "Lateralisation Index (p<0.10)"
  ) +
  theme_minimal() +
  theme(
    plot.title   = element_text(size = 16, face = "bold", hjust = 0.5),
    axis.title.x = element_text(size = 16, face = "bold"),
    axis.title.y = element_text(size = 16, face = "bold"),
    axis.text    = element_text(size = 12)
  )

ggsave(here("results/figures", "LI_0.1_age.png"), plot = LI_age_children, width = 5, height = 5, units = "in", dpi = 300)

```


```{r}

markdownToHTML("FRIC_DevelopmentalChange.Rmd",output ="FRIC_DevelopmentalChange.html")

```

