---
title: "FRIC_FunctionalMaturityFFA"
author: "LJS"
date: "2025-01-17"
output: html_document
---

# Libraries 

```{r setup, include=FALSE}

library("rlang") #toolbox
library("readr") #toolbox
library("dplyr") #data manipulation
library("here") #toolbox
library("tidyverse") #data manipulation
library("ggpubr") #plotting
library("tidytext") #data manipulation
library("knitr") #rmarkdown
library("htmltools") #rmarkdown
library("markdown") #rmarkdown
library("httpuv") #rmarkdown
library("NCmisc") #toolbox
library("stringr") #data manipulation
library("reshape") #data manipulation
library("reshape2") #data manipulation
library("lme4") #regression models
library("lmerTest") #regression models
library("broom.mixed") #save regression results
library("car") #VIF
library("gridExtra") #combine plots
library("patchwork") #combine plots
library("broom") #tidying model summaries

```


# Face Responses in Childhood (FRIC) project

This script tests whether functional connectivity to/functional maturity of MMPFC, STS and amygdala correlates with functional maturity of FFA.

Structure:
- Section I: Functional connectivity effects on functional maturity of right or left FFA
- Section II: Functional maturity of MMPFC/amygdala/STS effects on functional maturity of right or left FFA (non-preregistered)
- Section III: Correlations between fMRI variables


## Section I: Functional connectivity effects on functional maturity of right or left FFA

### Read data

```{r}

# Covariates

participants <- read_tsv(here("raw_data/covariates", "participants.tsv"), col_names=TRUE)
colnames(participants)[which(names(participants) == "participant_id")] <- "ID"

## Remove the word "pixar" and trim extra whitespace

participants$ID <- gsub("[sub-pixar-]","", participants$ID)
participants$ID <- trimws(participants$ID)

# Motion

motion <- read_tsv(here("raw_data/motion", "outlier_info.tsv"), col_names=TRUE)
colnames(motion)[which(names(motion) == "subject")] <- "ID"

## Remove the word "pixar" and trim extra whitespace

motion$ID <- gsub("[sub-pixar-]","", motion$ID)
motion$ID <- trimws(motion$ID)

# Child fMRI variables

child_MRIvariables <- read_csv(here("processed_data", "child_MRIvariables.csv"), col_names=TRUE)

# Complete dataset

child_MRIvariables <- child_MRIvariables[,c(1:9, 202:229)]
child_MRIvariables <- merge(child_MRIvariables, participants[,c(1:2)], by="ID")
child_MRIvariables <- merge(child_MRIvariables, motion[,c(4,6)], by="ID")
child_MRIvariables <- child_MRIvariables %>%
  rename_with(~ sub("^zscored_", "", .x), starts_with("zscored_"))
child_MRIvariables[, c("Age", "MeanFD")] <- scale(child_MRIvariables[, c("Age", "MeanFD")])

```

### Models (models including STS were not pre-registered)

Right FFA

```{r}

long_data <- child_MRIvariables

# Filter long data

long_data_amygdala <- long_data %>%
  select(
    ID,
    fm_rFFA,
    fx_rFFA_ramygdala,
    fx_rFFA_lamygdala,
    Age,
    MeanFD
  )
long_data_MMPFC <- long_data %>%
  select(
    ID,
    fm_rFFA,
    fx_rFFA_rMMPFC,
    fx_rFFA_lMMPFC,
    Age,
    MeanFD
  )

long_data_STS <- long_data %>%
  select(
    ID,
    fm_rFFA,
    fx_rFFA_rSTS,
    fx_rFFA_lSTS,
    Age,
    MeanFD
  )

# Reshape the data and adjust columns

long_data_amygdala <- long_data_amygdala %>%
  ## Pivot the data into a long format with "Right" and "Left" hemispheres
  pivot_longer(
    cols = c(fx_rFFA_ramygdala, fx_rFFA_lamygdala),
    names_to = "region",
    values_to = "fx_rFFA_rlamygdala"
  ) %>%
  ## Create Hemisphere column based on the region name
  mutate(
    Hemisphere = case_when(
      region == "fx_rFFA_ramygdala" ~ "Right",
      region == "fx_rFFA_lamygdala" ~ "Left",
      TRUE ~ NA_character_
    )
  ) %>%
  ## Keep only relevant columns
  select(ID, fm_rFFA, fx_rFFA_rlamygdala, Age, MeanFD, Hemisphere)
long_data_MMPFC <- long_data_MMPFC %>%
  ## Pivot the data into a long format with "Right" and "Left" hemispheres
  pivot_longer(
    cols = c(fx_rFFA_rMMPFC, fx_rFFA_lMMPFC),
    names_to = "region",
    values_to = "fx_rFFA_rlMMPFC"
  ) %>%
  ## Create Hemisphere column based on the region name
  mutate(
    Hemisphere = case_when(
      region == "fx_rFFA_rMMPFC" ~ "Right",
      region == "fx_rFFA_lMMPFC" ~ "Left",
      TRUE ~ NA_character_
    )
  ) %>%
  ## Keep only relevant columns
  select(ID, fm_rFFA, fx_rFFA_rlMMPFC, Age, MeanFD, Hemisphere)
long_data_STS <- long_data_STS %>%
  ## Pivot the data into a long format with "Right" and "Left" hemispheres
  pivot_longer(
    cols = c(fx_rFFA_rSTS, fx_rFFA_lSTS),
    names_to = "region",
    values_to = "fx_rFFA_rlSTS"
  ) %>%
  ## Create Hemisphere column based on the region name
  mutate(
    Hemisphere = case_when(
      region == "fx_rFFA_rSTS" ~ "Right",
      region == "fx_rFFA_lSTS" ~ "Left",
      TRUE ~ NA_character_
    )
  ) %>%
  ## Keep only relevant columns
  select(ID, fm_rFFA, fx_rFFA_rlSTS, Age, MeanFD, Hemisphere)

long_data_amygdala_selected <- long_data_amygdala %>%
  select(ID, Hemisphere, fx_rFFA_rlamygdala)  # Include only relevant columns
long_data_STS_selected <- long_data_STS %>%
  select(ID, Hemisphere, fx_rFFA_rlSTS)  # Include only relevant columns
model_data <- merge(long_data_amygdala_selected, long_data_MMPFC, by = c("ID", "Hemisphere"))
model_data <- merge(model_data, long_data_STS_selected, by = c("ID", "Hemisphere"))
model_data$Hemisphere <- as.factor(model_data$Hemisphere)

# Models

model_rFFA_fm <- lmer(fm_rFFA ~ fx_rFFA_rlMMPFC*Hemisphere*Age + fx_rFFA_rlamygdala*Hemisphere*Age + fx_rFFA_rlSTS*Hemisphere*Age + MeanFD + (1| ID), data = model_data)
summary(model_rFFA_fm)

```

Left FFA

```{r}

long_data <- child_MRIvariables

# Filter long data

long_data_amygdala <- long_data %>%
  select(
    ID,
    fm_lFFA,
    fx_lFFA_ramygdala,
    fx_lFFA_lamygdala,
    Age,
    MeanFD
  )
long_data_MMPFC <- long_data %>%
  select(
    ID,
    fm_lFFA,
    fx_lFFA_rMMPFC,
    fx_lFFA_lMMPFC,
    Age,
    MeanFD
  )

long_data_STS <- long_data %>%
  select(
    ID,
    fm_lFFA,
    fx_lFFA_rSTS,
    fx_lFFA_lSTS,
    Age,
    MeanFD
  )

# Reshape the data and adjust columns

long_data_amygdala <- long_data_amygdala %>%
  ## Pivot the data into a long format with "Right" and "Left" hemispheres
  pivot_longer(
    cols = c(fx_lFFA_ramygdala, fx_lFFA_lamygdala),
    names_to = "region",
    values_to = "fx_lFFA_rlamygdala"
  ) %>%
  ## Create Hemisphere column based on the region name
  mutate(
    Hemisphere = case_when(
      region == "fx_lFFA_ramygdala" ~ "Right",
      region == "fx_lFFA_lamygdala" ~ "Left",
      TRUE ~ NA_character_
    )
  ) %>%
  ## Keep only relevant columns
  select(ID, fm_lFFA, fx_lFFA_rlamygdala, Age, MeanFD, Hemisphere)
long_data_MMPFC <- long_data_MMPFC %>%
  ## Pivot the data into a long format with "Right" and "Left" hemispheres
  pivot_longer(
    cols = c(fx_lFFA_rMMPFC, fx_lFFA_lMMPFC),
    names_to = "region",
    values_to = "fx_lFFA_rlMMPFC"
  ) %>%
  ## Create Hemisphere column based on the region name
  mutate(
    Hemisphere = case_when(
      region == "fx_lFFA_rMMPFC" ~ "Right",
      region == "fx_lFFA_lMMPFC" ~ "Left",
      TRUE ~ NA_character_
    )
  ) %>%
  ## Keep only relevant columns
  select(ID, fm_lFFA, fx_lFFA_rlMMPFC, Age, MeanFD, Hemisphere)
long_data_STS <- long_data_STS %>%
  ## Pivot the data into a long format with "Right" and "Left" hemispheres
  pivot_longer(
    cols = c(fx_lFFA_rSTS, fx_lFFA_lSTS),
    names_to = "region",
    values_to = "fx_lFFA_rlSTS"
  ) %>%
  ## Create Hemisphere column based on the region name
  mutate(
    Hemisphere = case_when(
      region == "fx_lFFA_rSTS" ~ "Right",
      region == "fx_lFFA_lSTS" ~ "Left",
      TRUE ~ NA_character_
    )
  ) %>%
  ## Keep only relevant columns
  select(ID, fm_lFFA, fx_lFFA_rlSTS, Age, MeanFD, Hemisphere)

long_data_amygdala_selected <- long_data_amygdala %>%
  select(ID, Hemisphere, fx_lFFA_rlamygdala)  # Include only relevant columns
long_data_STS_selected <- long_data_STS %>%
  select(ID, Hemisphere, fx_lFFA_rlSTS)  # Include only relevant columns
model_data <- merge(long_data_amygdala_selected, long_data_MMPFC, by = c("ID", "Hemisphere"))
model_data <- merge(model_data, long_data_STS_selected, by = c("ID", "Hemisphere"))
model_data$Hemisphere <- as.factor(model_data$Hemisphere)

# Models

model_lFFA_fm <- lmer(fm_lFFA ~ fx_lFFA_rlMMPFC*Hemisphere*Age + fx_lFFA_rlamygdala*Hemisphere*Age + fx_lFFA_rlSTS*Hemisphere*Age + MeanFD + (1| ID), data = model_data)
summary(model_lFFA_fm)

```

Our preregistered linear mixed-effects models did not converge, likely due to the repeated-measures factor being assigned to the independent variable instead of the dependent variable. To test the same associations, we instead reversed the independent and dependent variables and ran separate linear mixed-effects models for each ROI pair.

### Alternative linear mixed effects models (non-preregistered)

Right FFA

```{r}

# Data wrangling

long_data <- child_MRIvariables

long_data_amygdala <- long_data %>%
  select(
    ID,
    fm_rFFA,
    fx_rFFA_ramygdala,
    fx_rFFA_lamygdala,
    Age,
    MeanFD
  )
long_data_MMPFC <- long_data %>%
  select(
    ID,
    fm_rFFA,
    fx_rFFA_rMMPFC,
    fx_rFFA_lMMPFC,
    Age,
    MeanFD
  )

long_data_STS <- long_data %>%
  select(
    ID,
    fm_rFFA,
    fx_rFFA_rSTS,
    fx_rFFA_lSTS,
    Age,
    MeanFD
  )

## Reshape the data and adjust columns

long_data_amygdala <- long_data_amygdala %>%
  ## Pivot the data into a long format with "Right" and "Left" hemispheres
  pivot_longer(
    cols = c(fx_rFFA_ramygdala, fx_rFFA_lamygdala),
    names_to = "region",
    values_to = "fx_rFFA_rlamygdala"
  ) %>%
  ## Create Hemisphere column based on the region name
  mutate(
    Hemisphere = case_when(
      region == "fx_rFFA_ramygdala" ~ "Right",
      region == "fx_rFFA_lamygdala" ~ "Left",
      TRUE ~ NA_character_
    )
  ) %>%
  select(ID, fm_rFFA, fx_rFFA_rlamygdala, Age, MeanFD, Hemisphere)

long_data_MMPFC <- long_data_MMPFC %>%
  pivot_longer(
    cols = c(fx_rFFA_rMMPFC, fx_rFFA_lMMPFC),
    names_to = "region",
    values_to = "fx_rFFA_rlMMPFC"
  ) %>%
  mutate(
    Hemisphere = case_when(
      region == "fx_rFFA_rMMPFC" ~ "Right",
      region == "fx_rFFA_lMMPFC" ~ "Left",
      TRUE ~ NA_character_
    )
  ) %>%
  select(ID, fm_rFFA, fx_rFFA_rlMMPFC, Age, MeanFD, Hemisphere)

long_data_STS <- long_data_STS %>%
  pivot_longer(
    cols = c(fx_rFFA_rSTS, fx_rFFA_lSTS),
    names_to = "region",
    values_to = "fx_rFFA_rlSTS"
  ) %>%
  mutate(
    Hemisphere = case_when(
      region == "fx_rFFA_rSTS" ~ "Right",
      region == "fx_rFFA_lSTS" ~ "Left",
      TRUE ~ NA_character_
    )
  ) %>%
  select(ID, fm_rFFA, fx_rFFA_rlSTS, Age, MeanFD, Hemisphere)

# Models

## MMPFC

model_rFFA_fm_MMPFC_fx <-lmer(fx_rFFA_rlMMPFC ~ fm_rFFA*Hemisphere*Age + MeanFD + (1|ID), data = long_data_MMPFC)
summary(model_rFFA_fm_MMPFC_fx)

### No interaction effects are significant but Hemisphere*Age, so models are run without interaction effects but Hemisphere*Age

model_rFFA_fm_MMPFC_fx <- lmer(fx_rFFA_rlMMPFC ~ fm_rFFA + Hemisphere + Age + MeanFD + Hemisphere*Age + (1| ID), data = long_data_MMPFC)
summary_rFFA_fm_MMPFC_fx <- tidy(model_rFFA_fm_MMPFC_fx)
summary_rFFA_fm_MMPFC_fx

## Amygdala

model_rFFA_fm_amygdala_fx <- lmer(fx_rFFA_rlamygdala ~ fm_rFFA*Hemisphere*Age + MeanFD + (1|ID), data = long_data_amygdala)
summary(model_rFFA_fm_amygdala_fx)

### No interaction effects are significant, so models are run without interaction effects 

model_rFFA_fm_amygdala_fx <- lmer(fx_rFFA_rlamygdala ~ fm_rFFA + Hemisphere + Age + MeanFD + (1| ID), data = long_data_amygdala)
summary_rFFA_fm_amygdala_fx <- tidy(model_rFFA_fm_amygdala_fx)
summary_rFFA_fm_amygdala_fx

## STS

model_rFFA_fm_STS_fx <- lmer(fx_rFFA_rlSTS ~ fm_rFFA*Hemisphere*Age + MeanFD + (1|ID), data = long_data_STS)
summary(model_rFFA_fm_STS_fx)

### No interaction effects are significant, so models are run without interaction effects 

model_rFFA_fm_STS_fx <- lmer(fx_rFFA_rlSTS ~ fm_rFFA + Hemisphere + Age + MeanFD + (1| ID), data = long_data_STS)
summary_rFFA_fm_STS_fx <- tidy(model_rFFA_fm_STS_fx)
summary_rFFA_fm_STS_fx

```

Left FFA

```{r}

# Data wrangling

long_data <- child_MRIvariables

long_data_amygdala <- long_data %>%
  select(
    ID,
    fm_lFFA,
    fx_lFFA_ramygdala,
    fx_lFFA_lamygdala,
    Age,
    MeanFD
  )
long_data_MMPFC <- long_data %>%
  select(
    ID,
    fm_lFFA,
    fx_lFFA_rMMPFC,
    fx_lFFA_lMMPFC,
    Age,
    MeanFD
  )

long_data_STS <- long_data %>%
  select(
    ID,
    fm_lFFA,
    fx_lFFA_rSTS,
    fx_lFFA_lSTS,
    Age,
    MeanFD
  )

## Reshape the data and adjust columns

long_data_amygdala <- long_data_amygdala %>%
  ## Pivot the data into a long format with "Right" and "Left" hemispheres
  pivot_longer(
    cols = c(fx_lFFA_ramygdala, fx_lFFA_lamygdala),
    names_to = "region",
    values_to = "fx_lFFA_rlamygdala"
  ) %>%
  ## Create Hemisphere column based on the region name
  mutate(
    Hemisphere = case_when(
      region == "fx_lFFA_ramygdala" ~ "Right",
      region == "fx_lFFA_lamygdala" ~ "Left",
      TRUE ~ NA_character_
    )
  ) %>%
  select(ID, fm_lFFA, fx_lFFA_rlamygdala, Age, MeanFD, Hemisphere)

long_data_MMPFC <- long_data_MMPFC %>%
  pivot_longer(
    cols = c(fx_lFFA_rMMPFC, fx_lFFA_lMMPFC),
    names_to = "region",
    values_to = "fx_lFFA_rlMMPFC"
  ) %>%
  mutate(
    Hemisphere = case_when(
      region == "fx_lFFA_rMMPFC" ~ "Right",
      region == "fx_lFFA_lMMPFC" ~ "Left",
      TRUE ~ NA_character_
    )
  ) %>%
  select(ID, fm_lFFA, fx_lFFA_rlMMPFC, Age, MeanFD, Hemisphere)

long_data_STS <- long_data_STS %>%
  pivot_longer(
    cols = c(fx_lFFA_rSTS, fx_lFFA_lSTS),
    names_to = "region",
    values_to = "fx_lFFA_rlSTS"
  ) %>%
  mutate(
    Hemisphere = case_when(
      region == "fx_lFFA_rSTS" ~ "Right",
      region == "fx_lFFA_lSTS" ~ "Left",
      TRUE ~ NA_character_
    )
  ) %>%
  select(ID, fm_lFFA, fx_lFFA_rlSTS, Age, MeanFD, Hemisphere)

# Models

## MMPFC

model_lFFA_fm_MMPFC_fx <-lmer(fx_lFFA_rlMMPFC ~ fm_lFFA*Hemisphere*Age + MeanFD + (1|ID), data = long_data_MMPFC)
summary(model_lFFA_fm_MMPFC_fx)

### No interaction effects are significant, so models are run without interaction effects 

model_lFFA_fm_MMPFC_fx <- lmer(fx_lFFA_rlMMPFC ~ fm_lFFA + Hemisphere + Age + MeanFD + (1| ID), data = long_data_MMPFC)
summary_lFFA_fm_MMPFC_fx <- tidy(model_lFFA_fm_MMPFC_fx)
summary_lFFA_fm_MMPFC_fx

## Amygdala

model_lFFA_fm_amygdala_fx <- lmer(fx_lFFA_rlamygdala ~ fm_lFFA*Hemisphere*Age + MeanFD + (1|ID), data = long_data_amygdala)
summary(model_lFFA_fm_amygdala_fx)

### No interaction effects are significant, so models are run without interaction effects 

model_lFFA_fm_amygdala_fx <- lmer(fx_lFFA_rlamygdala ~ fm_lFFA + Hemisphere + Age + MeanFD + (1| ID), data = long_data_amygdala)
summary_lFFA_fm_amygdala_fx <- tidy(model_lFFA_fm_amygdala_fx)
summary_lFFA_fm_amygdala_fx

## STS

model_lFFA_fm_STS_fx <- lmer(fx_lFFA_rlSTS ~ fm_lFFA*Hemisphere*Age + MeanFD + (1|ID), data = long_data_STS)
summary(model_lFFA_fm_STS_fx)

### No interaction effects are significant, so models are run without interaction effects 

model_lFFA_fm_STS_fx <- lmer(fx_lFFA_rlSTS ~ fm_lFFA + Hemisphere + Age + MeanFD + (1| ID), data = long_data_STS)
summary_lFFA_fm_STS_fx <- tidy(model_lFFA_fm_STS_fx)
summary_lFFA_fm_STS_fx

```

Save models

```{r}

all_summaries <- bind_rows(
  summary_rFFA_fm_MMPFC_fx %>% mutate(model = "fm_rFFA_fx_MMPFC", Label = "Primary"),
  summary_rFFA_fm_amygdala_fx %>% mutate(model = "fm_rFFA_fx_amygdala", Label = "Primary"),
  summary_rFFA_fm_STS_fx %>% mutate(model = "fm_rFFA_fx_STS", Label = "Primary"),
  summary_lFFA_fm_MMPFC_fx %>% mutate(model = "fm_lFFA_fx_MMPFC", Label = "Secondary"),
  summary_lFFA_fm_amygdala_fx %>% mutate(model = "fm_lFFA_fx_amygdala", Label = "Secondary"),
  summary_lFFA_fm_STS_fx %>% mutate(model = "fm_lFFA_fx_STS", Label = "Secondary"),
) %>%
  mutate(
    estimate = round(estimate, 2),
    std.error = round(std.error, 2),
    statistic = round(statistic, 2),
    df = round(df, 0),
    p.value = if_else(
      p.value < 0.001,
      format(p.value, scientific = TRUE, digits = 4),
      sprintf("%.3f", p.value)
    )
  )

write.csv(all_summaries, here("results/RQ2", "Fm_fx.csv"), row.names = FALSE)

```

### Relationship between functional connectivity of right FFA and right MMPFC and functional maturity of right FFA

Since connectivity between right MMPFC and right FFA increased with age more than connectivity between left MMPFC and right FFA, we tested if this relationship was correlated with the functional maturity of FFA separately.

```{r}

# Model

model_rFFA_fm_rFFA_rMMPFC_fx <- lm(fm_rFFA ~ fx_rFFA_rMMPFC*Age + MeanFD, data = child_MRIvariables)
summary(model_rFFA_fm_rFFA_rMMPFC_fx)

### No interaction effects are significant, so models are run without interaction effects

model_rFFA_fm_rFFA_rMMPFC_fx <- lm(fm_rFFA ~ fx_rFFA_rMMPFC + Age + MeanFD, data = child_MRIvariables)
model_rFFA_fm_rFFA_rMMPFC_fx <- tidy(model_rFFA_fm_rFFA_rMMPFC_fx)

# Save model

model_rFFA_fm_rFFA_rMMPFC_fx <- model_rFFA_fm_rFFA_rMMPFC_fx %>%
  mutate(
    estimate = round(estimate, 2),
    std.error = round(std.error, 2),
    statistic = round(statistic, 2),
    p.value = if_else(
      p.value < 0.001,
      format(p.value, scientific = TRUE, digits = 4),
      sprintf("%.3f", p.value)
    )
  )

write.csv(model_rFFA_fm_rFFA_rMMPFC_fx, here("results/RQ2", "rFFA_fm_rFFA_rMMPFC_fx.csv"), row.names = FALSE)

```

### Plots

```{r}

# Data wrangling

data_plot <- read_csv(here("processed_data", "child_MRIvariables.csv"), col_names=TRUE)
data_plot <- merge(data_plot, participants[,c(1:2)], by="ID")
data_plot <- merge(data_plot, motion[,c(4,6)], by="ID")
data_plot <- data_plot[,c(1,4,5, 202:229)]
data_plot <- data_plot %>%
  rename_with(~ sub("^zscored_", "", .x), starts_with("zscored_"))
data_plot <- data_plot %>%
  pivot_longer(
    cols = starts_with("fx_"),
    names_to = c("Region1", "Region2"),
    names_pattern = "fx_(.+)_(.+)",
    values_to = "zscored_value"
  )
data_plot <- data_plot %>%
  mutate(
    Hemisphere = ifelse(grepl("^r", Region2), "right", "left"),
    Region2 = sub("^[rl]", "", Region2)
  )
data_plot_rFFA_MMPFC <- data_plot %>%
  filter(Region2 == "MMPFC", Region1 == "rFFA")
data_plot_lFFA_MMPFC <- data_plot %>%
  filter(Region2 == "MMPFC", Region1 == "lFFA")
data_plot_rFFA_amygdala <- data_plot %>%
  filter(Region2 == "amygdala", Region1 == "rFFA")
data_plot_lFFA_amygdala <- data_plot %>%
  filter(Region2 == "amygdala", Region1 == "lFFA")
data_plot_rFFA_STS <- data_plot %>%
  filter(Region2 == "STS", Region1 == "rFFA")
data_plot_lFFA_STS <- data_plot %>%
  filter(Region2 == "STS", Region1 == "lFFA")

# Colours

custom_colours_amygdala <- c("#E1AA9F", "#D34835")
custom_colours_MMPFC <- c("#87BACF", "#578CAD")
custom_colours_FFA <- c("#C39EDA", "#652975")
custom_colours_STS <- c("#FFF865", "#FFCE1B")

# Define a base theme to avoid repetition

base_theme <- theme_minimal() +
  theme(
    strip.text = element_text(size = 14, face = "bold"),
    strip.background = element_blank(),
    axis.line.x = element_blank(),
    axis.text = element_text(size = 16),
    axis.title = element_text(size = 14, face = "bold"),
    plot.title = element_text(size = 14, hjust = 0.5, face = "bold"),
    legend.text = element_text(size = 16),
    legend.title = element_text(size = 14, face = "bold")
  )

# Function to create ggplots efficiently

create_plot <- function(data, x_var, y_var, color_values, x_label, y_label = "", legend_title = "Hemisphere", legend_position = "none", remove_y_axis_labels = FALSE) {
  
  plot <- ggplot(data, aes(x = {{ x_var }}, y = {{ y_var }}, color = Hemisphere)) +
    geom_point(alpha = 0.8, size = 2.8, shape = 19) +
    geom_smooth(method = "lm", se = FALSE, linetype = "solid", size = 2) +
    scale_color_manual(values = color_values) +
    labs(x = x_label, y = y_label, color = legend_title) +
    base_theme +
    theme(
      legend.position = legend_position,
      axis.line.x = element_blank(),
      plot.title = element_text(hjust = 0.5, size = 14, face = "bold"),
      axis.title.y = element_text(size = 14, face = "bold"),
      axis.text.y = element_text(size = 12)
    ) +
    coord_cartesian(ylim = c(-3, 3)) +  
    scale_x_continuous(breaks = c(-2, 0, 2))

  if (remove_y_axis_labels) {
    plot <- plot + theme(
      axis.title.y = element_blank(),
      axis.text.y = element_blank()
    )
  }

  return(plot)
}

# Create plots

plot_lFFA_MMPFC <- create_plot(data_plot_lFFA_MMPFC, zscored_value, fm_lFFA, custom_colours_MMPFC, "", "Functional maturity of left FFA", legend_title = "MMPFC Hemisphere")
plot_lFFA_amygdala <- create_plot(data_plot_lFFA_amygdala, zscored_value, fm_lFFA, custom_colours_amygdala, "Functional connectivity between left FFA and region", "Functional maturity of left FFA", legend_title = "Amygdala Hemisphere", legend_position = "bottom", remove_y_axis_labels = TRUE)
plot_lFFA_STS <- create_plot(data_plot_lFFA_STS, zscored_value, fm_lFFA, custom_colours_STS, "", "", legend_title = "STS Hemisphere", legend_position = "bottom", remove_y_axis_labels = TRUE)+
  annotate(
    "text",
    x = Inf, y = -Inf,                        # bottom right corner
    label = "Fm left FFA effect:\nβ(SE)=-0.14(0.07), p=0.046",
    hjust = 1.05,      # slightly >1 for proper right alignment
    vjust = -0.25,      # nudges text up from bottom
    size = 4,
    color = "black"
)

plot_rFFA_MMPFC <- create_plot(data_plot_rFFA_MMPFC, zscored_value, fm_rFFA, custom_colours_MMPFC, "", "Functional maturity of right FFA", legend_title = "MMPFC Hemisphere", legend_position = "bottom") +
  annotate(
    "text",
    x = Inf, y = -Inf,                        # bottom right corner
    label = "Fx right FFA - right MMPFC effect:\nβ(SE)=0.17(0.08), p=0.045",
    hjust = 1.05,      # slightly >1 for proper right alignment
    vjust = -0.25,      # nudges text up from bottom
    size = 4,
    color = "black"
)
plot_rFFA_amygdala <- create_plot(data_plot_rFFA_amygdala, zscored_value, fm_rFFA, custom_colours_amygdala, "Functional connectivity between right FFA and region", "Functional maturity of right FFA", legend_title = "Amygdala Hemisphere", remove_y_axis_labels = TRUE)
plot_rFFA_STS <- create_plot(data_plot_rFFA_STS, zscored_value, fm_lFFA, custom_colours_STS, "", "", legend_title = "STS Hemisphere", legend_position = "bottom", remove_y_axis_labels = TRUE)

## Combine plots into a single row

fm_fx_rFFA <- (plot_rFFA_MMPFC | plot_rFFA_amygdala | plot_rFFA_STS) +  
  plot_layout(ncol = 3, guides = "collect") +
  plot_annotation(
    title = ""
  ) &
  theme(
    legend.position = "bottom",
    legend.text = element_text(size = 12),
    legend.title = element_text(size = 12),
    plot.title = element_text(size = 14, hjust = 0.5, face = "bold")
  )
fm_fx_lFFA <- (plot_lFFA_MMPFC | plot_lFFA_amygdala | plot_lFFA_STS) +  
  plot_layout(ncol = 3, guides = "collect") +
  plot_annotation(
    title = ""
  ) &
  theme(
    legend.position = "bottom",
    legend.text = element_text(size = 12),
    legend.title = element_text(size = 12),
    plot.title = element_text(size = 14, hjust = 0.5, face = "bold")
  )

## Display and save plot

ggsave(here("results/figures", "Fm_fx_rFFA.png"), plot = fm_fx_rFFA, width = 10, height = 5, units = "in", dpi = 300)
ggsave(here("results/figures", "Fm_fx_lFFA.png"), plot = fm_fx_lFFA, width = 10, height = 5, units = "in", dpi = 300)

```


## Section II: Functional maturity of MMPFC/amygdala/STS effects on functional maturity of right or left FFA (non-preregistered)

A similar approach than the one used in the previous section was taken for these analyses.

### Alternative mixed-effects models

Right FFA

```{r}

# Data wrangling

long_data <- child_MRIvariables

long_data_amygdala <- long_data %>%
  select(
    ID,
    fm_rFFA,
    fm_ramygdala,
    fm_lamygdala,
    Age,
    MeanFD
  )
long_data_MMPFC <- long_data %>%
  select(
    ID,
    fm_rFFA,
    fm_rMMPFC,
    fm_lMMPFC,
    Age,
    MeanFD
  )

long_data_STS <- long_data %>%
  select(
    ID,
    fm_rFFA,
    fm_rSTS,
    fm_lSTS,
    Age,
    MeanFD
  )

## Reshape the data and adjust columns

long_data_amygdala <- long_data_amygdala %>%
  ## Pivot the data into a long format with "Right" and "Left" hemispheres
  pivot_longer(
    cols = c(fm_ramygdala, fm_lamygdala),
    names_to = "region",
    values_to = "fm_rlamygdala"
  ) %>%
  ## Create Hemisphere column based on the region name
  mutate(
    Hemisphere = case_when(
      region == "fm_ramygdala" ~ "Right",
      region == "fm_lamygdala" ~ "Left",
      TRUE ~ NA_character_
    )
  ) %>%
  select(ID, fm_rFFA, fm_rlamygdala, Age, MeanFD, Hemisphere)

long_data_MMPFC <- long_data_MMPFC %>%
  pivot_longer(
    cols = c(fm_rMMPFC, fm_lMMPFC),
    names_to = "region",
    values_to = "fm_rlMMPFC"
  ) %>%
  mutate(
    Hemisphere = case_when(
      region == "fm_rMMPFC" ~ "Right",
      region == "fm_lMMPFC" ~ "Left",
      TRUE ~ NA_character_
    )
  ) %>%
  select(ID, fm_rFFA, fm_rlMMPFC, Age, MeanFD, Hemisphere)

long_data_STS <- long_data_STS %>%
  pivot_longer(
    cols = c(fm_rSTS, fm_lSTS),
    names_to = "region",
    values_to = "fm_rlSTS"
  ) %>%
  mutate(
    Hemisphere = case_when(
      region == "fm_rSTS" ~ "Right",
      region == "fm_lSTS" ~ "Left",
      TRUE ~ NA_character_
    )
  ) %>%
  select(ID, fm_rFFA, fm_rlSTS, Age, MeanFD, Hemisphere)

# Models

## MMPFC

model_rFFA_fm_MMPFC_fm <-lmer(fm_rlMMPFC ~ fm_rFFA*Hemisphere*Age + MeanFD + (1|ID), data = long_data_MMPFC)
summary(model_rFFA_fm_MMPFC_fm)

### No interaction effects are significant, so models are run without interaction effects 

model_rFFA_fm_MMPFC_fm <- lmer(fm_rlMMPFC ~ fm_rFFA + Hemisphere + Age + MeanFD + (1| ID), data = long_data_MMPFC)
summary_rFFA_fm_MMPFC_fm <- tidy(model_rFFA_fm_MMPFC_fm)
summary_rFFA_fm_MMPFC_fm

## Amygdala

model_rFFA_fm_amygdala_fm <- lmer(fm_rlamygdala ~ fm_rFFA*Hemisphere*Age + MeanFD + (1|ID), data = long_data_amygdala)
summary(model_rFFA_fm_amygdala_fm)

### No interaction effects are significant, so models are run without interaction effects 

model_rFFA_fm_amygdala_fm <- lmer(fm_rlamygdala ~ fm_rFFA + Hemisphere + Age + MeanFD + (1| ID), data = long_data_amygdala)
summary_rFFA_fm_amygdala_fm <- tidy(model_rFFA_fm_amygdala_fm)
summary_rFFA_fm_amygdala_fm

## STS

model_rFFA_fm_STS_fm <- lmer(fm_rlSTS ~ fm_rFFA*Hemisphere*Age + MeanFD + (1|ID), data = long_data_STS)
summary(model_rFFA_fm_STS_fm)

### No interaction effects are significant, so models are run without interaction effects 

model_rFFA_fm_STS_fm <- lmer(fm_rlSTS ~ fm_rFFA + Hemisphere + Age + MeanFD + (1| ID), data = long_data_STS)
summary_rFFA_fm_STS_fm <- tidy(model_rFFA_fm_STS_fm)
summary_rFFA_fm_STS_fm

```

Left FFA

```{r}

# Data wrangling

long_data <- child_MRIvariables

long_data_amygdala <- long_data %>%
  select(
    ID,
    fm_lFFA,
    fm_ramygdala,
    fm_lamygdala,
    Age,
    MeanFD
  )
long_data_MMPFC <- long_data %>%
  select(
    ID,
    fm_lFFA,
    fm_rMMPFC,
    fm_lMMPFC,
    Age,
    MeanFD
  )

long_data_STS <- long_data %>%
  select(
    ID,
    fm_lFFA,
    fm_rSTS,
    fm_lSTS,
    Age,
    MeanFD
  )

## Reshape the data and adjust columns

long_data_amygdala <- long_data_amygdala %>%
  ## Pivot the data into a long format with "Right" and "Left" hemispheres
  pivot_longer(
    cols = c(fm_ramygdala, fm_lamygdala),
    names_to = "region",
    values_to = "fm_rlamygdala"
  ) %>%
  ## Create Hemisphere column based on the region name
  mutate(
    Hemisphere = case_when(
      region == "fm_ramygdala" ~ "Right",
      region == "fm_lamygdala" ~ "Left",
      TRUE ~ NA_character_
    )
  ) %>%
  select(ID, fm_lFFA, fm_rlamygdala, Age, MeanFD, Hemisphere)

long_data_MMPFC <- long_data_MMPFC %>%
  pivot_longer(
    cols = c(fm_rMMPFC, fm_lMMPFC),
    names_to = "region",
    values_to = "fm_rlMMPFC"
  ) %>%
  mutate(
    Hemisphere = case_when(
      region == "fm_rMMPFC" ~ "Right",
      region == "fm_lMMPFC" ~ "Left",
      TRUE ~ NA_character_
    )
  ) %>%
  select(ID, fm_lFFA, fm_rlMMPFC, Age, MeanFD, Hemisphere)

long_data_STS <- long_data_STS %>%
  pivot_longer(
    cols = c(fm_rSTS, fm_lSTS),
    names_to = "region",
    values_to = "fm_rlSTS"
  ) %>%
  mutate(
    Hemisphere = case_when(
      region == "fm_rSTS" ~ "Right",
      region == "fm_lSTS" ~ "Left",
      TRUE ~ NA_character_
    )
  ) %>%
  select(ID, fm_lFFA, fm_rlSTS, Age, MeanFD, Hemisphere)

# Models

## MMPFC

model_lFFA_fm_MMPFC_fm <-lmer(fm_rlMMPFC ~ fm_lFFA*Hemisphere*Age + MeanFD + (1|ID), data = long_data_MMPFC)
summary(model_lFFA_fm_MMPFC_fm)

### No interaction effects are significant, so models are run without interaction effects 

model_lFFA_fm_MMPFC_fm <- lmer(fm_rlMMPFC ~ fm_lFFA + Hemisphere + Age + MeanFD + (1| ID), data = long_data_MMPFC)
summary_lFFA_fm_MMPFC_fm <- tidy(model_lFFA_fm_MMPFC_fm)
summary_lFFA_fm_MMPFC_fm

## Amygdala

model_lFFA_fm_amygdala_fm <- lmer(fm_rlamygdala ~ fm_lFFA*Hemisphere*Age + MeanFD + (1|ID), data = long_data_amygdala)
summary(model_lFFA_fm_amygdala_fm)

### No interaction effects are significant, so models are run without interaction effects 

model_lFFA_fm_amygdala_fm <- lmer(fm_rlamygdala ~ fm_lFFA + Hemisphere + Age + MeanFD + (1| ID), data = long_data_amygdala)
summary_lFFA_fm_amygdala_fm <- tidy(model_lFFA_fm_amygdala_fm)
summary_lFFA_fm_amygdala_fm

## STS

model_lFFA_fm_STS_fm <- lmer(fm_rlSTS ~ fm_lFFA*Hemisphere*Age + MeanFD + (1|ID), data = long_data_STS)
summary(model_lFFA_fm_STS_fm)

### No interaction effects are significant, so models are run without interaction effects 

model_lFFA_fm_STS_fm <- lmer(fm_rlSTS ~ fm_lFFA + Hemisphere + Age + MeanFD + (1| ID), data = long_data_STS)
summary_lFFA_fm_STS_fm <- tidy(model_lFFA_fm_STS_fm)
summary_lFFA_fm_STS_fm

```

Save models

```{r}

all_summaries <- bind_rows(
  summary_rFFA_fm_MMPFC_fm %>% mutate(model = "fm_rFFA_fm_MMPFC", Label = "Primary"),
  summary_rFFA_fm_amygdala_fm %>% mutate(model = "fm_rFFA_fm_amygdala", Label = "Primary"),
  summary_rFFA_fm_STS_fm %>% mutate(model = "fm_rFFA_fm_STS", Label = "Primary"),
  summary_lFFA_fm_MMPFC_fm %>% mutate(model = "fm_lFFA_fm_MMPFC", Label = "Secondary"),
  summary_lFFA_fm_amygdala_fm %>% mutate(model = "fm_lFFA_fm_amygdala", Label = "Secondary"),
  summary_lFFA_fm_STS_fm %>% mutate(model = "fm_lFFA_fm_STS", Label = "Secondary"),
) %>%
  mutate(
    estimate = round(estimate, 2),
    std.error = round(std.error, 2),
    statistic = round(statistic, 2),
    df = round(df, 0),
    p.value = if_else(
      p.value < 0.001,
      format(p.value, scientific = TRUE, digits = 4),
      sprintf("%.3f", p.value)
    )
  )

write.csv(all_summaries, here("results/RQ2", "Fm_fm.csv"), row.names = FALSE)

```

### Plots

```{r}

# Data wrangling

data_plot <- read_csv(here("processed_data", "child_MRIvariables.csv"), col_names=TRUE)
data_plot <- data_plot %>%
  rename_with(~ sub("^zscored_", "", .x), starts_with("zscored_"))
data_plot <- data_plot %>%
  dplyr::rename_with(~ sub("^fm_", "fmo_", .x), 
                     .cols = c(fm_rMMPFC, fm_lMMPFC, fm_ramygdala, fm_lamygdala, fm_rSTS, fm_lSTS))
data_plot <- data_plot %>%
  select(fm_rFFA, fm_lFFA, fmo_rMMPFC, fmo_lMMPFC, fmo_ramygdala, fmo_lamygdala, fmo_rSTS, fmo_lSTS) %>%
  pivot_longer(
    cols = c("fmo_rMMPFC", "fmo_lMMPFC", "fmo_ramygdala", "fmo_lamygdala", "fmo_rSTS", "fmo_lSTS"),
    names_to = c("Hemisphere", "Region"),
    names_pattern = "fmo_([rl])(.+)",   # r/l hemisphere + region name
    values_to = "zscored_value"
  ) %>%
  mutate(
    Hemisphere = case_when(
      Hemisphere == "r" ~ "right",
      Hemisphere == "l" ~ "left"),
    Region = case_when(
      Region == "MMPFC" ~ "MMPFC",
      Region == "amygdala" ~ "amygdala",
      Region == "STS" ~ "STS",
      TRUE ~ Region
    )
  )

data_plot_rFFA_MMPFC <- data_plot %>%
  select(fm_rFFA, Hemisphere, Region, zscored_value) %>%
  filter(Region == "MMPFC")
data_plot_lFFA_MMPFC <- data_plot %>%
  select(fm_lFFA, Hemisphere, Region, zscored_value) %>%
  filter(Region == "MMPFC")
data_plot_rFFA_amygdala <- data_plot %>%
  select(fm_rFFA, Hemisphere, Region, zscored_value) %>%
  filter(Region == "amygdala")
data_plot_lFFA_amygdala <- data_plot %>%
  select(fm_lFFA, Hemisphere, Region, zscored_value) %>%
  filter(Region == "amygdala")
data_plot_rFFA_STS <- data_plot %>%
  select(fm_rFFA, Hemisphere, Region, zscored_value) %>%
  filter(Region == "STS")
data_plot_lFFA_STS <- data_plot %>%
  select(fm_lFFA, Hemisphere, Region, zscored_value) %>%
  filter(Region == "STS")

# Colours

custom_colours_amygdala <- c("#E1AA9F", "#D34835")
custom_colours_MMPFC <- c("#87BACF", "#578CAD")
custom_colours_FFA <- c("#C39EDA", "#652975")
custom_colours_STS <- c("#FFF865", "#FFCE1B")

# Define a base theme to avoid repetition

base_theme <- theme_minimal() +
  theme(
    strip.text = element_text(size = 14, face = "bold"),
    strip.background = element_blank(),
    axis.line.x = element_blank(),
    axis.text = element_text(size = 16),
    axis.title = element_text(size = 14, face = "bold"),
    plot.title = element_text(size = 14, hjust = 0.5, face = "bold"),
    legend.text = element_text(size = 16),
    legend.title = element_text(size = 14, face = "bold")
  )

# Function to create ggplots efficiently

create_plot <- function(data, x_var, y_var, color_values, x_label, y_label = "", legend_title = "Hemisphere", legend_position = "none", remove_y_axis_labels = FALSE) {
  
  plot <- ggplot(data, aes(x = {{ x_var }}, y = {{ y_var }}, color = Hemisphere)) +
    geom_point(alpha = 0.8, size = 2.8, shape = 19) +
    geom_smooth(method = "lm", se = FALSE, linetype = "solid", linewidth = 2) +
    scale_color_manual(values = color_values) +
    labs(x = x_label, y = y_label, color = legend_title) +
    base_theme +
    theme(
      legend.position = legend_position,
      axis.line.x = element_blank(),
      plot.title = element_text(hjust = 0.5, size = 14, face = "bold"),
      axis.title.y = element_text(size = 14, face = "bold"),
      axis.text.y = element_text(size = 12)
    ) +
    coord_cartesian(ylim = c(-3, 3)) +  
    scale_x_continuous(breaks = c(-2, 0, 2))

  if (remove_y_axis_labels) {
    plot <- plot + theme(
      axis.title.y = element_blank(),
      axis.text.y = element_blank()
    )
  }

  return(plot)
}

# Create all plots using the function

plot_lFFA_MMPFC <- create_plot(data_plot_lFFA_MMPFC, zscored_value, fm_lFFA, custom_colours_MMPFC, "", "Functional maturity of left FFA", legend_title = "MMPFC Hemisphere")
plot_lFFA_amygdala <- create_plot(data_plot_lFFA_amygdala, zscored_value, fm_lFFA, custom_colours_amygdala, "Functional maturity of region", "Functional maturity of left FFA", legend_title = "Amygdala Hemisphere", legend_position = "bottom", remove_y_axis_labels = TRUE)
plot_lFFA_STS <- create_plot(data_plot_lFFA_STS, zscored_value, fm_lFFA, custom_colours_STS, "", "Functional maturity of left FFA", legend_title = "STS Hemisphere", legend_position = "bottom", remove_y_axis_labels = TRUE)+
  annotate(
    "text",
    x = Inf, y = -Inf,                        # bottom right corner
    label = "Fm left FFA  effect:\nβ(SE)=0.16(0.07), p=0.019 ",    # your annotation
    hjust = 1.05,      # slightly >1 for proper right alignment
    vjust = -0.25,      # nudges text up from bottom
    size = 4,
    color = "black"
)

plot_rFFA_MMPFC <- create_plot(data_plot_rFFA_MMPFC, zscored_value, fm_rFFA, custom_colours_MMPFC, "", "Functional maturity of right FFA", legend_title = "MMPFC Hemisphere", legend_position = "bottom")
plot_rFFA_amygdala <- create_plot(data_plot_rFFA_amygdala, zscored_value, fm_rFFA, custom_colours_amygdala, "Functional maturity of region", "Functional maturity of right FFA", legend_title = "Amygdala Hemisphere", remove_y_axis_labels = TRUE)
plot_rFFA_STS <- create_plot(data_plot_rFFA_STS, zscored_value, fm_rFFA, custom_colours_STS, "", "Functional maturity of right FFA", legend_title = "STS Hemisphere", legend_position = "bottom", remove_y_axis_labels = TRUE)+
  annotate(
    "text",
    x = Inf, y = -Inf,                        # bottom right corner
    label = "Fm right FFA effect:\nβ(SE)=0.19(0.07), p=0.008 ",    # your annotation
    hjust = 1.05,      # slightly >1 for proper right alignment
    vjust = -0.25,      # nudges text up from bottom
    size = 4,
    color = "black"
)

# Combine plots into a single row

fm_fm_rFFA <- (plot_rFFA_MMPFC | plot_rFFA_amygdala | plot_rFFA_STS) +  
  plot_layout(ncol = 3, guides = "collect") +
  plot_annotation(
    title = ""
  ) &
  theme(
    legend.position = "bottom",
    legend.text = element_text(size = 12),
    legend.title = element_text(size = 12),
    plot.title = element_text(size = 14, hjust = 0.5, face = "bold")
  )

fm_fm_lFFA <- (plot_lFFA_MMPFC | plot_lFFA_amygdala | plot_lFFA_STS) +  
  plot_layout(ncol = 3, guides = "collect") +
  plot_annotation(
    title = ""
  ) &
  theme(
    legend.position = "bottom",
    legend.text = element_text(size = 12),
    legend.title = element_text(size = 12),
    plot.title = element_text(size = 14, hjust = 0.5, face = "bold")
  )

## Display and save plot

ggsave(here("results/figures", "Fm_fm_rFFA.png"), plot = fm_fm_rFFA, width = 10, height = 5, units = "in", dpi = 300)
ggsave(here("results/figures", "Fm_fm_lFFA.png"), plot = fm_fm_lFFA, width = 10, height = 5, units = "in", dpi = 300)

```


## Section III: Correlations between fMRI variables

### Correlation between functional connectivity measures

```{r}

# Select relevant variables

selected_vars <- child_MRIvariables %>%
  select(
    fx_rFFA_ramygdala, fx_rFFA_lamygdala,
    fx_lFFA_ramygdala, fx_lFFA_lamygdala,
    fx_rFFA_rMMPFC, fx_rFFA_lMMPFC,
    fx_lFFA_rMMPFC, fx_lFFA_lMMPFC,
    fx_rFFA_rSTS, fx_rFFA_lSTS,
    fx_lFFA_rSTS, fx_lFFA_lSTS
  )

selected_vars <- selected_vars %>%
  rename_with(~ c("Fx right FFA-right amygdala", "Fx right FFA-left amygdala", "Fx left FFA-right amygdala", "Fx left FFA-left amygdala", 
                  "Fx right FFA-right MMPFC", "Fx right FFA-left MMPFC", "Fx left FFA-right MMPFC", "Fx left FFA-left MMPFC",
                  "Fx right FFA-right STS", "Fx right FFA-left STS", "Fx left FFA-right STS", "Fx left FFA-left STS"),
              .cols = c("fx_rFFA_ramygdala", "fx_rFFA_lamygdala", "fx_lFFA_ramygdala", "fx_lFFA_lamygdala", 
                        "fx_rFFA_rMMPFC", "fx_rFFA_lMMPFC", "fx_lFFA_rMMPFC", "fx_lFFA_lMMPFC",
                        "fx_rFFA_rSTS", "fx_rFFA_lSTS", "fx_lFFA_rSTS", "fx_lFFA_lSTS"))

# Define order of variables of interest

variables <- c("Fx left FFA-right amygdala", "Fx left FFA-left amygdala",
  "Fx left FFA-right MMPFC", "Fx left FFA-left MMPFC",
  "Fx left FFA-right STS", "Fx left FFA-left STS",
  "Fx right FFA-right amygdala", "Fx right FFA-left amygdala",
  "Fx right FFA-right MMPFC", "Fx right FFA-left MMPFC",
  "Fx right FFA-right STS", "Fx right FFA-left STS"
)

# Calculate correlation matrix

cor_matrix <- cor(selected_vars, use = "complete.obs", method = "pearson")

# Convert to long format

data_plot <- as.data.frame(as.table(cor_matrix))
colnames(data_plot) <- c("Variable1", "Variable2", "value")

data_plot <- data_plot %>%
  filter(Variable1 != Variable2)

# Order factor levels for consistent axis order

Variable_levels <- variables
data_plot$Variable1 <- factor(data_plot$ Variable1, levels = Variable_levels)
data_plot$Variable2 <- factor(data_plot$Variable2, levels = Variable_levels)

# Identify upper triangle entries (for displaying numbers only)

data_plot <- data_plot %>%
  mutate(is_upper = as.numeric(Variable1) < as.numeric(Variable2))

# Plot

heatmap_plot <- ggplot(data_plot, aes(x = Variable1, y = Variable2, fill = value)) +
  geom_tile() +
  geom_tile(data = data_plot %>% filter(is_upper), fill = "white", color = NA) +
  geom_text(data = data_plot %>% filter(is_upper), 
    aes(label = sprintf("%.2f", value)), size = 3) +  # smaller text
  scale_fill_gradient2(
    low = "#D34835", high = "#87BACF", mid = "white", 
    midpoint = 0, limit = c(-0.80, 0.80), 
    name = "Correlation",
    breaks = c(-0.80, -0.40, 0, 0.40, 0.80),
    labels = c("-0.80", "-0.40", "0.00", "0.40", "0.80")
  ) +
  theme_minimal() +
  labs(
    title = "",
    x = "",
    y = ""
  ) +
  theme(
    legend.position = "right",
    axis.text.x = element_text(angle = 45, hjust = 1, face = "bold", color = "darkgrey", size = 10),
    axis.text.y = element_text(face = "bold", color = "darkgrey", size = 10),
    strip.text = element_text(size = 10),
    plot.title = element_text(hjust = 0.5, size = 14),
    plot.title.position = "plot"
  )

heatmap_plot
ggsave(here("results/figures", "Fx_Correlations.png"), plot = heatmap_plot, width = 7, height = 5.5, units = "in", dpi = 300)

```

### Correlation between functional maturity measures

```{r}

# Select relevant variables

selected_vars <- child_MRIvariables %>%
  select(
    fm_rFFA, fm_lFFA,
    fm_ramygdala, fm_lamygdala,
    fm_rMMPFC, fm_lMMPFC,
    fm_rSTS, fm_lSTS
  )

selected_vars <- selected_vars %>%
  rename_with(~ c("Fm right FFA", "Fm left FFA", 
                  "Fm right amygdala", "Fm left amygdala",
                  "Fm right MMPFC", "Fm left MMPFC",
                  "Fm right STS", "Fm left STS"),
              .cols = c("fm_rFFA", "fm_lFFA", 
                        "fm_ramygdala", "fm_lamygdala",
                        "fm_rMMPFC", "fm_lMMPFC", 
                        "fm_rSTS", "fm_lSTS"))

# Define order of variables of interest

variables <- c("Fm right FFA", "Fm left FFA", 
                  "Fm right amygdala", "Fm left amygdala",
                  "Fm right MMPFC", "Fm left MMPFC",
                  "Fm right STS", "Fm left STS")

# Calculate correlation matrix

cor_matrix <- cor(selected_vars, use = "complete.obs", method = "pearson")

# Convert to long format

data_plot <- as.data.frame(as.table(cor_matrix))
colnames(data_plot) <- c("Variable1", "Variable2", "value")

data_plot <- data_plot %>%
  filter(Variable1 != Variable2)

# Order factor levels for consistent axis order

Variable_levels <- variables
data_plot$Variable1 <- factor(data_plot$ Variable1, levels = Variable_levels)
data_plot$Variable2 <- factor(data_plot$Variable2, levels = Variable_levels)

# Identify upper triangle entries (for displaying numbers only)

data_plot <- data_plot %>%
  mutate(is_upper = as.numeric(Variable1) < as.numeric(Variable2))

# Plot

heatmap_plot <- ggplot(data_plot, aes(x = Variable1, y = Variable2, fill = value)) +
  geom_tile() +
  geom_tile(data = data_plot %>% filter(is_upper), fill = "white", color = NA) +
  geom_text(data = data_plot %>% filter(is_upper), 
    aes(label = sprintf("%.2f", value)), size = 3) +  # smaller text
  scale_fill_gradient2(
    low = "#D34835", high = "#87BACF", mid = "white", 
    midpoint = 0, limit = c(-0.80, 0.80), 
    name = "Correlation",
    breaks = c(-0.80, -0.40, 0, 0.40, 0.80),
    labels = c("-0.80", "-0.40", "0.00", "0.40", "0.80")
  ) +
  theme_minimal() +
  labs(
    title = "",
    x = "",
    y = ""
  ) +
  theme(
    legend.position = "right",
    axis.text.x = element_text(angle = 45, hjust = 1, face = "bold", color = "darkgrey", size = 10),
    axis.text.y = element_text(face = "bold", color = "darkgrey", size = 10),
    strip.text = element_text(size = 10),
    plot.title = element_text(hjust = 0.5, size = 14),
    plot.title.position = "plot"
  )

heatmap_plot
ggsave(here("results/figures", "Fm_Correlations.png"), plot = heatmap_plot, width = 7, height = 5.5, units = "in", dpi = 300)

```


```{r}

markdownToHTML("FRIC_FunctionalMaturityFFA.Rmd",output ="FRIC_FunctionalMaturityFFA.html")

```

