---
title: "FRIC_LateralisationIndexFFA"
author: "LJS"
date: "2025-01-17"
output: html_document
---

# Libraries 

```{r setup, include=FALSE}

library("rlang") #toolbox
library("readr") #toolbox
library("dplyr") #data manipulation
library("here") #toolbox
library("tidyverse") #data manipulation
library("ggpubr") #plotting
library("tidytext") #data manipulation
library("knitr") #rmarkdown
library("htmltools") #rmarkdown
library("markdown") #rmarkdown
library("httpuv") #rmarkdown
library("NCmisc") #toolbox
library("stringr") #data manipulation
library("reshape") #data manipulation
library("lme4") #regression models
library("lmerTest") #regression models
library("broom.mixed") #save regression results
library("car") #VIF
library("VIM") #visualise missing data
library("reshape2") # For reshaping data
library("patchwork") # For combining multiple plots (if needed)
library("broom") #tidying model summaries

```


# Face Responses in Childhood (FRIC) project

This script tests if the FFA lateralisation index correlates with functional connectivity to or functional maturity of MMPFC, STS and amygdala.

Structure:
- Section I: Lateralised connectivity to the MMPFC or amygdala drives lateralisation of FFA response
- Section II: Functional maturation of MMPFC/amygdala drives lateralisation of FFA response
- Section III: Relationship between lateralisation of FFA response and functional maturity of FFA.


## Section I: Lateralised connectivity to the MMPFC or amygdala drives lateralisation of FFA response

### Read data

```{r}

# Covariates

participants <- read_tsv(here("raw_data/covariates", "participants.tsv"), col_names=TRUE)
colnames(participants)[which(names(participants) == "participant_id")] <- "ID"

## Remove the word "pixar" and trim extra whitespace

participants$ID <- gsub("[sub-pixar-]","", participants$ID)
participants$ID <- trimws(participants$ID)

# Motion

motion <- read_tsv(here("raw_data/motion", "outlier_info.tsv"), col_names=TRUE)
colnames(motion)[which(names(motion) == "subject")] <- "ID"

## Remove the word "pixar" and trim extra whitespace

motion$ID <- gsub("[sub-pixar-]","", motion$ID)
motion$ID <- trimws(motion$ID)

# Child fMRI variables

child_LI <- read_csv(here("processed_data", "child_MRIvariables.csv"), col_names=TRUE)

# Complete dataset

child_LI <- child_LI[,c(1:9, 202:231)]
child_LI <- merge(child_LI, participants[,c(1:2)], by="ID")
child_LI <- merge(child_LI, motion[,c(4,6)], by="ID")
child_LI <- child_LI %>%
  rename_with(~ sub("^zscored_", "", .x), starts_with("zscored_"))
child_LI[, c("lateralisation_index_0.05","lateralisation_index_0.1", "Age", "MeanFD")] <- scale(child_LI[, c("lateralisation_index_0.05","lateralisation_index_0.1", "Age", "MeanFD")])

```

### Threshold p<0.05 (non-preregistered threshold)

Primary models

```{r}

long_data <- child_LI

# Filter long data

long_data_amygdala <- long_data %>%
  select(
    ID,
    lateralisation_index_0.05,
    fx_rFFA_ramygdala,
    fx_rFFA_lamygdala,
    Age,
    MeanFD
  )
long_data_MMPFC <- long_data %>%
  select(
    ID,
    lateralisation_index_0.05,
    fx_rFFA_rMMPFC,
    fx_rFFA_lMMPFC,
    Age,
    MeanFD
  )

## Reshape the data and adjust columns

long_data_amygdala <- long_data_amygdala %>%
  ## Pivot the data into a long format with "Right" and "Left" hemispheres
  pivot_longer(
    cols = c(fx_rFFA_ramygdala, fx_rFFA_lamygdala),
    names_to = "region",
    values_to = "fx_rFFA_rlamygdala"
  ) %>%
  ## Create Hemisphere column based on the region name
  mutate(
    Hemisphere = case_when(
      region == "fx_rFFA_ramygdala" ~ "Right",
      region == "fx_rFFA_lamygdala" ~ "Left",
      TRUE ~ NA_character_
    )
  ) %>%
  ## Keep only relevant columns
  select(ID, lateralisation_index_0.05, fx_rFFA_rlamygdala, Age, MeanFD, Hemisphere)

long_data_MMPFC <- long_data_MMPFC %>%
  ## Pivot the data into a long format with "Right" and "Left" hemispheres
  pivot_longer(
    cols = c(fx_rFFA_rMMPFC, fx_rFFA_lMMPFC),
    names_to = "region",
    values_to = "fx_rFFA_rlMMPFC"
  ) %>%
  ## Create Hemisphere column based on the region name
  mutate(
    Hemisphere = case_when(
      region == "fx_rFFA_rMMPFC" ~ "Right",
      region == "fx_rFFA_lMMPFC" ~ "Left",
      TRUE ~ NA_character_
    )
  ) %>%
  ## Keep only relevant columns
  select(ID, lateralisation_index_0.05, fx_rFFA_rlMMPFC, Age, MeanFD, Hemisphere)

long_data_amygdala_selected <- long_data_amygdala %>%
  select(ID, Hemisphere, fx_rFFA_rlamygdala)
model_data <- merge(long_data_amygdala_selected, long_data_MMPFC, by = c("ID", "Hemisphere"))
model_data$Hemisphere <- as.factor(model_data$Hemisphere)

# Models

model_LI_rFFA <- lmer(lateralisation_index_0.05 ~ fx_rFFA_rlMMPFC*Hemisphere*Age + fx_rFFA_rlamygdala*Hemisphere*Age + MeanFD + (1| ID), data = model_data)
summary(model_LI_rFFA)

```

Secondary models

```{r}

long_data <- child_LI

# Filter long data

long_data_amygdala <- long_data %>%
  select(
    ID,
    lateralisation_index_0.05,
    fx_lFFA_ramygdala,
    fx_lFFA_lamygdala,
    Age,
    MeanFD
  )
long_data_MMPFC <- long_data %>%
  select(
    ID,
    lateralisation_index_0.05,
    fx_lFFA_rMMPFC,
    fx_lFFA_lMMPFC,
    Age,
    MeanFD
  )

## Reshape the data and adjust columns

long_data_amygdala <- long_data_amygdala %>%
  ## Pivot the data into a long format with "Right" and "Left" hemispheres
  pivot_longer(
    cols = c(fx_lFFA_ramygdala, fx_lFFA_lamygdala),
    names_to = "region",
    values_to = "fx_lFFA_rlamygdala"
  ) %>%
  ## Create Hemisphere column based on the region name
  mutate(
    Hemisphere = case_when(
      region == "fx_lFFA_ramygdala" ~ "Right",
      region == "fx_lFFA_lamygdala" ~ "Left",
      TRUE ~ NA_character_
    )
  ) %>%
  ## Keep only relevant columns
  select(ID, lateralisation_index_0.05, fx_lFFA_rlamygdala, Age, MeanFD, Hemisphere)

long_data_MMPFC <- long_data_MMPFC %>%
  ## Pivot the data into a long format with "Right" and "Left" hemispheres
  pivot_longer(
    cols = c(fx_lFFA_rMMPFC, fx_lFFA_lMMPFC),
    names_to = "region",
    values_to = "fx_lFFA_rlMMPFC"
  ) %>%
  ## Create Hemisphere column based on the region name
  mutate(
    Hemisphere = case_when(
      region == "fx_lFFA_rMMPFC" ~ "Right",
      region == "fx_lFFA_lMMPFC" ~ "Left",
      TRUE ~ NA_character_
    )
  ) %>%
  ## Keep only relevant columns
  select(ID, lateralisation_index_0.05, fx_lFFA_rlMMPFC, Age, MeanFD, Hemisphere)

long_data_amygdala_selected <- long_data_amygdala %>%
  select(ID, Hemisphere, fx_lFFA_rlamygdala)
model_data <- merge(long_data_amygdala_selected, long_data_MMPFC, by = c("ID", "Hemisphere"))
model_data$Hemisphere <- as.factor(model_data$Hemisphere)

# Models

model_LI_lFFA_fx <- lmer(lateralisation_index_0.05 ~ fx_lFFA_rlMMPFC*Hemisphere*Age + fx_lFFA_rlamygdala*Hemisphere*Age + MeanFD + (1| ID), data = model_data)
summary(model_LI_lFFA_fx)

```

### Threshold p<0.10 (non-preregistered threshold)

Primary models 

```{r}

long_data <- child_LI

# Filter long data

long_data_amygdala <- long_data %>%
  select(
    ID,
    lateralisation_index_0.1,
    fx_rFFA_ramygdala,
    fx_rFFA_lamygdala,
    Age,
    MeanFD
  )

long_data_MMPFC <- long_data %>%
  select(
    ID,
    lateralisation_index_0.1,
    fx_rFFA_rMMPFC,
    fx_rFFA_lMMPFC,
    Age,
    MeanFD
  )

## Reshape the data and adjust columns

long_data_amygdala <- long_data_amygdala %>%
  ## Pivot the data into a long format with "Right" and "Left" hemispheres
  pivot_longer(
    cols = c(fx_rFFA_ramygdala, fx_rFFA_lamygdala),
    names_to = "region",
    values_to = "fx_rFFA_rlamygdala"
  ) %>%
  ## Create Hemisphere column based on the region name
  mutate(
    Hemisphere = case_when(
      region == "fx_rFFA_ramygdala" ~ "Right",
      region == "fx_rFFA_lamygdala" ~ "Left",
      TRUE ~ NA_character_
    )
  ) %>%
  ## Keep only relevant columns
  select(ID, lateralisation_index_0.1, fx_rFFA_rlamygdala, Age, MeanFD, Hemisphere)

long_data_MMPFC <- long_data_MMPFC %>%
  ## Pivot the data into a long format with "Right" and "Left" hemispheres
  pivot_longer(
    cols = c(fx_rFFA_rMMPFC, fx_rFFA_lMMPFC),
    names_to = "region",
    values_to = "fx_rFFA_rlMMPFC"
  ) %>%
  ## Create Hemisphere column based on the region name
  mutate(
    Hemisphere = case_when(
      region == "fx_rFFA_rMMPFC" ~ "Right",
      region == "fx_rFFA_lMMPFC" ~ "Left",
      TRUE ~ NA_character_
    )
  ) %>%
  ## Keep only relevant columns
  select(ID, lateralisation_index_0.1, fx_rFFA_rlMMPFC, Age, MeanFD, Hemisphere)

long_data_amygdala_selected <- long_data_amygdala %>%
  select(ID, Hemisphere, fx_rFFA_rlamygdala)
model_data <- merge(long_data_amygdala_selected, long_data_MMPFC, by = c("ID", "Hemisphere"))
model_data$Hemisphere <- as.factor(model_data$Hemisphere)

# Models

model_LI_rFFA <- lmer(lateralisation_index_0.1 ~ fx_rFFA_rlMMPFC*Hemisphere*Age + fx_rFFA_rlamygdala*Hemisphere*Age + MeanFD + (1| ID), data = model_data)
summary(model_LI_rFFA)

```

Secondary models

```{r}

long_data <- child_LI

# Filter long data

long_data_amygdala <- long_data %>%
  select(
    ID,
    lateralisation_index_0.1,
    fx_lFFA_ramygdala,
    fx_lFFA_lamygdala,
    Age,
    MeanFD
  )
long_data_MMPFC <- long_data %>%
  select(
    ID,
    lateralisation_index_0.1,
    fx_lFFA_rMMPFC,
    fx_lFFA_lMMPFC,
    Age,
    MeanFD
  )

## Reshape the data and adjust columns

long_data_amygdala <- long_data_amygdala %>%
  ## Pivot the data into a long format with "Right" and "Left" hemispheres
  pivot_longer(
    cols = c(fx_lFFA_ramygdala, fx_lFFA_lamygdala),
    names_to = "region",
    values_to = "fx_lFFA_rlamygdala"
  ) %>%
  ## Create Hemisphere column based on the region name
  mutate(
    Hemisphere = case_when(
      region == "fx_lFFA_ramygdala" ~ "Right",
      region == "fx_lFFA_lamygdala" ~ "Left",
      TRUE ~ NA_character_
    )
  ) %>%
  ## Keep only relevant columns
  select(ID, lateralisation_index_0.1, fx_lFFA_rlamygdala, Age, MeanFD, Hemisphere)

long_data_MMPFC <- long_data_MMPFC %>%
  ## Pivot the data into a long format with "Right" and "Left" hemispheres
  pivot_longer(
    cols = c(fx_lFFA_rMMPFC, fx_lFFA_lMMPFC),
    names_to = "region",
    values_to = "fx_lFFA_rlMMPFC"
  ) %>%
  ## Create Hemisphere column based on the region name
  mutate(
    Hemisphere = case_when(
      region == "fx_lFFA_rMMPFC" ~ "Right",
      region == "fx_lFFA_lMMPFC" ~ "Left",
      TRUE ~ NA_character_
    )
  ) %>%
  ## Keep only relevant columns
  select(ID, lateralisation_index_0.1, fx_lFFA_rlMMPFC, Age, MeanFD, Hemisphere)

long_data_amygdala_selected <- long_data_amygdala %>%
  select(ID, Hemisphere, fx_lFFA_rlamygdala)
model_data <- merge(long_data_amygdala_selected, long_data_MMPFC, by = c("ID", "Hemisphere"))
model_data$Hemisphere <- as.factor(model_data$Hemisphere)

# Models

model_LI_lFFA_fx <- lmer(lateralisation_index_0.1 ~ fx_lFFA_rlMMPFC*Hemisphere*Age + fx_lFFA_rlamygdala*Hemisphere*Age + MeanFD + (1| ID), data = model_data)
summary(model_LI_lFFA_fx)

```

Our preregistered linear mixed-effects models did not converge, likely due to the repeated-measures factor being assigned to the independent variable instead of the dependent variable. To test the same associations, we instead reversed the independent and dependent variables and ran separate linear mixed-effects models for each ROI pair.

### Alternative linear mixed-effects models for threshold p<0.05 (non-preregistered)

Primary models

```{r}

# Data wrangling

long_data <- child_LI

long_data_amygdala <- long_data %>%
  select(
    ID,
    lateralisation_index_0.05,
    fx_rFFA_ramygdala,
    fx_rFFA_lamygdala,
    Age,
    MeanFD
  )
long_data_MMPFC <- long_data %>%
  select(
    ID,
    lateralisation_index_0.05,
    fx_rFFA_rMMPFC,
    fx_rFFA_lMMPFC,
    Age,
    MeanFD
  )

long_data_STS <- long_data %>%
  select(
    ID,
    lateralisation_index_0.05,
    fx_rFFA_rSTS,
    fx_rFFA_lSTS,
    Age,
    MeanFD
  )

## Reshape the data and adjust columns

long_data_amygdala <- long_data_amygdala %>%
  ## Pivot the data into a long format with "Right" and "Left" hemispheres
  pivot_longer(
    cols = c(fx_rFFA_ramygdala, fx_rFFA_lamygdala),
    names_to = "region",
    values_to = "fx_rFFA_rlamygdala"
  ) %>%
  ## Create Hemisphere column based on the region name
  mutate(
    Hemisphere = case_when(
      region == "fx_rFFA_ramygdala" ~ "Right",
      region == "fx_rFFA_lamygdala" ~ "Left",
      TRUE ~ NA_character_
    )
  ) %>%
  select(ID, lateralisation_index_0.05, fx_rFFA_rlamygdala, Age, MeanFD, Hemisphere)

long_data_MMPFC <- long_data_MMPFC %>%
  pivot_longer(
    cols = c(fx_rFFA_rMMPFC, fx_rFFA_lMMPFC),
    names_to = "region",
    values_to = "fx_rFFA_rlMMPFC"
  ) %>%
  mutate(
    Hemisphere = case_when(
      region == "fx_rFFA_rMMPFC" ~ "Right",
      region == "fx_rFFA_lMMPFC" ~ "Left",
      TRUE ~ NA_character_
    )
  ) %>%
  select(ID, lateralisation_index_0.05, fx_rFFA_rlMMPFC, Age, MeanFD, Hemisphere)

long_data_STS <- long_data_STS %>%
  pivot_longer(
    cols = c(fx_rFFA_rSTS, fx_rFFA_lSTS),
    names_to = "region",
    values_to = "fx_rFFA_rlSTS"
  ) %>%
  mutate(
    Hemisphere = case_when(
      region == "fx_rFFA_rSTS" ~ "Right",
      region == "fx_rFFA_lSTS" ~ "Left",
      TRUE ~ NA_character_
    )
  ) %>%
  select(ID, lateralisation_index_0.05, fx_rFFA_rlSTS, Age, MeanFD, Hemisphere)

# Models

## MMPFC

model_LI_0.05_rFFA_MMPFC_fx <-lmer(fx_rFFA_rlMMPFC ~ lateralisation_index_0.05*Hemisphere*Age + MeanFD + (1|ID), data = long_data_MMPFC)
summary(model_LI_0.05_rFFA_MMPFC_fx)

### No interaction effects are significant, so models are run without interaction effects

model_LI_0.05_rFFA_MMPFC_fx <- lmer(fx_rFFA_rlMMPFC ~ lateralisation_index_0.05 + Hemisphere + Age + MeanFD + (1| ID), data = long_data_MMPFC)
summary_LI_0.05_rFFA_MMPFC_fx <- tidy(model_LI_0.05_rFFA_MMPFC_fx)
summary_LI_0.05_rFFA_MMPFC_fx

## Amygdala

model_LI_0.05_rFFA_amygdala_fx <- lmer(fx_rFFA_rlamygdala ~ lateralisation_index_0.05*Hemisphere*Age + MeanFD + (1|ID), data = long_data_amygdala)
summary(model_LI_0.05_rFFA_amygdala_fx)

### No interaction effects are significant, so models are run without interaction effects 

model_LI_0.05_rFFA_amygdala_fx <- lmer(fx_rFFA_rlamygdala ~ lateralisation_index_0.05 + Hemisphere + Age + MeanFD + (1| ID), data = long_data_amygdala)
summary_LI_0.05_rFFA_amygdala_fx <- tidy(model_LI_0.05_rFFA_amygdala_fx)
summary_LI_0.05_rFFA_amygdala_fx

## STS

model_LI_0.05_rFFA_STS_fx <- lmer(fx_rFFA_rlSTS ~ lateralisation_index_0.05*Hemisphere*Age + MeanFD + (1|ID), data = long_data_STS)
summary(model_LI_0.05_rFFA_STS_fx)

### No interaction effects are significant, so models are run without interaction effects 

model_LI_0.05_rFFA_STS_fx <- lmer(fx_rFFA_rlSTS ~ lateralisation_index_0.05 + Hemisphere + Age + MeanFD + (1| ID), data = long_data_STS)
summary_LI_0.05_rFFA_STS_fx <- tidy(model_LI_0.05_rFFA_STS_fx)
summary_LI_0.05_rFFA_STS_fx

```

Secondary models 

```{r}

# Data wrangling

long_data <- child_LI

long_data_amygdala <- long_data %>%
  select(
    ID,
    lateralisation_index_0.05,
    fx_lFFA_ramygdala,
    fx_lFFA_lamygdala,
    Age,
    MeanFD
  )
long_data_MMPFC <- long_data %>%
  select(
    ID,
    lateralisation_index_0.05,
    fx_lFFA_rMMPFC,
    fx_lFFA_lMMPFC,
    Age,
    MeanFD
  )

long_data_STS <- long_data %>%
  select(
    ID,
    lateralisation_index_0.05,
    fx_lFFA_rSTS,
    fx_lFFA_lSTS,
    Age,
    MeanFD
  )

## Reshape the data and adjust columns

long_data_amygdala <- long_data_amygdala %>%
  ## Pivot the data into a long format with "Right" and "Left" hemispheres
  pivot_longer(
    cols = c(fx_lFFA_ramygdala, fx_lFFA_lamygdala),
    names_to = "region",
    values_to = "fx_lFFA_rlamygdala"
  ) %>%
  ## Create Hemisphere column based on the region name
  mutate(
    Hemisphere = case_when(
      region == "fx_lFFA_ramygdala" ~ "Right",
      region == "fx_lFFA_lamygdala" ~ "Left",
      TRUE ~ NA_character_
    )
  ) %>%
  select(ID, lateralisation_index_0.05, fx_lFFA_rlamygdala, Age, MeanFD, Hemisphere)

long_data_MMPFC <- long_data_MMPFC %>%
  pivot_longer(
    cols = c(fx_lFFA_rMMPFC, fx_lFFA_lMMPFC),
    names_to = "region",
    values_to = "fx_lFFA_rlMMPFC"
  ) %>%
  mutate(
    Hemisphere = case_when(
      region == "fx_lFFA_rMMPFC" ~ "Right",
      region == "fx_lFFA_lMMPFC" ~ "Left",
      TRUE ~ NA_character_
    )
  ) %>%
  select(ID, lateralisation_index_0.05, fx_lFFA_rlMMPFC, Age, MeanFD, Hemisphere)

long_data_STS <- long_data_STS %>%
  pivot_longer(
    cols = c(fx_lFFA_rSTS, fx_lFFA_lSTS),
    names_to = "region",
    values_to = "fx_lFFA_rlSTS"
  ) %>%
  mutate(
    Hemisphere = case_when(
      region == "fx_lFFA_rSTS" ~ "Right",
      region == "fx_lFFA_lSTS" ~ "Left",
      TRUE ~ NA_character_
    )
  ) %>%
  select(ID, lateralisation_index_0.05, fx_lFFA_rlSTS, Age, MeanFD, Hemisphere)

# Models

## MMPFC

model_LI_0.05_lFFA_MMPFC_fx <-lmer(fx_lFFA_rlMMPFC ~ lateralisation_index_0.05*Hemisphere*Age + MeanFD + (1|ID), data = long_data_MMPFC)
summary(model_LI_0.05_lFFA_MMPFC_fx)

### No interaction effects are significant, so models are run without interaction effects

model_LI_0.05_lFFA_MMPFC_fx <- lmer(fx_lFFA_rlMMPFC ~ lateralisation_index_0.05 + Hemisphere + Age + MeanFD + (1| ID), data = long_data_MMPFC)
summary_LI_0.05_lFFA_MMPFC_fx <- tidy(model_LI_0.05_lFFA_MMPFC_fx)
summary_LI_0.05_lFFA_MMPFC_fx

## Amygdala

model_LI_0.05_lFFA_amygdala_fx <- lmer(fx_lFFA_rlamygdala ~ lateralisation_index_0.05*Hemisphere*Age + MeanFD + (1|ID), data = long_data_amygdala)
summary(model_LI_0.05_lFFA_amygdala_fx)

### No interaction effects are significant, so models are run without interaction effects 

model_LI_0.05_lFFA_amygdala_fx <- lmer(fx_lFFA_rlamygdala ~ lateralisation_index_0.05 + Hemisphere + Age + MeanFD + (1| ID), data = long_data_amygdala)
summary_LI_0.05_lFFA_amygdala_fx <- tidy(model_LI_0.05_lFFA_amygdala_fx)
summary_LI_0.05_lFFA_amygdala_fx

## STS

model_LI_0.05_lFFA_STS_fx <- lmer(fx_lFFA_rlSTS ~ lateralisation_index_0.05*Hemisphere*Age + MeanFD + (1|ID), data = long_data_STS)
summary(model_LI_0.05_lFFA_STS_fx)

### No interaction effects are significant, so models are run without interaction effects 

model_LI_0.05_lFFA_STS_fx <- lmer(fx_lFFA_rlSTS ~ lateralisation_index_0.05 + Hemisphere + Age + MeanFD + (1| ID), data = long_data_STS)
summary_LI_0.05_lFFA_STS_fx <- tidy(model_LI_0.05_lFFA_STS_fx)
summary_LI_0.05_lFFA_STS_fx

```

Save models

```{r}

all_summaries <- bind_rows(
  summary_LI_0.05_rFFA_MMPFC_fx %>% mutate(model = "LI_0.05_fx_rFFA_MMPFC", Label = "Primary"),
  summary_LI_0.05_rFFA_amygdala_fx %>% mutate(model = "LI_0.05_fx_rFFA_amygdala", Label = "Primary"),
  summary_LI_0.05_rFFA_STS_fx %>% mutate(model = "LI_0.05_fx_rFFA_STS", Label = "Primary"),
  summary_LI_0.05_lFFA_MMPFC_fx %>% mutate(model = "LI_0.05_fx_lFFA_MMPFC", Label = "Secondary"),
  summary_LI_0.05_lFFA_amygdala_fx %>% mutate(model = "LI_0.05_fx_lFFA_amygdala", Label = "Secondary"),
  summary_LI_0.05_lFFA_STS_fx %>% mutate(model = "LI_0.05_fx_lFFA_STS", Label = "Secondary"),
) %>%
  mutate(
    estimate = round(estimate, 2),
    std.error = round(std.error, 2),
    statistic = round(statistic, 2),
    df = round(df, 0),
    p.value = if_else(
      p.value < 0.001,
      format(p.value, scientific = TRUE, digits = 4),
      sprintf("%.3f", p.value)
    )
  )

write.csv(all_summaries, here("results/RQ3", "LI_0.05_fx.csv"), row.names = FALSE)

```

### Alternative linear mixed-effects models for threshold p<0.10 (non-preregistered)

Primary analyses

```{r}

# Data wrangling

long_data <- child_LI

long_data_amygdala <- long_data %>%
  select(
    ID,
    lateralisation_index_0.1,
    fx_rFFA_ramygdala,
    fx_rFFA_lamygdala,
    Age,
    MeanFD
  )
long_data_MMPFC <- long_data %>%
  select(
    ID,
    lateralisation_index_0.1,
    fx_rFFA_rMMPFC,
    fx_rFFA_lMMPFC,
    Age,
    MeanFD
  )

long_data_STS <- long_data %>%
  select(
    ID,
    lateralisation_index_0.1,
    fx_rFFA_rSTS,
    fx_rFFA_lSTS,
    Age,
    MeanFD
  )

## Reshape the data and adjust columns

long_data_amygdala <- long_data_amygdala %>%
  ## Pivot the data into a long format with "Right" and "Left" hemispheres
  pivot_longer(
    cols = c(fx_rFFA_ramygdala, fx_rFFA_lamygdala),
    names_to = "region",
    values_to = "fx_rFFA_rlamygdala"
  ) %>%
  ## Create Hemisphere column based on the region name
  mutate(
    Hemisphere = case_when(
      region == "fx_rFFA_ramygdala" ~ "Right",
      region == "fx_rFFA_lamygdala" ~ "Left",
      TRUE ~ NA_character_
    )
  ) %>%
  select(ID, lateralisation_index_0.1, fx_rFFA_rlamygdala, Age, MeanFD, Hemisphere)

long_data_MMPFC <- long_data_MMPFC %>%
  pivot_longer(
    cols = c(fx_rFFA_rMMPFC, fx_rFFA_lMMPFC),
    names_to = "region",
    values_to = "fx_rFFA_rlMMPFC"
  ) %>%
  mutate(
    Hemisphere = case_when(
      region == "fx_rFFA_rMMPFC" ~ "Right",
      region == "fx_rFFA_lMMPFC" ~ "Left",
      TRUE ~ NA_character_
    )
  ) %>%
  select(ID, lateralisation_index_0.1, fx_rFFA_rlMMPFC, Age, MeanFD, Hemisphere)

long_data_STS <- long_data_STS %>%
  pivot_longer(
    cols = c(fx_rFFA_rSTS, fx_rFFA_lSTS),
    names_to = "region",
    values_to = "fx_rFFA_rlSTS"
  ) %>%
  mutate(
    Hemisphere = case_when(
      region == "fx_rFFA_rSTS" ~ "Right",
      region == "fx_rFFA_lSTS" ~ "Left",
      TRUE ~ NA_character_
    )
  ) %>%
  select(ID, lateralisation_index_0.1, fx_rFFA_rlSTS, Age, MeanFD, Hemisphere)

# Models

## MMPFC

model_LI_0.1_rFFA_MMPFC_fx <-lmer(fx_rFFA_rlMMPFC ~ lateralisation_index_0.1*Hemisphere*Age + MeanFD + (1|ID), data = long_data_MMPFC)
summary(model_LI_0.1_rFFA_MMPFC_fx)

### No interaction effects are significant except for Hemisphere:age, so models are run without interaction effects except for Hemisphere:age

model_LI_0.1_rFFA_MMPFC_fx <- lmer(fx_rFFA_rlMMPFC ~ lateralisation_index_0.1 + Hemisphere + Age + lateralisation_index_0.1:Hemisphere + MeanFD + (1| ID), data = long_data_MMPFC)
summary_LI_0.1_rFFA_MMPFC_fx <- tidy(model_LI_0.1_rFFA_MMPFC_fx)
summary_LI_0.1_rFFA_MMPFC_fx

## Amygdala

model_LI_0.1_rFFA_amygdala_fx <- lmer(fx_rFFA_rlamygdala ~ lateralisation_index_0.1*Hemisphere*Age + MeanFD + (1|ID), data = long_data_amygdala)
summary(model_LI_0.1_rFFA_amygdala_fx)

### No interaction effects are significant, so models are run without interaction effects 

model_LI_0.1_rFFA_amygdala_fx <- lmer(fx_rFFA_rlamygdala ~ lateralisation_index_0.1 + Hemisphere + Age + MeanFD + (1| ID), data = long_data_amygdala)
summary_LI_0.1_rFFA_amygdala_fx <- tidy(model_LI_0.1_rFFA_amygdala_fx)
summary_LI_0.1_rFFA_amygdala_fx

## STS

model_LI_0.1_rFFA_STS_fx <- lmer(fx_rFFA_rlSTS ~ lateralisation_index_0.1*Hemisphere*Age + MeanFD + (1|ID), data = long_data_STS)
summary(model_LI_0.1_rFFA_STS_fx)

### No interaction effects are significant, so models are run without interaction effects 

model_LI_0.1_rFFA_STS_fx <- lmer(fx_rFFA_rlSTS ~ lateralisation_index_0.1 + Hemisphere + Age + MeanFD + (1| ID), data = long_data_STS)
summary_LI_0.1_rFFA_STS_fx <- tidy(model_LI_0.1_rFFA_STS_fx)
summary_LI_0.1_rFFA_STS_fx

```

Secondary analyses

```{r}

# Data wrangling

long_data <- child_LI

long_data_amygdala <- long_data %>%
  select(
    ID,
    lateralisation_index_0.1,
    fx_lFFA_ramygdala,
    fx_lFFA_lamygdala,
    Age,
    MeanFD
  )
long_data_MMPFC <- long_data %>%
  select(
    ID,
    lateralisation_index_0.1,
    fx_lFFA_rMMPFC,
    fx_lFFA_lMMPFC,
    Age,
    MeanFD
  )

long_data_STS <- long_data %>%
  select(
    ID,
    lateralisation_index_0.1,
    fx_lFFA_rSTS,
    fx_lFFA_lSTS,
    Age,
    MeanFD
  )

## Reshape the data and adjust columns

long_data_amygdala <- long_data_amygdala %>%
  ## Pivot the data into a long format with "Right" and "Left" hemispheres
  pivot_longer(
    cols = c(fx_lFFA_ramygdala, fx_lFFA_lamygdala),
    names_to = "region",
    values_to = "fx_lFFA_rlamygdala"
  ) %>%
  ## Create Hemisphere column based on the region name
  mutate(
    Hemisphere = case_when(
      region == "fx_lFFA_ramygdala" ~ "Right",
      region == "fx_lFFA_lamygdala" ~ "Left",
      TRUE ~ NA_character_
    )
  ) %>%
  select(ID, lateralisation_index_0.1, fx_lFFA_rlamygdala, Age, MeanFD, Hemisphere)

long_data_MMPFC <- long_data_MMPFC %>%
  pivot_longer(
    cols = c(fx_lFFA_rMMPFC, fx_lFFA_lMMPFC),
    names_to = "region",
    values_to = "fx_lFFA_rlMMPFC"
  ) %>%
  mutate(
    Hemisphere = case_when(
      region == "fx_lFFA_rMMPFC" ~ "Right",
      region == "fx_lFFA_lMMPFC" ~ "Left",
      TRUE ~ NA_character_
    )
  ) %>%
  select(ID, lateralisation_index_0.1, fx_lFFA_rlMMPFC, Age, MeanFD, Hemisphere)

long_data_STS <- long_data_STS %>%
  pivot_longer(
    cols = c(fx_lFFA_rSTS, fx_lFFA_lSTS),
    names_to = "region",
    values_to = "fx_lFFA_rlSTS"
  ) %>%
  mutate(
    Hemisphere = case_when(
      region == "fx_lFFA_rSTS" ~ "Right",
      region == "fx_lFFA_lSTS" ~ "Left",
      TRUE ~ NA_character_
    )
  ) %>%
  select(ID, lateralisation_index_0.1, fx_lFFA_rlSTS, Age, MeanFD, Hemisphere)

# Models

## MMPFC

model_LI_0.1_lFFA_MMPFC_fx <-lmer(fx_lFFA_rlMMPFC ~ lateralisation_index_0.1*Hemisphere*Age + MeanFD + (1|ID), data = long_data_MMPFC)
summary(model_LI_0.1_lFFA_MMPFC_fx)

### No interaction effects are significant, so models are run without interaction effects

model_LI_0.1_lFFA_MMPFC_fx <- lmer(fx_lFFA_rlMMPFC ~ lateralisation_index_0.1 + Hemisphere + Age + MeanFD + (1| ID), data = long_data_MMPFC)
summary_LI_0.1_lFFA_MMPFC_fx <- tidy(model_LI_0.1_lFFA_MMPFC_fx)
summary_LI_0.1_lFFA_MMPFC_fx

## Amygdala

model_LI_0.1_lFFA_amygdala_fx <- lmer(fx_lFFA_rlamygdala ~ lateralisation_index_0.1*Hemisphere*Age + MeanFD + (1|ID), data = long_data_amygdala)
summary(model_LI_0.1_lFFA_amygdala_fx)

### No interaction effects are significant, so models are run without interaction effects 

model_LI_0.1_lFFA_amygdala_fx <- lmer(fx_lFFA_rlamygdala ~ lateralisation_index_0.1 + Hemisphere + Age + MeanFD + (1| ID), data = long_data_amygdala)
summary_LI_0.1_lFFA_amygdala_fx <- tidy(model_LI_0.1_lFFA_amygdala_fx)
summary_LI_0.1_lFFA_amygdala_fx

## STS

model_LI_0.1_lFFA_STS_fx <- lmer(fx_lFFA_rlSTS ~ lateralisation_index_0.1*Hemisphere*Age + MeanFD + (1|ID), data = long_data_STS)
summary(model_LI_0.1_lFFA_STS_fx)

### No interaction effects are significant, so models are run without interaction effects 

model_LI_0.1_lFFA_STS_fx <- lmer(fx_lFFA_rlSTS ~ lateralisation_index_0.1 + Hemisphere + Age + MeanFD + (1| ID), data = long_data_STS)
summary_LI_0.1_lFFA_STS_fx <- tidy(model_LI_0.1_lFFA_STS_fx)
summary_LI_0.1_lFFA_STS_fx

```

Save models

```{r}

all_summaries <- bind_rows(
  summary_LI_0.1_rFFA_MMPFC_fx %>% mutate(model = "LI_0.1_fx_rFFA_MMPFC", Label = "Primary"),
  summary_LI_0.1_rFFA_amygdala_fx %>% mutate(model = "LI_0.1_fx_rFFA_amygdala", Label = "Primary"),
  summary_LI_0.1_rFFA_STS_fx %>% mutate(model = "LI_0.1_fx_rFFA_STS", Label = "Primary"),
  summary_LI_0.1_lFFA_MMPFC_fx %>% mutate(model = "LI_0.1_fx_lFFA_MMPFC", Label = "Secondary"),
  summary_LI_0.1_lFFA_amygdala_fx %>% mutate(model = "LI_0.1_fx_lFFA_amygdala", Label = "Secondary"),
  summary_LI_0.1_lFFA_STS_fx %>% mutate(model = "LI_0.1_fx_lFFA_STS", Label = "Secondary"),
) %>%
  mutate(
    estimate = round(estimate, 2),
    std.error = round(std.error, 2),
    statistic = round(statistic, 2),
    df = round(df, 0),
    p.value = if_else(
      p.value < 0.001,
      format(p.value, scientific = TRUE, digits = 4),
      sprintf("%.3f", p.value)
    )
  )

write.csv(all_summaries, here("results/RQ3", "LI_0.1_fx.csv"), row.names = FALSE)

```

### Plots

```{r}

# Data wrangling

data_plot <- read_csv(here("processed_data", "child_MRIvariables.csv"), col_names=TRUE)
data_plot <- data_plot[,c(1, 202:231)]
data_plot <- data_plot %>%
  rename_with(~ sub("^zscored_", "", .x), starts_with("zscored_"))
data_plot <- data_plot %>%
  pivot_longer(
    cols = starts_with("fx_"),
    names_to = c("Region1", "Region2"),
    names_pattern = "fx_(.+)_(.+)",
    values_to = "zscored_value"
  )
data_plot <- data_plot %>%
  mutate(
    Hemisphere = ifelse(grepl("^r", Region2), "right", "left"),
    Region2 = sub("^[rl]", "", Region2)
  )
data_plot_rFFA_MMPFC <- data_plot %>%
  filter(Region2 == "MMPFC", Region1 == "rFFA")
data_plot_lFFA_MMPFC <- data_plot %>%
  filter(Region2 == "MMPFC", Region1 == "lFFA")
data_plot_rFFA_amygdala <- data_plot %>%
  filter(Region2 == "amygdala", Region1 == "rFFA")
data_plot_lFFA_amygdala <- data_plot %>%
  filter(Region2 == "amygdala", Region1 == "lFFA")
data_plot_rFFA_STS <- data_plot %>%
  filter(Region2 == "STS", Region1 == "rFFA")
data_plot_lFFA_STS <- data_plot %>%
  filter(Region2 == "STS", Region1 == "lFFA")

# Colours

custom_colours_amygdala <- c("#E1AA9F", "#D34835")
custom_colours_MMPFC <- c("#87BACF", "#578CAD")
custom_colours_FFA <- c("#C39EDA", "#652975")
custom_colours_STS <- c("#FFF865", "#FFCE1B")

# Define a base theme to avoid repetition

base_theme <- theme_minimal() +
  theme(
    strip.text = element_text(size = 14, face = "bold"),
    strip.background = element_blank(),
    axis.line.x = element_blank(),
    axis.text = element_text(size = 16),
    axis.title = element_text(size = 14, face = "bold"),
    plot.title = element_text(size = 14, hjust = 0.5, face = "bold"),
    legend.text = element_text(size = 16),
    legend.title = element_text(size = 14, face = "bold")
  )

# Function to create ggplots efficiently

create_plot <- function(data, x_var, y_var, color_values, x_label, y_label = "", legend_title = "Hemisphere", legend_position = "none", remove_y_axis_labels = FALSE) {
  
  plot <- ggplot(data, aes(x = {{ x_var }}, y = {{ y_var }}, color = Hemisphere)) +
    geom_point(alpha = 0.4, size = 2.8, shape = 19) +
    geom_smooth(method = "lm", se = FALSE, linetype = "solid", linewidth = 2) +
    scale_color_manual(values = color_values) +
    labs(x = x_label, y = y_label, color = legend_title) +
    base_theme +
    theme(
      legend.position = legend_position,
      axis.line.x = element_blank(),
      plot.title = element_text(hjust = 0.5, size = 14, face = "bold"),
      axis.title.y = element_text(size = 14, face = "bold"),
      axis.text.y = element_text(size = 12)
    ) +
    coord_cartesian(ylim = c(-1, 1)) +  
    scale_x_continuous(breaks = c(-2, 0, 2))

  if (remove_y_axis_labels) {
    plot <- plot + theme(
      axis.title.y = element_blank(),
      axis.text.y = element_blank()
    )
  }

  return(plot)
}

# Threshold p<0.05

plot_lFFA_MMPFC <- create_plot(data_plot_lFFA_MMPFC, zscored_value, lateralisation_index_0.05, custom_colours_MMPFC, "", "Lateralisation Index (p<0.05)", legend_title = "MMPFC Hemisphere")
plot_lFFA_amygdala <- create_plot(data_plot_lFFA_amygdala, zscored_value, lateralisation_index_0.05, custom_colours_amygdala, "Functional connectivity between left FFA and region", "Lateralisation Index (p<0.05)", legend_title = "Amygdala Hemisphere", legend_position = "bottom", remove_y_axis_labels = TRUE)
plot_lFFA_STS <- create_plot(data_plot_lFFA_STS, zscored_value, lateralisation_index_0.05, custom_colours_STS, "", "", legend_title = "STS Hemisphere", legend_position = "bottom", remove_y_axis_labels = TRUE)

plot_rFFA_MMPFC <- create_plot(data_plot_rFFA_MMPFC, zscored_value, lateralisation_index_0.05, custom_colours_MMPFC, "", "Lateralisation Index (p<0.05)", legend_title = "MMPFC Hemisphere", legend_position = "bottom")
plot_rFFA_amygdala <- create_plot(data_plot_rFFA_amygdala, zscored_value, lateralisation_index_0.05, custom_colours_amygdala, "Functional connectivity between right FFA and region", "Lateralisation Index (p<0.05)", legend_title = "Amygdala Hemisphere", remove_y_axis_labels = TRUE)
plot_rFFA_STS <- create_plot(data_plot_rFFA_STS, zscored_value, lateralisation_index_0.05, custom_colours_STS, "", "", legend_title = "STS Hemisphere", legend_position = "bottom", remove_y_axis_labels = TRUE)

## Combine plots into a single row

LI_fx_rFFA <- (plot_rFFA_MMPFC | plot_rFFA_amygdala | plot_rFFA_STS) +  
  plot_layout(ncol = 3, guides = "collect") +
  plot_annotation(
    title = ""
  ) &
  theme(
    legend.position = "bottom",
    legend.text = element_text(size = 12),
    legend.title = element_text(size = 12),
    plot.title = element_text(size = 14, hjust = 0.5, face = "bold")
  )
LI_fx_lFFA <- (plot_lFFA_MMPFC | plot_lFFA_amygdala | plot_lFFA_STS) +  
  plot_layout(ncol = 3, guides = "collect") +
  plot_annotation(
    title = ""
  ) &
  theme(
    legend.position = "bottom",
    legend.text = element_text(size = 12),
    legend.title = element_text(size = 12),
    plot.title = element_text(size = 14, hjust = 0.5, face = "bold")
  )

## Save plots

ggsave(here("results/figures", "LI_0.05_fx_rFFA.png"), plot = LI_fx_rFFA, width = 10, height = 5, units = "in", dpi = 300)
ggsave(here("results/figures", "LI_0.05_fx_lFFA.png"), plot = LI_fx_lFFA, width = 10, height = 5, units = "in", dpi = 300)

# Threshold p<0.10

plot_lFFA_MMPFC <- create_plot(data_plot_lFFA_MMPFC, zscored_value, lateralisation_index_0.1, custom_colours_MMPFC, "", "Lateralisation Index (p<0.10)", legend_title = "MMPFC Hemisphere")
plot_lFFA_amygdala <- create_plot(data_plot_lFFA_amygdala, zscored_value, lateralisation_index_0.1, custom_colours_amygdala, "Functional connectivity between left FFA and region", "Lateralisation Index (p<0.10)", legend_title = "Amygdala Hemisphere", legend_position = "bottom", remove_y_axis_labels = TRUE)
plot_lFFA_STS <- create_plot(data_plot_lFFA_STS, zscored_value, lateralisation_index_0.1, custom_colours_STS, "", "", legend_title = "STS Hemisphere", legend_position = "bottom", remove_y_axis_labels = TRUE)

plot_rFFA_MMPFC <- create_plot(data_plot_rFFA_MMPFC, zscored_value, lateralisation_index_0.1, custom_colours_MMPFC, "", "Lateralisation Index (p<0.10)", legend_title = "MMPFC Hemisphere")+
  annotate(
    "text",
    x = Inf, y = -Inf,                        # bottom right corner
    label = "LI effect:\nβ(SE)=0.22(0.10), p=0.027;
    \n LI x Hemisphere (right) effect\nβ(SE)=-0.23(0.07), p<0.001",    # your annotation
    hjust = 1.05,      # slightly >1 for proper right alignment
    vjust = -0.25,      # nudges text up from bottom
    size = 4,
    color = "black"
)
plot_rFFA_amygdala <- create_plot(data_plot_rFFA_amygdala, zscored_value, lateralisation_index_0.1, custom_colours_amygdala, "Functional connectivity between right FFA and region", "Lateralisation Index (p<0.10)", legend_title = "Amygdala Hemisphere", remove_y_axis_labels = TRUE)
plot_rFFA_STS <- create_plot(data_plot_rFFA_STS, zscored_value, lateralisation_index_0.1, custom_colours_STS, "", "", legend_title = "STS Hemisphere", legend_position = "bottom", remove_y_axis_labels = TRUE)

## Combine plots into a single row

LI_fx_rFFA <- (plot_rFFA_MMPFC | plot_rFFA_amygdala | plot_rFFA_STS) +  
  plot_layout(ncol = 3, guides = "collect") +
  plot_annotation(
    title = ""
  ) &
  theme(
    legend.position = "bottom",
    legend.text = element_text(size = 12),
    legend.title = element_text(size = 12),
    plot.title = element_text(size = 14, hjust = 0.5, face = "bold")
  )
LI_fx_lFFA <- (plot_lFFA_MMPFC | plot_lFFA_amygdala | plot_lFFA_STS) +  
  plot_layout(ncol = 3, guides = "collect") +
  plot_annotation(
    title = ""
  ) &
  theme(
    legend.position = "bottom",
    legend.text = element_text(size = 12),
    legend.title = element_text(size = 12),
    plot.title = element_text(size = 14, hjust = 0.5, face = "bold")
  )

## Save plots

ggsave(here("results/figures", "LI_0.1_fx_rFFA.png"), plot = LI_fx_rFFA, width = 10, height = 5, units = "in", dpi = 300)
ggsave(here("results/figures", "LI_0.1_fx_lFFA.png"), plot = LI_fx_lFFA, width = 10, height = 5, units = "in", dpi = 300)

```


## Section II: Functional maturation of MMPFC/amygdala drives lateralisation of FFA response

### Threshold p<0.05

```{r}

long_data <- child_LI

# Filter long data

long_data_amygdala <- long_data %>%
  select(
    ID,
    lateralisation_index_0.05,
    fm_ramygdala,
    fm_lamygdala,
    Age,
    MeanFD
  )
long_data_MMPFC <- long_data %>%
  select(
    ID,
    lateralisation_index_0.05,
    fm_rMMPFC,
    fm_lMMPFC,
    Age,
    MeanFD
  )

## Reshape the data and adjust columns

long_data_amygdala <- long_data_amygdala %>%
  ## Pivot the data into a long format with "Right" and "Left" hemispheres
  pivot_longer(
    cols = c(fm_ramygdala, fm_lamygdala),
    names_to = "region",
    values_to = "fm_rlamygdala"
  ) %>%
  ## Create Hemisphere column based on the region name
  mutate(
    Hemisphere = case_when(
      region == "fm_ramygdala" ~ "Right",
      region == "fm_lamygdala" ~ "Left",
      TRUE ~ NA_character_
    )
  ) %>%
  ## Keep only relevant columns
  select(ID, lateralisation_index_0.05, fm_rlamygdala, Age, MeanFD, Hemisphere)

long_data_MMPFC <- long_data_MMPFC %>%
  ## Pivot the data into a long format with "Right" and "Left" hemispheres
  pivot_longer(
    cols = c(fm_rMMPFC, fm_lMMPFC),
    names_to = "region",
    values_to = "fm_rlMMPFC"
  ) %>%
  ## Create Hemisphere column based on the region name
  mutate(
    Hemisphere = case_when(
      region == "fm_rMMPFC" ~ "Right",
      region == "fm_lMMPFC" ~ "Left",
      TRUE ~ NA_character_
    )
  ) %>%
  ## Keep only relevant columns
  select(ID, lateralisation_index_0.05, fm_rlMMPFC, Age, MeanFD, Hemisphere)

long_data_amygdala_selected <- long_data_amygdala %>%
  select(ID, Hemisphere, fm_rlamygdala)
model_data <- merge(long_data_amygdala_selected, long_data_MMPFC, by = c("ID", "Hemisphere"))
model_data$Hemisphere <- as.factor(model_data$Hemisphere)

# Models 

model_LI_fm <- lmer(lateralisation_index_0.05 ~ fm_rlMMPFC*Hemisphere*Age + fm_rlamygdala*Hemisphere*Age + MeanFD + (1| ID), data = model_data)
summary(model_LI_fm)

```

### Threshold p<0.10

```{r}

long_data <- child_LI

# Filter long data

long_data_amygdala <- long_data %>%
  select(
    ID,
    lateralisation_index_0.1,
    fm_ramygdala,
    fm_lamygdala,
    Age,
    MeanFD
  )
long_data_MMPFC <- long_data %>%
  select(
    ID,
    lateralisation_index_0.1,
    fm_rMMPFC,
    fm_lMMPFC,
    Age,
    MeanFD
  )

## Reshape the data and adjust columns

long_data_amygdala <- long_data_amygdala %>%
  ## Pivot the data into a long format with "Right" and "Left" hemispheres
  pivot_longer(
    cols = c(fm_ramygdala, fm_lamygdala),
    names_to = "region",
    values_to = "fm_rlamygdala"
  ) %>%
  ## Create Hemisphere column based on the region name
  mutate(
    Hemisphere = case_when(
      region == "fm_ramygdala" ~ "Right",
      region == "fm_lamygdala" ~ "Left",
      TRUE ~ NA_character_
    )
  ) %>%
  ## Keep only relevant columns
  select(ID, lateralisation_index_0.1, fm_rlamygdala, Age, MeanFD, Hemisphere)

long_data_MMPFC <- long_data_MMPFC %>%
  ## Pivot the data into a long format with "Right" and "Left" hemispheres
  pivot_longer(
    cols = c(fm_rMMPFC, fm_lMMPFC),
    names_to = "region",
    values_to = "fm_rlMMPFC"
  ) %>%
  ## Create Hemisphere column based on the region name
  mutate(
    Hemisphere = case_when(
      region == "fm_rMMPFC" ~ "Right",
      region == "fm_lMMPFC" ~ "Left",
      TRUE ~ NA_character_
    )
  ) %>%
  ## Keep only relevant columns
  select(ID, lateralisation_index_0.1, fm_rlMMPFC, Age, MeanFD, Hemisphere)

long_data_amygdala_selected <- long_data_amygdala %>%
  select(ID, Hemisphere, fm_rlamygdala)
model_data <- merge(long_data_amygdala_selected, long_data_MMPFC, by = c("ID", "Hemisphere"))
model_data$Hemisphere <- as.factor(model_data$Hemisphere)

# Models 

model_LI_fm <- lmer(lateralisation_index_0.1 ~ fm_rlMMPFC*Hemisphere*Age + fm_rlamygdala*Hemisphere*Age + MeanFD + (1| ID), data = model_data)
summary(model_LI_fm)

```

Since models at two thresholds show convergence issues, a similar approach than the one used in the previous section was taken for these analyses.

### Alternative linear mixed-effects models for threshold p<0.05 (non-preregistered)

```{r}

# Data wrangling

long_data <- child_LI

long_data_amygdala <- long_data %>%
  select(
    ID,
    lateralisation_index_0.05,
    fm_ramygdala,
    fm_lamygdala,
    Age,
    MeanFD
  )
long_data_MMPFC <- long_data %>%
  select(
    ID,
    lateralisation_index_0.05,
    fm_rMMPFC,
    fm_lMMPFC,
    Age,
    MeanFD
  )

long_data_STS <- long_data %>%
  select(
    ID,
    lateralisation_index_0.05,
    fm_rSTS,
    fm_lSTS,
    Age,
    MeanFD
  )

## Reshape the data and adjust columns

long_data_amygdala <- long_data_amygdala %>%
  ## Pivot the data into a long format with "Right" and "Left" hemispheres
  pivot_longer(
    cols = c(fm_ramygdala, fm_lamygdala),
    names_to = "region",
    values_to = "fm_rlamygdala"
  ) %>%
  ## Create Hemisphere column based on the region name
  mutate(
    Hemisphere = case_when(
      region == "fm_ramygdala" ~ "Right",
      region == "fm_lamygdala" ~ "Left",
      TRUE ~ NA_character_
    )
  ) %>%
  select(ID, lateralisation_index_0.05, fm_rlamygdala, Age, MeanFD, Hemisphere)

long_data_MMPFC <- long_data_MMPFC %>%
  pivot_longer(
    cols = c(fm_rMMPFC, fm_lMMPFC),
    names_to = "region",
    values_to = "fm_rlMMPFC"
  ) %>%
  mutate(
    Hemisphere = case_when(
      region == "fm_rMMPFC" ~ "Right",
      region == "fm_lMMPFC" ~ "Left",
      TRUE ~ NA_character_
    )
  ) %>%
  select(ID, lateralisation_index_0.05, fm_rlMMPFC, Age, MeanFD, Hemisphere)

long_data_STS <- long_data_STS %>%
  pivot_longer(
    cols = c(fm_rSTS, fm_lSTS),
    names_to = "region",
    values_to = "fm_rlSTS"
  ) %>%
  mutate(
    Hemisphere = case_when(
      region == "fm_rSTS" ~ "Right",
      region == "fm_lSTS" ~ "Left",
      TRUE ~ NA_character_
    )
  ) %>%
  select(ID, lateralisation_index_0.05, fm_rlSTS, Age, MeanFD, Hemisphere)

# Models

## MMPFC

model_LI_0.05_MMPFC_fm <-lmer(fm_rlMMPFC ~ lateralisation_index_0.05*Hemisphere*Age + MeanFD + (1|ID), data = long_data_MMPFC)
summary(model_LI_0.05_MMPFC_fm)

### No interaction effects are significant, so models are run without interaction effects

model_LI_0.05_MMPFC_fm <- lmer(fm_rlMMPFC ~ lateralisation_index_0.05 + Hemisphere + Age + MeanFD + (1| ID), data = long_data_MMPFC)
summary_LI_0.05_MMPFC_fm <- tidy(model_LI_0.05_MMPFC_fm)
summary_LI_0.05_MMPFC_fm

## Amygdala

model_LI_0.05_amygdala_fm <-lmer(fm_rlamygdala ~ lateralisation_index_0.05*Hemisphere*Age + MeanFD + (1|ID), data = long_data_amygdala)
summary(model_LI_0.05_amygdala_fm)

### No interaction effects are significant, so models are run without interaction effects

model_LI_0.05_amygdala_fm <- lmer(fm_rlamygdala ~ lateralisation_index_0.05 + Hemisphere + Age + MeanFD + (1| ID), data = long_data_amygdala)
summary_LI_0.05_amygdala_fm <- tidy(model_LI_0.05_amygdala_fm)
summary_LI_0.05_amygdala_fm

## STS

model_LI_0.05_STS_fm <-lmer(fm_rlSTS ~ lateralisation_index_0.05*Hemisphere*Age + MeanFD + (1|ID), data = long_data_STS)
summary(model_LI_0.05_STS_fm)

### No interaction effects are significant, so models are run without interaction effects

model_LI_0.05_STS_fm <- lmer(fm_rlSTS ~ lateralisation_index_0.05 + Hemisphere + Age + MeanFD + (1| ID), data = long_data_STS)
summary_LI_0.05_STS_fm <- tidy(model_LI_0.05_STS_fm)
summary_LI_0.05_STS_fm

```

Save models

```{r}

all_summaries <- bind_rows(
  summary_LI_0.05_MMPFC_fm %>% mutate(model = "LI_0.05_fm_MMPFC"),
  summary_LI_0.05_amygdala_fm %>% mutate(model = "LI_0.05_fm_amygdala"),
  summary_LI_0.05_STS_fm %>% mutate(model = "LI_0.05_fm_STS"),
) %>%
  mutate(
    estimate = round(estimate, 2),
    std.error = round(std.error, 2),
    statistic = round(statistic, 2),
    df = round(df, 0),
    p.value = if_else(
      p.value < 0.01,
      format(p.value, scientific = TRUE, digits = 4),
      sprintf("%.3f", p.value)
    )
  )

write.csv(all_summaries, here("results/RQ3", "LI_0.05_fm.csv"), row.names = FALSE)

```

### Alternative linear mixed-effects models for threshold p<0.10 (non-preregistered)

```{r}

# Data wrangling

long_data <- child_LI

long_data_amygdala <- long_data %>%
  select(
    ID,
    lateralisation_index_0.1,
    fm_ramygdala,
    fm_lamygdala,
    Age,
    MeanFD
  )
long_data_MMPFC <- long_data %>%
  select(
    ID,
    lateralisation_index_0.1,
    fm_rMMPFC,
    fm_lMMPFC,
    Age,
    MeanFD
  )

long_data_STS <- long_data %>%
  select(
    ID,
    lateralisation_index_0.1,
    fm_rSTS,
    fm_lSTS,
    Age,
    MeanFD
  )

## Reshape the data and adjust columns

long_data_amygdala <- long_data_amygdala %>%
  ## Pivot the data into a long format with "Right" and "Left" hemispheres
  pivot_longer(
    cols = c(fm_ramygdala, fm_lamygdala),
    names_to = "region",
    values_to = "fm_rlamygdala"
  ) %>%
  ## Create Hemisphere column based on the region name
  mutate(
    Hemisphere = case_when(
      region == "fm_ramygdala" ~ "Right",
      region == "fm_lamygdala" ~ "Left",
      TRUE ~ NA_character_
    )
  ) %>%
  select(ID, lateralisation_index_0.1, fm_rlamygdala, Age, MeanFD, Hemisphere)

long_data_MMPFC <- long_data_MMPFC %>%
  pivot_longer(
    cols = c(fm_rMMPFC, fm_lMMPFC),
    names_to = "region",
    values_to = "fm_rlMMPFC"
  ) %>%
  mutate(
    Hemisphere = case_when(
      region == "fm_rMMPFC" ~ "Right",
      region == "fm_lMMPFC" ~ "Left",
      TRUE ~ NA_character_
    )
  ) %>%
  select(ID, lateralisation_index_0.1, fm_rlMMPFC, Age, MeanFD, Hemisphere)

long_data_STS <- long_data_STS %>%
  pivot_longer(
    cols = c(fm_rSTS, fm_lSTS),
    names_to = "region",
    values_to = "fm_rlSTS"
  ) %>%
  mutate(
    Hemisphere = case_when(
      region == "fm_rSTS" ~ "Right",
      region == "fm_lSTS" ~ "Left",
      TRUE ~ NA_character_
    )
  ) %>%
  select(ID, lateralisation_index_0.1, fm_rlSTS, Age, MeanFD, Hemisphere)

# Models

## MMPFC

model_LI_0.1_MMPFC_fm <-lmer(fm_rlMMPFC ~ lateralisation_index_0.1*Hemisphere*Age + MeanFD + (1|ID), data = long_data_MMPFC)
summary(model_LI_0.1_MMPFC_fm)

### No interaction effects are significant, so models are run without interaction effects

model_LI_0.1_MMPFC_fm <- lmer(fm_rlMMPFC ~ lateralisation_index_0.1 + Hemisphere + Age + MeanFD + (1| ID), data = long_data_MMPFC)
summary_LI_0.1_MMPFC_fm <- tidy(model_LI_0.1_MMPFC_fm)
summary_LI_0.1_MMPFC_fm

## Amygdala

model_LI_0.1_amygdala_fm <-lmer(fm_rlamygdala ~ lateralisation_index_0.1*Hemisphere*Age + MeanFD + (1|ID), data = long_data_amygdala)
summary(model_LI_0.1_amygdala_fm)

### No interaction effects are significant, so models are run without interaction effects

model_LI_0.1_amygdala_fm <- lmer(fm_rlamygdala ~ lateralisation_index_0.1 + Hemisphere + Age + MeanFD + (1| ID), data = long_data_amygdala)
summary_LI_0.1_amygdala_fm <- tidy(model_LI_0.1_amygdala_fm)
summary_LI_0.1_amygdala_fm

## STS

model_LI_0.1_STS_fm <-lmer(fm_rlSTS ~ lateralisation_index_0.1*Hemisphere*Age + MeanFD + (1|ID), data = long_data_STS)
summary(model_LI_0.1_STS_fm)

### No interaction effects are significant, so models are run without interaction effects

model_LI_0.1_STS_fm <- lmer(fm_rlSTS ~ lateralisation_index_0.1 + Hemisphere + Age + MeanFD + (1| ID), data = long_data_STS)
summary_LI_0.1_STS_fm <- tidy(model_LI_0.1_STS_fm)
summary_LI_0.1_STS_fm

```

Save models

```{r}

all_summaries <- bind_rows(
  summary_LI_0.1_MMPFC_fm %>% mutate(model = "LI_0.1_fm_MMPFC"),
  summary_LI_0.1_amygdala_fm %>% mutate(model = "LI_0.1_fm_amygdala"),
  summary_LI_0.1_STS_fm %>% mutate(model = "LI_0.1_fm_STS"),
) %>%
  mutate(
    estimate = round(estimate, 2),
    std.error = round(std.error, 2),
    statistic = round(statistic, 2),
    df = round(df, 0),
    p.value = if_else(
      p.value < 0.1,
      format(p.value, scientific = TRUE, digits = 4),
      sprintf("%.3f", p.value)
    )
  )

write.csv(all_summaries, here("results/RQ3", "LI_0.1_fm.csv"), row.names = FALSE)

```

### Plots

```{r}

# Data wrangling

data_plot <- read_csv(here("processed_data", "child_MRIvariables.csv"), col_names=TRUE)
data_plot <- data_plot[,c(1:3, 6:9, 230:231)]
data_plot <- data_plot %>%
  rename_with(~ sub("^zscored_", "", .x), starts_with("zscored_"))
data_plot <- data_plot %>%
  select(fm_rMMPFC, fm_lMMPFC, fm_ramygdala, fm_lamygdala, fm_rSTS, fm_lSTS, lateralisation_index_0.05, lateralisation_index_0.1) %>%
  pivot_longer(
    cols = c("fm_rMMPFC", "fm_lMMPFC", "fm_ramygdala", "fm_lamygdala", "fm_rSTS", "fm_lSTS"),
    names_to = c("Hemisphere", "Region"),
    names_pattern = "fm_([rl])(.+)",   # r/l hemisphere + region name
    values_to = "zscored_value"
  ) %>%
  mutate(
    Hemisphere = case_when(
      Hemisphere == "r" ~ "right",
      Hemisphere == "l" ~ "left"),
    Region = case_when(
      Region == "MMPFC" ~ "MMPFC",
      Region == "amygdala" ~ "amygdala",
      Region == "STS" ~ "STS",
      TRUE ~ Region
    )
  )
data_plot_MMPFC <- data_plot %>%
  filter(Region == "MMPFC")
data_plot_amygdala <- data_plot %>%
  filter(Region == "amygdala")
data_plot_STS <- data_plot %>%
  filter(Region == "STS")

# Threshold p<0.05

plot_MMPFC <- create_plot(data_plot_MMPFC, zscored_value, lateralisation_index_0.05, custom_colours_MMPFC, "", "Lateralisation Index (p<0.05)", legend_title = "MMPFC Hemisphere")
plot_amygdala <- create_plot(data_plot_amygdala, zscored_value, lateralisation_index_0.05, custom_colours_amygdala, "Functional maturity of region", "Lateralisation Index (p<0.05)", legend_title = "Amygdala Hemisphere", legend_position = "bottom", remove_y_axis_labels = TRUE)
plot_STS <- create_plot(data_plot_STS, zscored_value, lateralisation_index_0.05, custom_colours_STS, "", "", legend_title = "STS Hemisphere", legend_position = "bottom", remove_y_axis_labels = TRUE)

## Combine plots into a single row

LI_fm <- (plot_MMPFC | plot_amygdala | plot_STS) +  
  plot_layout(ncol = 3, guides = "collect") +
  plot_annotation(
    title = ""
  ) &
  theme(
    legend.position = "bottom",
    legend.text = element_text(size = 12),
    legend.title = element_text(size = 12),
    plot.title = element_text(size = 14, hjust = 0.5, face = "bold")
  )
## Save plots

ggsave(here("results/figures", "LI_0.05_fm.png"), plot = LI_fm, width = 10, height = 5, units = "in", dpi = 300)

# Threshold p<0.10

plot_MMPFC <- create_plot(data_plot_MMPFC, zscored_value, lateralisation_index_0.1, custom_colours_MMPFC, "", "Lateralisation Index (p<0.10)", legend_title = "MMPFC Hemisphere")
plot_amygdala <- create_plot(data_plot_amygdala, zscored_value, lateralisation_index_0.1, custom_colours_amygdala, "Functional maturity of region", "Lateralisation Index (p<0.1)", legend_title = "Amygdala Hemisphere", legend_position = "bottom", remove_y_axis_labels = TRUE)
plot_STS <- create_plot(data_plot_STS, zscored_value, lateralisation_index_0.1, custom_colours_STS, "", "", legend_title = "STS Hemisphere", legend_position = "bottom", remove_y_axis_labels = TRUE)

## Combine plots into a single row

LI_fm <- (plot_MMPFC | plot_amygdala | plot_STS) +  
  plot_layout(ncol = 3, guides = "collect") +
  plot_annotation(
    title = ""
  ) &
  theme(
    legend.position = "bottom",
    legend.text = element_text(size = 12),
    legend.title = element_text(size = 12),
    plot.title = element_text(size = 14, hjust = 0.5, face = "bold")
  )

## Save plots

ggsave(here("results/figures", "LI_0.1_fm.png"), plot = LI_fm, width = 10, height = 5, units = "in", dpi = 300)

```


## Section III: Relationship between lateralisation of FFA response and functional maturity of FFA (non-preregistered)

#### Threshold p<0.05

```{r}

# Data wrangling

long_data <- child_LI

long_data_FFA <- long_data %>%
  select(
    ID,
    lateralisation_index_0.05,
    fm_rFFA,
    fm_lFFA,
    Age,
    MeanFD
  )

## Reshape the data and adjust columns

long_data_FFA <- long_data_FFA %>%
  pivot_longer(
    cols = c(fm_rFFA, fm_lFFA),
    names_to = "region",
    values_to = "fm_rlFFA"
  ) %>%
  mutate(
    Hemisphere = case_when(
      region == "fm_rFFA" ~ "Right",
      region == "fm_lFFA" ~ "Left",
      TRUE ~ NA_character_
    )
  ) %>%
  select(ID, lateralisation_index_0.05, fm_rlFFA, Age, MeanFD, Hemisphere)


# Models

## FFA

model_LI_0.05_FFA_fm <-lmer(fm_rlFFA ~ lateralisation_index_0.05*Hemisphere*Age + MeanFD + (1|ID), data = long_data_FFA)
summary(model_LI_0.05_FFA_fm)

### No interaction effects are significant, so models are run without interaction effects

model_LI_0.05_FFA_fm <- lmer(fm_rlFFA ~ lateralisation_index_0.05 + Hemisphere + Age + MeanFD + (1| ID), data = long_data_FFA)
summary_LI_0.05_FFA_fm <- tidy(model_LI_0.05_FFA_fm)
summary_LI_0.05_FFA_fm

```

### Threshold p<0.10

```{r}

# Data wrangling

long_data <- child_LI

long_data_FFA <- long_data %>%
  select(
    ID,
    lateralisation_index_0.1,
    fm_rFFA,
    fm_lFFA,
    Age,
    MeanFD
  )

## Reshape the data and adjust columns

long_data_FFA <- long_data_FFA %>%
  pivot_longer(
    cols = c(fm_rFFA, fm_lFFA),
    names_to = "region",
    values_to = "fm_rlFFA"
  ) %>%
  mutate(
    Hemisphere = case_when(
      region == "fm_rFFA" ~ "Right",
      region == "fm_lFFA" ~ "Left",
      TRUE ~ NA_character_
    )
  ) %>%
  select(ID, lateralisation_index_0.1, fm_rlFFA, Age, MeanFD, Hemisphere)


# Models

## FFA

model_LI_0.1_FFA_fm <-lmer(fm_rlFFA ~ lateralisation_index_0.1*Hemisphere*Age + MeanFD + (1|ID), data = long_data_FFA)
summary(model_LI_0.1_FFA_fm)

### No interaction effects are significant, so models are run without interaction effects

model_LI_0.1_FFA_fm <- lmer(fm_rlFFA ~ lateralisation_index_0.1 + Hemisphere + Age + MeanFD + (1| ID), data = long_data_FFA)
summary_LI_0.1_FFA_fm <- tidy(model_LI_0.1_FFA_fm)
summary_LI_0.1_FFA_fm

```

Save models

```{r}

all_summaries <- bind_rows(
  summary_LI_0.1_FFA_fm %>% mutate(model = "LI_0.1_fm_FFA"),
  summary_LI_0.05_FFA_fm %>% mutate(model = "LI_0.05_fm_FFA")) %>%
  mutate(
    estimate = round(estimate, 2),
    std.error = round(std.error, 2),
    statistic = round(statistic, 2),
    df = round(df, 0),
    p.value = if_else(
      p.value < 0.1,
      format(p.value, scientific = TRUE, digits = 4),
      sprintf("%.3f", p.value)
    )
  )

write.csv(all_summaries, here("results/RQ3", "LI_fm_FFA.csv"), row.names = FALSE)

```


```{r}

markdownToHTML("FRIC_LateralisationIndex.Rmd",output ="FRIC_LateralisationIndex.html")

```

