---
title: "FRIC_MRIvariables"
author: "LJS"
date: "2025-01-08"
output: html_document
---


# Libraries 

```{r setup, include=FALSE}

library("rlang") #toolbox
library("readr") #toolbox
library("dplyr") #data manipulation
library("here") #toolbox
library("tidyverse") #data manipulation
library("ggpubr") #plotting
library("tidytext") #data manipulation
library("knitr") #rmarkdown
library("htmltools") #rmarkdown
library("markdown") #rmarkdown
library("httpuv") #rmarkdown
library("NCmisc") #toolbox
library("stringr") #data manipulation
library("tidyr") #data manipulation
library("purrr") #data manipulation

```


# Face Responses in Childhood (FRIC) project

This script creates MRI variables i.e., functional  maturity  measures, magnitude of responses to face and scene events, inter-region  correlations  (also  referred  to  as  functional  connectivity) and lateralisation index of FFA at two statistical thresholds.

Structure:
- Section I: Functional maturity (fm)
- Section II: Magnitude of responses to face and scene events
- Section III: Inter-region correlations (functional connectivity, fx)
- Section IV: Lateralisation index (LI)
- Section V: Combine all children dependent variables into one spreadsheet and save files


## Section I: Functional maturity (fm)

### Read data

```{r}

# Covariates

participants <- read_tsv(here("raw_data/covariates", "participants.tsv"), col_names = TRUE)
colnames(participants)[which(names(participants) == "participant_id")] <- "ID"

## Remove the word "pixar" and trim extra whitespace

participants$ID <- gsub("[sub-pixar-]", "", participants$ID)
participants$ID <- trimws(participants$ID)

## Create child or adult lists

adult_list <- row.names(participants)[which(participants[["Child_Adult"]] == "adult")]
child_list <- row.names(participants)[which(participants[["Child_Adult"]] == "child")]
child_list <- sprintf("%03d", as.integer(child_list))

# Timecourses

## Anatomical ROIs: amygdalae

tcs_amygdala <- read.csv(here("raw_data/timecourses", "tcs_amygdala.csv"), header = TRUE, dec = ".", sep = ",")

### Remove the word "pixar" and trim extra whitespace

tcs_amygdala$sub <- gsub("[pixar]", "", tcs_amygdala$sub)
tcs_amygdala$sub <- trimws(tcs_amygdala$sub)

### Tidy up final columns

tcs_amygdala$run <- NULL
colnames(tcs_amygdala) <- c("time", "ID", "lamygdala", "ramygdala")

## Functional ROIs: FFA, STS, MMPFC

tcs_fROIs <- read.csv(here("raw_data/timecourses", "tcs_fROIs.csv"), header = TRUE, dec = ".", sep = ",")

### Remove the word "pixar" and trim extra whitespace

tcs_fROIs$sub <- gsub("[pixar]", "", tcs_fROIs$sub)
tcs_fROIs$sub <- trimws(tcs_fROIs$sub)

### Creating a single column for left/right ROI tcs
#### Define mapping of new columns to their source columns

roi_map <- list(
  left_FFA  = c("fROI.lFFA.lffa.lloc.splithalf.01", "fROI.lFFA.lffa.lloc.splithalf.02"),
  right_FFA = c("fROI.rFFA.rffa.rloc.splithalf.01", "fROI.rFFA.rffa.rloc.splithalf.02"),
  left_STS  = c("fROI.lSTS.lsts.lloc.splithalf.01", "fROI.lSTS.lsts.lloc.splithalf.02"),
  right_LOC = c("fROI.rSTS.rsts.rloc.splithalf.01", "fROI.rSTS.rsts.rloc.splithalf.02"),
  left_MMPFC  = c("fROI.lMMPFC.lmmpfc.ls2.splithalf.01", "fROI.lMMPFC.lmmpfc.ls2.splithalf.02"),
  right_MMPFC = c("fROI.rMMPFC.rmmpfc.rs2.splithalf.01", "fROI.rMMPFC.rmmpfc.rs2.splithalf.02")
)

#### Loop over map and add columns

tcs_fROIs <- tcs_fROIs %>%
  mutate(across(.cols = everything(), .fns = identity)) %>% # keep structure
  { 
    out <- .
    for (newcol in names(roi_map)) {
      out[[newcol]] <- rowSums(out[roi_map[[newcol]]], na.rm = TRUE)
      out[[newcol]][out[[newcol]] == 0] <- NA
    }
    out
  }

### Change timepoint numeration

tcs_fROIs <- tcs_fROIs %>%
  mutate(time = case_when(
    half == "splithalf-01" ~ time + 0,
    half == "splithalf-02" ~ time + 86,
    TRUE ~ time
  ))

### Tidy up final columns

tcs_fROIs <- subset(tcs_fROIs, select = -c(3:16))
colnames(tcs_fROIs) <- c("time", "ID", "lFFA", "rFFA", "lSTS", "rSTS", "lMMPFC", "rMMPFC")

```

### Generate/READ average adult timecourses (tcs)

```{r}

# Generating average adult tcs for amygdalae

adult_tcs_amygdala <- tcs_amygdala %>%
  filter(ID %in% adult_list)
avg_adult_tcs_amygdala <- adult_tcs_amygdala %>%
  group_by(time) %>%
  summarise(
    avg_lamygdala = mean(lamygdala, na.rm = TRUE),
    avg_ramygdala = mean(ramygdala, na.rm = TRUE)
  )

# Traditional fROIs from adult samples

avg_adult_tcs_trad_fROIs <- read.csv(here("raw_data/timecourses", "tcs_trad_adult_fROIs.csv"), header = TRUE, dec = ".", sep = ",")

## Change timepoint numeration according to first TR=0

avg_adult_tcs_trad_fROIs <- avg_adult_tcs_trad_fROIs %>%
  mutate(time = time - 1)

```

### Generate fm per individual

Amygdala 

```{r}

# Calculate general fm

## Data wrangling

child_tcs_amygdala <- tcs_amygdala %>%
  filter(ID %in% child_list)
fm_data_tcs_amygdala <- merge(child_tcs_amygdala, avg_adult_tcs_amygdala, by = "time")
child_fm_amygdala <- numeric(nrow(fm_data_tcs_amygdala))

## Calculate Pearson correlations for left and right amygdala

child_fm_amygdala <- fm_data_tcs_amygdala %>%
  group_by(ID) %>%
  summarise(
    lamygdala = cor(lamygdala, avg_lamygdala, method = "pearson", use = "complete.obs"),
    ramygdala = cor(ramygdala, avg_ramygdala, method = "pearson", use = "complete.obs")
  )

# Columns to z-score

roi_cols <- c("lamygdala", "ramygdala")

# Create a list to store zscore vectors

z_list <- list()

# Loop to compute z-scores

for (col in roi_cols) {
  mean_val <- mean(child_fm_amygdala[[col]], na.rm = TRUE)
  sd_val   <- sd(child_fm_amygdala[[col]], na.rm = TRUE)
  z_list[[col]] <- (child_fm_amygdala[[col]] - mean_val) / sd_val
}

# Add z-scores to dataframe with the names you requested

child_fm_amygdala <- child_fm_amygdala %>%
  ungroup() %>%
  mutate(
    zscored_lamygdala   = z_list$lamygdala,
    zscored_ramygdala   = z_list$ramygdala
  )

```

fROIs

```{r}

# Calculate general fm

## Data wrangling

child_tcs_fROIs <- tcs_fROIs %>%
  filter(ID %in% child_list)
fm_data_tcs_fROIs <- merge(child_tcs_fROIs, avg_adult_tcs_trad_fROIs, by = "time")
child_fm_fROIs <- NULL

## Calculate Pearson correlations for left and right fROIs

child_fm_fROIs <- fm_data_tcs_fROIs %>%
  group_by(ID) %>%
  nest() %>%
  mutate(
    lFFA = map_dbl(data, ~ {
      tc <- .x
      seg1 <- tc %>% filter(time >= 0 & time <= 81)
      seg2 <- tc %>% filter(time >= 86 & time <= 167)
      corr1 <- cor(seg1$lFFA, seg1$avg_lFFA, method = "pearson", use = "complete.obs")
      corr2 <- cor(seg2$lFFA, seg2$avg_lFFA, method = "pearson", use = "complete.obs")
      mean(c(corr1, corr2), na.rm = TRUE)
    }),
    rFFA = map_dbl(data, ~ {
      tc <- .x
      seg1 <- tc %>% filter(time >= 0 & time <= 81)
      seg2 <- tc %>% filter(time >= 86 & time <= 167)
      corr1 <- cor(seg1$rFFA, seg1$avg_rFFA, method = "pearson", use = "complete.obs")
      corr2 <- cor(seg2$rFFA, seg2$avg_rFFA, method = "pearson", use = "complete.obs")
      mean(c(corr1, corr2), na.rm = TRUE)
    }),
    lSTS = map_dbl(data, ~ {
      tc <- .x
      seg1 <- tc %>% filter(time >= 0 & time <= 81)
      seg2 <- tc %>% filter(time >= 86 & time <= 167)
      corr1 <- cor(seg1$lSTS, seg1$avg_lSTS, method = "pearson", use = "complete.obs")
      corr2 <- cor(seg2$lSTS, seg2$avg_lSTS, method = "pearson", use = "complete.obs")
      mean(c(corr1, corr2), na.rm = TRUE)
    }),
    rSTS = map_dbl(data, ~ {
      tc <- .x
      seg1 <- tc %>% filter(time >= 0 & time <= 81)
      seg2 <- tc %>% filter(time >= 86 & time <= 167)
      corr1 <- cor(seg1$rSTS, seg1$avg_rSTS, method = "pearson", use = "complete.obs")
      corr2 <- cor(seg2$rSTS, seg2$avg_rSTS, method = "pearson", use = "complete.obs")
      mean(c(corr1, corr2), na.rm = TRUE)
    }),
    lMMPFC = map_dbl(data, ~ {
      tc <- .x
      seg1 <- tc %>% filter(time >= 0 & time <= 81)
      seg2 <- tc %>% filter(time >= 86 & time <= 167)
      corr1 <- cor(seg1$lMMPFC, seg1$avg_lMMPFC, method = "pearson", use = "complete.obs")
      corr2 <- cor(seg2$lMMPFC, seg2$avg_lMMPFC, method = "pearson", use = "complete.obs")
      mean(c(corr1, corr2), na.rm = TRUE)
    }),
    rMMPFC = map_dbl(data, ~ {
      tc <- .x
      seg1 <- tc %>% filter(time >= 0 & time <= 81)
      seg2 <- tc %>% filter(time >= 86 & time <= 167)
      corr1 <- cor(seg1$rMMPFC, seg1$avg_rMMPFC, method = "pearson", use = "complete.obs")
      corr2 <- cor(seg2$rMMPFC, seg2$avg_rMMPFC, method = "pearson", use = "complete.obs")
      mean(c(corr1, corr2), na.rm = TRUE)
    })
  ) %>%
  select(ID, lFFA, rFFA, lSTS, rSTS, lMMPFC, rMMPFC)


# Columns to z-score

roi_cols <- c("lFFA", "rFFA", "lSTS", "rSTS", "lMMPFC", "rMMPFC")

# Create a list to store zscore vectors

z_list <- list()

# Loop to compute z-scores

for (col in roi_cols) {
  mean_val <- mean(child_fm_fROIs[[col]], na.rm = TRUE)
  sd_val   <- sd(child_fm_fROIs[[col]], na.rm = TRUE)
  z_list[[col]] <- (child_fm_fROIs[[col]] - mean_val) / sd_val
}

# Add z-scores to dataframe with the names requested

child_fm_fROIs <- child_fm_fROIs %>%
  ungroup() %>%
  mutate(
    zscored_lFFA   = z_list$lFFA,
    zscored_rFFA   = z_list$rFFA,
    zscored_lSTS   = z_list$lSTS,
    zscored_rSTS   = z_list$rSTS,
    zscored_lMMPFC = z_list$lMMPFC,
    zscored_rMMPFC = z_list$rMMPFC
  )

```

Group results

```{r}

child_fm <- merge(child_fm_amygdala, child_fm_fROIs, by = "ID")
child_fm <- child_fm %>% select(contains(c("ID", "zscored")))
colnames(child_fm) <- c("ID", "zscored_fm_lamygdala", "zscored_fm_ramygdala", "zscored_fm_lFFA", "zscored_fm_rFFA", "zscored_fm_lSTS", "zscored_fm_rSTS", "zscored_fm_lMMPFC", "zscored_fm_rMMPFC")

```

Save timecourse data

```{r}

tcs_total <- merge(tcs_amygdala, tcs_fROIs, by = c("time", "ID"), all.x = TRUE)
write.csv(tcs_total, here("processed_data", "tcs_total.csv"), row.names = FALSE)

```


## Section II: Magnitude of responses to face and scene events

### Read data

```{r}

events_TRs <- read_tsv(here("raw_data/events", "faces_scenes.tsv"), col_names=TRUE)
rownames(events_TRs) <- NULL
events_TRs$event <- c("F01", "F09", "F11", "F04", "F10", "F12", "F07", "F08", "F06", "F05", "F02", "F03",
                     "S07", "S02", "S03", "S04", "S12", "S11", "S10", "S06", "S08", "S05", "S09", "S01")

```

### Find timepoint per each face/scene event in the movie that elicited the peak average magnitude of responses in adults (i.e., 12 timepoints for face events, 12 timepoints for scene events)

Amygdala

```{r}

# Function to find the timepoint associated with the maximum response value for both left and right amygdala in an interval

get_max_timepoint <- function(start, end, avg_adult_tcs_amygdala) {
  ## Filter rows where timepoint is within the interval [start, end]
  interval_data <- avg_adult_tcs_amygdala[avg_adult_tcs_amygdala$time >= start & avg_adult_tcs_amygdala$time <= end, ]
  
  ## If there are values within the interval, find the timepoint with the max value for both left and right amygdala
    if (nrow(interval_data) > 0) {
    ## Find the timepoint associated with the max value for left amygdala
    max_lindex <- which.max(interval_data$avg_lamygdala)
    max_ltimepoint <- interval_data$time[max_lindex]
            
    ## Find the timepoint associated with the max value for right amygdala
    max_rindex <- which.max(interval_data$avg_ramygdala)
    max_rtimepoint <- interval_data$time[max_rindex]
            
    ## Return both timepoints for left and right amygdala
        return(c(max_ltimepoint, max_rtimepoint))
  } else {
  return(c(NA, NA))  #return NA if no timepoints are within the interval
  }
}

# Apply the function to each row of the interval_df

max_timepoints <- t(mapply(get_max_timepoint, events_TRs$onset, events_TRs$end, MoreArgs = list(avg_adult_tcs_amygdala = avg_adult_tcs_amygdala)))

# Add the results to the interval dataframe

events_TRs$max_lamygdala_timepoint <- max_timepoints[, 1]
events_TRs$max_ramygdala_timepoint <- max_timepoints[, 2]

```

FFA

```{r}

get_max_timepoint <- function(start, end, avg_adult_tcs_trad_fROIs) {
  ## Filter rows where timepoint is within the interval [start, end]
  interval_data <- avg_adult_tcs_trad_fROIs[avg_adult_tcs_trad_fROIs$time >= start & avg_adult_tcs_trad_fROIs$time <= end, ]
  
  ## If there are values within the interval, find the timepoint with the max value for both left and right FFA
    if (nrow(interval_data) > 0) {
    ## Find the timepoint associated with the max value for left FFA
    max_lindex <- which.max(interval_data$avg_lFFA)
    max_ltimepoint <- interval_data$time[max_lindex]
            
    ## Find the timepoint associated with the max value for right FFA
    max_rindex <- which.max(interval_data$avg_rFFA)
    max_rtimepoint <- interval_data$time[max_rindex]
            
    ## Return both timepoints for left and right FFA
        return(c(max_ltimepoint, max_rtimepoint))
  } else {
  return(c(NA, NA))  #return NA if no timepoints are within the interval
  }
}

# Apply the function to each row of the interval_df

max_timepoints <- t(mapply(get_max_timepoint, events_TRs$onset, events_TRs$end, MoreArgs = list(avg_adult_tcs_trad_fROIs = avg_adult_tcs_trad_fROIs)))

# Add the results to the interval dataframe

events_TRs$max_lFFA_timepoint <- max_timepoints[, 1]
events_TRs$max_rFFA_timepoint <- max_timepoints[, 2]

```

STS

```{r}

get_max_timepoint <- function(start, end, avg_adult_tcs_trad_fROIs) {
  ## Filter rows where timepoint is within the interval [start, end]
  interval_data <- avg_adult_tcs_trad_fROIs[avg_adult_tcs_trad_fROIs$time >= start & avg_adult_tcs_trad_fROIs$time <= end, ]
  
  ## If there are values within the interval, find the timepoint with the max value for both left and right STS
    if (nrow(interval_data) > 0) {
    ## Find the timepoint associated with the max value for left STS
    max_lindex <- which.max(interval_data$avg_lSTS)
    max_ltimepoint <- interval_data$time[max_lindex]
            
    ## Find the timepoint associated with the max value for right STS
    max_rindex <- which.max(interval_data$avg_rSTS)
    max_rtimepoint <- interval_data$time[max_rindex]
            
    ## Return both timepoints for left and right STS
        return(c(max_ltimepoint, max_rtimepoint))
  } else {
  return(c(NA, NA))  #return NA if no timepoints are within the interval
  }
}

# Apply the function to each row of the interval_df

max_timepoints <- t(mapply(get_max_timepoint, events_TRs$onset, events_TRs$end, MoreArgs = list(avg_adult_tcs_trad_fROIs = avg_adult_tcs_trad_fROIs)))

# Add the results to the interval dataframe

events_TRs$max_lSTS_timepoint <- max_timepoints[, 1]
events_TRs$max_rSTS_timepoint <- max_timepoints[, 2]

```

MMPFC

```{r}

get_max_timepoint <- function(start, end, avg_adult_tcs_trad_fROIs) {
  ## Filter rows where timepoint is within the interval [start, end]
  interval_data <- avg_adult_tcs_trad_fROIs[avg_adult_tcs_trad_fROIs$time >= start & avg_adult_tcs_trad_fROIs$time <= end, ]
  
  ## If there are values within the interval, find the timepoint with the max value for both left and right MMPFC
    if (nrow(interval_data) > 0) {
    ## Find the timepoint associated with the max value for left MMPFC
    max_lindex <- which.max(interval_data$avg_lMMPFC)
    max_ltimepoint <- interval_data$time[max_lindex]
            
    ## Find the timepoint associated with the max value for right MMPFC
    max_rindex <- which.max(interval_data$avg_rMMPFC)
    max_rtimepoint <- interval_data$time[max_rindex]
            
    ## Return both timepoints for left and right MMPFC
        return(c(max_ltimepoint, max_rtimepoint))
  } else {
  return(c(NA, NA))  #return NA if no timepoints are within the interval
  }
}

# Apply the function to each row of the interval_df

max_timepoints <- t(mapply(get_max_timepoint, events_TRs$onset, events_TRs$end, MoreArgs = list(avg_adult_tcs_trad_fROIs = avg_adult_tcs_trad_fROIs)))

# Add the results to the interval dataframe

events_TRs$max_lMMPFC_timepoint <- max_timepoints[, 1]
events_TRs$max_rMMPFC_timepoint <- max_timepoints[, 2]

```

### Find children's response magnitude to previous timepoints

Amygdala

```{r}

# Filter magnitudes for relevant timepoints for left amygdala 

lamygdala_timepoints_list <- events_TRs[, c("event", "max_lamygdala_timepoint")]
child_tcs_lamygdala <- child_tcs_amygdala[, c("time", "ID", "lamygdala")]
child_eventsmagnitude_lamygdala <- lamygdala_timepoints_list %>%
  inner_join(child_tcs_lamygdala, by = c("max_lamygdala_timepoint" = "time"), relationship = "many-to-many")
child_eventsmagnitude_lamygdala <- child_eventsmagnitude_lamygdala %>%
  select(ID, event, max_lamygdala_timepoint, lamygdala)

# Shift rows/columns

child_eventsmagnitude_lamygdala <- child_eventsmagnitude_lamygdala %>%
  mutate(event = paste0("lamygdala_", event)) %>%
  group_by(ID, event) %>%
  summarise(lamygdala = mean(lamygdala, na.rm = TRUE), .groups = "drop") %>%
  pivot_wider(
    names_from = event,
    values_from = lamygdala
  )
child_eventsmagnitude_lamygdala <- child_eventsmagnitude_lamygdala %>%
  mutate_all(~ replace(., is.nan(.), NA))

# Filter magnitudes for relevant timepoints for right amygdala 

ramygdala_timepoints_list <- events_TRs[, c("event", "max_ramygdala_timepoint")]
child_tcs_ramygdala <- child_tcs_amygdala[, c("time", "ID", "ramygdala")]
child_eventsmagnitude_ramygdala <- ramygdala_timepoints_list %>%
  inner_join(child_tcs_ramygdala, by = c("max_ramygdala_timepoint" = "time"), relationship = "many-to-many")
child_eventsmagnitude_ramygdala <- child_eventsmagnitude_ramygdala %>%
  select(ID, event, max_ramygdala_timepoint, ramygdala)

# Assign timepoint/event names

child_eventsmagnitude_ramygdala <- child_eventsmagnitude_ramygdala %>%
  mutate(event = paste0("ramygdala_", event)) %>%
  group_by(ID, event) %>%
  summarise(ramygdala = mean(ramygdala, na.rm = TRUE), .groups = "drop") %>%
  pivot_wider(
    names_from = event,
    values_from = ramygdala
  )
child_eventsmagnitude_ramygdala <- child_eventsmagnitude_ramygdala %>%
  mutate_all(~ replace(., is.nan(.), NA))

```

FFA

```{r}

# Filter magnitudes for relevant timepoints for left FFA 

lFFA_timepoints_list <- events_TRs[, c("event", "max_lFFA_timepoint")]
child_tcs_lFFA <- child_tcs_fROIs[, c("time", "ID", "lFFA")]
child_eventsmagnitude_lFFA <- lFFA_timepoints_list %>%
  inner_join(child_tcs_lFFA, by = c("max_lFFA_timepoint" = "time"), relationship = "many-to-many")
child_eventsmagnitude_lFFA <- child_eventsmagnitude_lFFA %>%
  select(ID, event, max_lFFA_timepoint, lFFA)

# Assign timepoint/event names

child_eventsmagnitude_lFFA <- child_eventsmagnitude_lFFA %>%
  mutate(event = paste0("lFFA_", event)) %>%
  group_by(ID, event) %>%
  summarise(lFFA = mean(lFFA, na.rm = TRUE), .groups = "drop") %>%
  pivot_wider(
    names_from = event,
    values_from = lFFA
  )
child_eventsmagnitude_lFFA <- child_eventsmagnitude_lFFA %>%
  mutate_all(~ replace(., is.nan(.), NA))

# Filter magnitudes for relevant timepoints for right FFA 

rFFA_timepoints_list <- events_TRs[, c("event", "max_rFFA_timepoint")]
child_tcs_rFFA <- child_tcs_fROIs[, c("time", "ID", "rFFA")]
child_eventsmagnitude_rFFA <- rFFA_timepoints_list %>%
  inner_join(child_tcs_rFFA, by = c("max_rFFA_timepoint" = "time"), relationship = "many-to-many")
child_eventsmagnitude_rFFA <- child_eventsmagnitude_rFFA %>%
  select(ID, event, max_rFFA_timepoint, rFFA)

# Assign timepoint/event names

child_eventsmagnitude_rFFA <- child_eventsmagnitude_rFFA %>%
  mutate(event = paste0("rFFA_", event)) %>%
  group_by(ID, event) %>%
  summarise(rFFA = mean(rFFA, na.rm = TRUE), .groups = "drop") %>%
  pivot_wider(
    names_from = event,
    values_from = rFFA
  )
child_eventsmagnitude_rFFA <- child_eventsmagnitude_rFFA %>%
  mutate_all(~ replace(., is.nan(.), NA))

```

STS

```{r}

# Filter magnitudes for relevant timepoints for left FFA 

lSTS_timepoints_list <- events_TRs[, c("event", "max_lSTS_timepoint")]
child_tcs_lSTS <- child_tcs_fROIs[, c("time", "ID", "lSTS")]
child_eventsmagnitude_lSTS <- lSTS_timepoints_list %>%
  inner_join(child_tcs_lSTS, by = c("max_lSTS_timepoint" = "time"), relationship = "many-to-many")
child_eventsmagnitude_lSTS <- child_eventsmagnitude_lSTS %>%
  select(ID, event, max_lSTS_timepoint, lSTS)

# Assign timepoint/event names

child_eventsmagnitude_lSTS <- child_eventsmagnitude_lSTS %>%
  mutate(event = paste0("lSTS_", event)) %>%
  group_by(ID, event) %>%
  summarise(lSTS = mean(lSTS, na.rm = TRUE), .groups = "drop") %>%
  pivot_wider(
    names_from = event,
    values_from = lSTS
  )
child_eventsmagnitude_lSTS <- child_eventsmagnitude_lSTS %>%
  mutate_all(~ replace(., is.nan(.), NA))

# Filter magnitudes for relevant timepoints for right STS 

rSTS_timepoints_list <- events_TRs[, c("event", "max_rSTS_timepoint")]
child_tcs_rSTS <- child_tcs_fROIs[, c("time", "ID", "rSTS")]
child_eventsmagnitude_rSTS <- rSTS_timepoints_list %>%
  inner_join(child_tcs_rSTS, by = c("max_rSTS_timepoint" = "time"), relationship = "many-to-many")
child_eventsmagnitude_rSTS <- child_eventsmagnitude_rSTS %>%
  select(ID, event, max_rSTS_timepoint, rSTS)

# Assign timepoint/event names

child_eventsmagnitude_rSTS <- child_eventsmagnitude_rSTS %>%
  mutate(event = paste0("rSTS_", event)) %>%
  group_by(ID, event) %>%
  summarise(rSTS = mean(rSTS, na.rm = TRUE), .groups = "drop") %>%
  pivot_wider(
    names_from = event,
    values_from = rSTS
  )
child_eventsmagnitude_rSTS <- child_eventsmagnitude_rSTS %>%
  mutate_all(~ replace(., is.nan(.), NA))

```

MMPFC

```{r}

# Filter magnitudes for relevant timepoints for left MMPFC 

lMMPFC_timepoints_list <- events_TRs[, c("event", "max_lMMPFC_timepoint")]
child_tcs_lMMPFC <- child_tcs_fROIs[, c("time", "ID", "lMMPFC")]
child_eventsmagnitude_lMMPFC <- lMMPFC_timepoints_list %>%
  inner_join(child_tcs_lMMPFC, by = c("max_lMMPFC_timepoint" = "time"), relationship = "many-to-many")
child_eventsmagnitude_lMMPFC <- child_eventsmagnitude_lMMPFC %>%
  select(ID, event, max_lMMPFC_timepoint, lMMPFC)

# Assign timepoint/event names

child_eventsmagnitude_lMMPFC <- child_eventsmagnitude_lMMPFC %>%
  mutate(event = paste0("lMMPFC_", event)) %>%
  group_by(ID, event) %>%
  summarise(lMMPFC = mean(lMMPFC, na.rm = TRUE), .groups = "drop") %>%
  pivot_wider(
    names_from = event,
    values_from = lMMPFC
  )
child_eventsmagnitude_lMMPFC <- child_eventsmagnitude_lMMPFC %>%
  mutate_all(~ replace(., is.nan(.), NA))

# Filter magnitudes for relevant timepoints for right MMPFC 

rMMPFC_timepoints_list <- events_TRs[, c("event", "max_rMMPFC_timepoint")]
child_tcs_rMMPFC <- child_tcs_fROIs[, c("time", "ID", "rMMPFC")]
child_eventsmagnitude_rMMPFC <- rMMPFC_timepoints_list %>%
  inner_join(child_tcs_rMMPFC, by = c("max_rMMPFC_timepoint" = "time"), relationship = "many-to-many")
child_eventsmagnitude_rMMPFC <- child_eventsmagnitude_rMMPFC %>%
  select(ID, event, max_rMMPFC_timepoint, rMMPFC)

# Assign timepoint/event names

child_eventsmagnitude_rMMPFC <- child_eventsmagnitude_rMMPFC %>%
  mutate(event = paste0("rMMPFC_", event)) %>%
  group_by(ID, event) %>%
  summarise(rMMPFC = mean(rMMPFC, na.rm = TRUE), .groups = "drop") %>%
  pivot_wider(
    names_from = event,
    values_from = rMMPFC
  )
child_eventsmagnitude_rMMPFC <- child_eventsmagnitude_rMMPFC %>%
  mutate_all(~ replace(., is.nan(.), NA))

```

Combine results

```{r}

data_frames <- list(
  child_eventsmagnitude_lamygdala,  child_eventsmagnitude_ramygdala,
  child_eventsmagnitude_lFFA,  child_eventsmagnitude_rFFA,
  child_eventsmagnitude_lSTS,  child_eventsmagnitude_rSTS,
  child_eventsmagnitude_lMMPFC,  child_eventsmagnitude_rMMPFC
)
child_eventsmagnitude <- Reduce(function(x, y) merge(x, y, by = "ID"), data_frames)

```

Save events data

```{r}

write.csv(events_TRs, here("processed_data", "events_TRs.csv"), row.names = FALSE)

```


## Section III: Inter-region correlations (functional connectivity, fx)

```{r}

# General fx 

## Calculate Pearson correlations for all ROIs

sample_fx <- tcs_total %>%
  group_by(ID) %>%
  nest() %>%
  mutate(
    fx_rFFA_lFFA = map_dbl(data, ~ {
      seg1 <- filter(.x, time >= 0 & time <= 81)
      seg2 <- filter(.x, time >= 86 & time <= 167)
      mean(c(cor(seg1$rFFA, seg1$lFFA, method = "pearson", use = "complete.obs"),
             cor(seg2$rFFA, seg2$lFFA, method = "pearson", use = "complete.obs")), na.rm = TRUE)
    }),
    fx_rFFA_lMMPFC = map_dbl(data, ~ {
      seg1 <- filter(.x, time >= 0 & time <= 81)
      seg2 <- filter(.x, time >= 86 & time <= 167)
      mean(c(cor(seg1$rFFA, seg1$lMMPFC, method = "pearson", use = "complete.obs"),
             cor(seg2$rFFA, seg2$lMMPFC, method = "pearson", use = "complete.obs")), na.rm = TRUE)
    }),
    fx_rFFA_rMMPFC = map_dbl(data, ~ {
      seg1 <- filter(.x, time >= 0 & time <= 81)
      seg2 <- filter(.x, time >= 86 & time <= 167)
      mean(c(cor(seg1$rFFA, seg1$rMMPFC, method = "pearson", use = "complete.obs"),
             cor(seg2$rFFA, seg2$rMMPFC, method = "pearson", use = "complete.obs")), na.rm = TRUE)
    }),
    fx_rFFA_lamygdala = map_dbl(data, ~ {
      seg1 <- filter(.x, time >= 0 & time <= 81)
      seg2 <- filter(.x, time >= 86 & time <= 167)
      mean(c(cor(seg1$rFFA, seg1$lamygdala, method = "pearson", use = "complete.obs"),
             cor(seg2$rFFA, seg2$lamygdala, method = "pearson", use = "complete.obs")), na.rm = TRUE)
    }),
    fx_rFFA_ramygdala = map_dbl(data, ~ {
      seg1 <- filter(.x, time >= 0 & time <= 81)
      seg2 <- filter(.x, time >= 86 & time <= 167)
      mean(c(cor(seg1$rFFA, seg1$ramygdala, method = "pearson", use = "complete.obs"),
             cor(seg2$rFFA, seg2$ramygdala, method = "pearson", use = "complete.obs")), na.rm = TRUE)
    }),
    fx_rFFA_lSTS = map_dbl(data, ~ {
      seg1 <- filter(.x, time >= 0 & time <= 81)
      seg2 <- filter(.x, time >= 86 & time <= 167)
      mean(c(cor(seg1$rFFA, seg1$lSTS, method = "pearson", use = "complete.obs"),
             cor(seg2$rFFA, seg2$lSTS, method = "pearson", use = "complete.obs")), na.rm = TRUE)
    }),
    fx_rFFA_rSTS = map_dbl(data, ~ {
      seg1 <- filter(.x, time >= 0 & time <= 81)
      seg2 <- filter(.x, time >= 86 & time <= 167)
      mean(c(cor(seg1$rFFA, seg1$rSTS, method = "pearson", use = "complete.obs"),
             cor(seg2$rFFA, seg2$rSTS, method = "pearson", use = "complete.obs")), na.rm = TRUE)
    }),
    fx_lFFA_lMMPFC = map_dbl(data, ~ {
      seg1 <- filter(.x, time >= 0 & time <= 81)
      seg2 <- filter(.x, time >= 86 & time <= 167)
      mean(c(cor(seg1$lFFA, seg1$lMMPFC, method = "pearson", use = "complete.obs"),
             cor(seg2$lFFA, seg2$lMMPFC, method = "pearson", use = "complete.obs")), na.rm = TRUE)
    }),
    fx_lFFA_rMMPFC = map_dbl(data, ~ {
      seg1 <- filter(.x, time >= 0 & time <= 81)
      seg2 <- filter(.x, time >= 86 & time <= 167)
      mean(c(cor(seg1$lFFA, seg1$rMMPFC, method = "pearson", use = "complete.obs"),
             cor(seg2$lFFA, seg2$rMMPFC, method = "pearson", use = "complete.obs")), na.rm = TRUE)
    }),
    fx_lFFA_lamygdala = map_dbl(data, ~ {
      seg1 <- filter(.x, time >= 0 & time <= 81)
      seg2 <- filter(.x, time >= 86 & time <= 167)
      mean(c(cor(seg1$lFFA, seg1$lamygdala, method = "pearson", use = "complete.obs"),
             cor(seg2$lFFA, seg2$lamygdala, method = "pearson", use = "complete.obs")), na.rm = TRUE)
    }),
    fx_lFFA_ramygdala = map_dbl(data, ~ {
      seg1 <- filter(.x, time >= 0 & time <= 81)
      seg2 <- filter(.x, time >= 86 & time <= 167)
      mean(c(cor(seg1$lFFA, seg1$ramygdala, method = "pearson", use = "complete.obs"),
             cor(seg2$lFFA, seg2$ramygdala, method = "pearson", use = "complete.obs")), na.rm = TRUE)
    }),
    fx_lFFA_lSTS = map_dbl(data, ~ {
      seg1 <- filter(.x, time >= 0 & time <= 81)
      seg2 <- filter(.x, time >= 86 & time <= 167)
      mean(c(cor(seg1$lFFA, seg1$lSTS, method = "pearson", use = "complete.obs"),
             cor(seg2$lFFA, seg2$lSTS, method = "pearson", use = "complete.obs")), na.rm = TRUE)
    }),
    fx_lFFA_rSTS = map_dbl(data, ~ {
      seg1 <- filter(.x, time >= 0 & time <= 81)
      seg2 <- filter(.x, time >= 86 & time <= 167)
      mean(c(cor(seg1$lFFA, seg1$rSTS, method = "pearson", use = "complete.obs"),
             cor(seg2$lFFA, seg2$rSTS, method = "pearson", use = "complete.obs")), na.rm = TRUE)
    }),
    fx_lMMPFC_rMMPFC = map_dbl(data, ~ {
      seg1 <- filter(.x, time >= 0 & time <= 81)
      seg2 <- filter(.x, time >= 86 & time <= 167)
      mean(c(cor(seg1$lMMPFC, seg1$rMMPFC, method = "pearson", use = "complete.obs"),
             cor(seg2$lMMPFC, seg2$rMMPFC, method = "pearson", use = "complete.obs")), na.rm = TRUE)
    }),
    fx_lMMPFC_lamygdala = map_dbl(data, ~ {
      seg1 <- filter(.x, time >= 0 & time <= 81)
      seg2 <- filter(.x, time >= 86 & time <= 167)
      mean(c(cor(seg1$lMMPFC, seg1$lamygdala, method = "pearson", use = "complete.obs"),
             cor(seg2$lMMPFC, seg2$lamygdala, method = "pearson", use = "complete.obs")), na.rm = TRUE)
    }),
    fx_lMMPFC_ramygdala = map_dbl(data, ~ {
      seg1 <- filter(.x, time >= 0 & time <= 81)
      seg2 <- filter(.x, time >= 86 & time <= 167)
      mean(c(cor(seg1$lMMPFC, seg1$ramygdala, method = "pearson", use = "complete.obs"),
             cor(seg2$lMMPFC, seg2$ramygdala, method = "pearson", use = "complete.obs")), na.rm = TRUE)
    }),
    fx_lMMPFC_lSTS = map_dbl(data, ~ {
      seg1 <- filter(.x, time >= 0 & time <= 81)
      seg2 <- filter(.x, time >= 86 & time <= 167)
      mean(c(cor(seg1$lMMPFC, seg1$lSTS, method = "pearson", use = "complete.obs"),
             cor(seg2$lMMPFC, seg2$lSTS, method = "pearson", use = "complete.obs")), na.rm = TRUE)
    }),
    fx_lMMPFC_rSTS = map_dbl(data, ~ {
      seg1 <- filter(.x, time >= 0 & time <= 81)
      seg2 <- filter(.x, time >= 86 & time <= 167)
      mean(c(cor(seg1$lMMPFC, seg1$rSTS, method = "pearson", use = "complete.obs"),
             cor(seg2$lMMPFC, seg2$rSTS, method = "pearson", use = "complete.obs")), na.rm = TRUE)
    }),
    fx_rMMPFC_lamygdala = map_dbl(data, ~ {
      seg1 <- filter(.x, time >= 0 & time <= 81)
      seg2 <- filter(.x, time >= 86 & time <= 167)
      mean(c(cor(seg1$rMMPFC, seg1$lamygdala, method = "pearson", use = "complete.obs"),
             cor(seg2$rMMPFC, seg2$lamygdala, method = "pearson", use = "complete.obs")), na.rm = TRUE)
    }),
    fx_rMMPFC_ramygdala = map_dbl(data, ~ {
      seg1 <- filter(.x, time >= 0 & time <= 81)
      seg2 <- filter(.x, time >= 86 & time <= 167)
      mean(c(cor(seg1$rMMPFC, seg1$ramygdala, method = "pearson", use = "complete.obs"),
             cor(seg2$rMMPFC, seg2$ramygdala, method = "pearson", use = "complete.obs")), na.rm = TRUE)
    }),
    fx_rMMPFC_lSTS = map_dbl(data, ~ {
      seg1 <- filter(.x, time >= 0 & time <= 81)
      seg2 <- filter(.x, time >= 86 & time <= 167)
      mean(c(cor(seg1$rMMPFC, seg1$lSTS, method = "pearson", use = "complete.obs"),
             cor(seg2$rMMPFC, seg2$lSTS, method = "pearson", use = "complete.obs")), na.rm = TRUE)
    }),
    fx_rMMPFC_rSTS = map_dbl(data, ~ {
      seg1 <- filter(.x, time >= 0 & time <= 81)
      seg2 <- filter(.x, time >= 86 & time <= 167)
      mean(c(cor(seg1$rMMPFC, seg1$rSTS, method = "pearson", use = "complete.obs"),
             cor(seg2$rMMPFC, seg2$rSTS, method = "pearson", use = "complete.obs")), na.rm = TRUE)
    }),
    fx_lamygdala_ramygdala = map_dbl(data, ~ cor(.x$lamygdala, .x$ramygdala, method = "pearson", use = "complete.obs")),
    fx_lamygdala_lSTS = map_dbl(data, ~ {
      seg1 <- filter(.x, time >= 0 & time <= 81)
      seg2 <- filter(.x, time >= 86 & time <= 167)
      mean(c(cor(seg1$lamygdala, seg1$lSTS, method = "pearson", use = "complete.obs"),
             cor(seg2$lamygdala, seg2$lSTS, method = "pearson", use = "complete.obs")), na.rm = TRUE)
    }),
    fx_lamygdala_rSTS = map_dbl(data, ~ {
      seg1 <- filter(.x, time >= 0 & time <= 81)
      seg2 <- filter(.x, time >= 86 & time <= 167)
      mean(c(cor(seg1$lamygdala, seg1$rSTS, method = "pearson", use = "complete.obs"),
             cor(seg2$lamygdala, seg2$rSTS, method = "pearson", use = "complete.obs")), na.rm = TRUE)
    }),
    fx_ramygdala_lSTS = map_dbl(data, ~ {
      seg1 <- filter(.x, time >= 0 & time <= 81)
      seg2 <- filter(.x, time >= 86 & time <= 167)
      mean(c(cor(seg1$ramygdala, seg1$lSTS, method = "pearson", use = "complete.obs"),
             cor(seg2$ramygdala, seg2$lSTS, method = "pearson", use = "complete.obs")), na.rm = TRUE)
    }),
    fx_ramygdala_rSTS = map_dbl(data, ~ {
      seg1 <- filter(.x, time >= 0 & time <= 81)
      seg2 <- filter(.x, time >= 86 & time <= 167)
      mean(c(cor(seg1$ramygdala, seg1$rSTS, method = "pearson", use = "complete.obs"),
             cor(seg2$ramygdala, seg2$rSTS, method = "pearson", use = "complete.obs")), na.rm = TRUE)
    }),
    fx_lSTS_rSTS = map_dbl(data, ~ {
      seg1 <- filter(.x, time >= 0 & time <= 81)
      seg2 <- filter(.x, time >= 86 & time <= 167)
      mean(c(cor(seg1$lSTS, seg1$rSTS, method = "pearson", use = "complete.obs"),
             cor(seg2$lSTS, seg2$rSTS, method = "pearson", use = "complete.obs")), na.rm = TRUE)
    }),
  ) %>%
  select(ID, starts_with("fx_"))

## Calculate z-scores 

### Define the columns to process

columns_to_process <- c("fx_rFFA_lFFA", "fx_rFFA_lMMPFC", "fx_rFFA_rMMPFC", "fx_rFFA_ramygdala", "fx_rFFA_lamygdala","fx_rFFA_lSTS", "fx_rFFA_rSTS",
                        "fx_lFFA_lMMPFC", "fx_lFFA_rMMPFC", "fx_lFFA_ramygdala", "fx_lFFA_lamygdala", "fx_lFFA_lSTS", "fx_lFFA_rSTS",
                        "fx_lMMPFC_rMMPFC", "fx_lMMPFC_lamygdala", "fx_lMMPFC_ramygdala", "fx_lMMPFC_lSTS", "fx_lMMPFC_rSTS", 
                        "fx_rMMPFC_lamygdala", "fx_rMMPFC_ramygdala", "fx_rMMPFC_lSTS", "fx_rMMPFC_rSTS",
                        "fx_lamygdala_ramygdala", "fx_lamygdala_lSTS", "fx_lamygdala_rSTS", "fx_ramygdala_lSTS", "fx_ramygdala_rSTS", "fx_lSTS_rSTS")

### Loop through the columns

for (column in columns_to_process) {
  ### Calculate mean and standard deviation for the current column
  mean_col <- mean(sample_fx[[column]], na.rm = TRUE)
  sd_col <- sd(sample_fx[[column]], na.rm = TRUE)
  
  #### Compute z-scores and store them in a new column
  zscore_column <- paste0("zscored_", column)
  sample_fx[[zscore_column]] <- (sample_fx[[column]] - mean_col) / sd_col
}
sample_fx <- sample_fx %>% select(contains(c("ID", "zscored")))

## Children 

child_fx <- sample_fx %>% 
  filter(ID %in% child_list)

## Adults

adult_fx <- sample_fx %>% 
  filter(ID %in% adult_list)

```


## Section IV: Lateralisation index (LI)

### Read data containing voxel-wise response magnitudes to the face-scene contrast

```{r}

# Read CSV file

facescene_contrast <- read.csv(here("raw_data/facescene_contrast", "events_compiled_stats.csv"), header = TRUE, dec = ".", sep = ",")

# Change column names and filter

colnames(facescene_contrast) <- c("ID", "task", "run", "contrast", "mask", "voxel_index", "t.stat", "z.stat")
facescene_contrast <- facescene_contrast[, c("ID", "mask", "voxel_index", "t.stat")]

# Remove the word "sub-pixar" and trim extra whitespace

facescene_contrast$ID <- gsub("[sub-pixar-]", "", facescene_contrast$ID)
facescene_contrast$ID <- trimws(facescene_contrast$ID)

# Change the name of the flipped rFFA ROI to left FFA

facescene_contrast <- facescene_contrast %>%
  mutate(mask = if_else(mask == "flipped_rFFA", "lFFA", mask))

facescene_contrast <- facescene_contrast %>%
  filter(ID %in% child_list)

```

### Threshold p<0.001

#### Assign p-values and flag significant voxels per hemisphere and participant.

```{r}

child_LI_0.001 <- facescene_contrast %>%
  rowwise() %>%
  mutate(
    significant = t.stat > 3.10  # flag voxels with t-stat > 3.10
  ) %>%
  ungroup()  # return to regular data frame

```

#### Calculate lateralisation index from significant voxels at threshold p<0.001

```{r}

# Calculate the number of significant voxels in left and right FFA per subject

child_LI_0.001 <- child_LI_0.001 %>%
  group_by(ID, mask) %>%
  summarise(
    significant_voxels = sum(significant, na.rm = TRUE), 
    .groups = "drop"
  )

# Exclude participants with less than 20 voxels in the left and right masks

child_LI_0.001 <- child_LI_0.001 %>%
  group_by(ID, mask) %>%
  summarise(significant_voxels = sum(significant_voxels, na.rm = TRUE), .groups = "drop") %>%
  pivot_wider(
    names_from = mask,
    values_from = significant_voxels,
    values_fill = 0
  ) %>%
  mutate(
    total_voxels = lFFA + rFFA,
    to_include  = if_else(total_voxels > 20, "yes", "no")
  )

child_LI_0.001 %>%
  filter(to_include == "yes") %>%
  count()

```

Cannot run analyses with LI calculated at t-stat>3.10, since only 9 subjects meet inclusion criteria (more than 20 significant voxels across hemispheres).

### Threshold p<0.01

#### Assign p-values and flag significant voxels per hemisphere and participant.

```{r}

child_LI_0.01 <- facescene_contrast %>%
  rowwise() %>%
  mutate(
    significant = t.stat > 2.33  # flag voxels with t-stat > 2.33
  ) %>%
  ungroup()  # return to regular data frame

```

#### Calculate lateralisation index from significant voxels at threshold p<0.01

```{r}

# Calculate the number of significant voxels in left and right FFA per subject

child_LI_0.01 <- child_LI_0.01 %>%
  group_by(ID, mask) %>%
  summarise(
    significant_voxels = sum(significant, na.rm = TRUE), 
    .groups = "drop"
  )

# Exclude participants with less than 20 voxels in the left and right masks

child_LI_0.01 <- child_LI_0.01 %>%
  group_by(ID, mask) %>%
  summarise(significant_voxels = sum(significant_voxels, na.rm = TRUE), .groups = "drop") %>%
  pivot_wider(
    names_from = mask,
    values_from = significant_voxels,
    values_fill = 0
  ) %>%
  mutate(
    total_voxels = lFFA + rFFA,
    to_include  = if_else(total_voxels > 20, "yes", "no")
  )

child_LI_0.01 %>%
  filter(to_include == "yes") %>%
  count()

```

Cannot run analyses with LI calculated at t-stat>2.33, since only 44 subjects meet inclusion criteria (more than 20 significant voxels across hemispheres).

Lateralisation index is instead calculated using p < 0.05 and p < 0.1.

### Threshold p<0.05 (non-preregistered)

#### Assign p-values and flag significant voxels per hemisphere and participant.

```{r}

child_LI_0.05 <- facescene_contrast %>%
  rowwise() %>%
  mutate(
    significant = t.stat > 1.645  # flag voxels with t-stat > 1.645
  ) %>%
  ungroup()  # return to regular data frame

```

#### Calculate lateralisation index from significant voxels at threshold p<0.05

```{r}

# Calculate the number of significant voxels in left and right FFA per subject

child_LI_0.05 <- child_LI_0.05 %>%
  group_by(ID, mask) %>%
  summarise(
    significant_voxels = sum(significant, na.rm = TRUE), 
    .groups = "drop"
  )

# Exclude participants with less than 20 voxels in the left and right masks

child_LI_0.05 <- child_LI_0.05 %>%
  group_by(ID, mask) %>%
  summarise(significant_voxels = sum(significant_voxels, na.rm = TRUE), .groups = "drop") %>%
  pivot_wider(
    names_from = mask,
    values_from = significant_voxels,
    values_fill = 0
  ) %>%
  mutate(
    total_voxels = lFFA + rFFA,
    to_include  = if_else(total_voxels > 20, "yes", "no")
  )

child_LI_0.05 %>%
  filter(to_include == "yes") %>%
  count()

# Calculate LI for included participants

child_LI_0.05 <- child_LI_0.05 %>%
mutate(
  lateralisation_index_0.05 = if_else(
    to_include == "yes",
    (lFFA - rFFA) / (lFFA + rFFA),
    NA_real_
  )
) %>%
  select(ID, lateralisation_index_0.05)

```

### Threshold p<0.10 (non-preregistered)

#### Assign p-values and flag significant voxels per hemisphere and participant.

```{r}

child_LI_0.1 <- facescene_contrast %>%
  rowwise() %>%
  mutate(
    significant = t.stat > 1.289  # flag voxels with t-stat > 1.289
  ) %>%
  ungroup()  # return to regular data frame

```

#### Calculate lateralisation index from significant voxels at threshold p<0.10

```{r}

# Calculate the number of significant voxels in left and right FFA per subject

child_LI_0.1 <- child_LI_0.1 %>%
  group_by(ID, mask) %>%
  summarise(
    significant_voxels = sum(significant, na.rm = TRUE), 
    .groups = "drop"
  )

# Exclude participants with less than 20 voxels in the left and right masks

child_LI_0.1 <- child_LI_0.1 %>%
  group_by(ID, mask) %>%
  summarise(significant_voxels = sum(significant_voxels, na.rm = TRUE), .groups = "drop") %>%
  pivot_wider(
    names_from = mask,
    values_from = significant_voxels,
    values_fill = 0
  ) %>%
  mutate(
    total_voxels = lFFA + rFFA,
    to_include  = if_else(total_voxels > 20, "yes", "no")
  )

child_LI_0.1 %>%
  filter(to_include == "yes") %>%
  count()

# Calculate LI for included participants

child_LI_0.1 <- child_LI_0.1 %>%
  mutate(
    lateralisation_index_0.1 = if_else(
      to_include == "yes",
      (lFFA - rFFA) / (lFFA + rFFA),
      NA_real_
    )
  ) %>%
  select(ID, lateralisation_index_0.1)

```


## Section V: Combine all children dependent variables into one spreadsheet and save files

```{r}

data_frames <- list(
  child_fm,  child_eventsmagnitude,
  child_fx,  child_LI_0.05, child_LI_0.1
)
child_MRIvariables <- Reduce(function(x, y) merge(x, y, by = "ID"), data_frames)
write.csv(child_MRIvariables, here("processed_data", "child_MRIvariables.csv"), row.names = FALSE)

```


```{r}

markdownToHTML("FRIC_MRIvariables.Rmd", output = "FRIC_MRIvariables.html")

```

