---
title: "BaselineCharacteristics"
author: "LJS"
date: "2025-05-12"
output: html_document
---


#Libraries 

```{r setup, include=FALSE}

library("rlang") #toolbox
library("readr") #toolbox
library("dplyr") #data manipulation
library("here") #toolbox
library("tidyverse") #data manipulation
library("tidytext") #data manipulation
library("knitr") #rmarkdown
library("htmltools") #rmarkdown
library("markdown") #rmarkdown
library("httpuv") #rmarkdown
library("NCmisc") #toolbox
library("stringr") #data manipulation
library("vtable") #summary tables
library("gtsummary") #summary tables
library("patchwork") #combine plots

```


# Face Responses in Childhood (FRIC) project

This script reports demographic and motion characteristics of final sample.

Structure:
- Section I: Read and tidy up data
- Section II: Demographic characteristics
- Section III: Correlation between motion and age


## Section I: Read and tidy up data

```{r}

# Covariates

participants <- read_tsv(here("raw_data/covariates", "participants.tsv"), col_names=TRUE)
colnames(participants)[which(names(participants) == "participant_id")] <- "ID"

## Remove the word "pixar" and trim extra whitespace

participants$ID <- gsub("[sub-pixar-]","", participants$ID)
participants$ID <- trimws(participants$ID)

## Create child or adult lists

adult_list <- row.names(participants)[which(participants[["Child_Adult"]] == "adult")]
child_MRIvariables <- read_csv(here("processed_data", "child_MRIvariables.csv"), col_names=TRUE)
child_list <- child_MRIvariables$ID
participants_list <- c(adult_list, child_list)

## Final sample

participants_filtered <- participants %>%
  filter(ID %in% participants_list)

# Add motion to final sample covariates

motion <- read_tsv(here("raw_data/motion", "outlier_info.tsv"), col_names=TRUE)
colnames(motion)[which(names(motion) == "subject")] <- "ID"

## Remove the word "pixar" and trim extra whitespace

motion$ID <- gsub("[sub-pixar-]","", motion$ID)
motion$ID <- trimws(motion$ID)
participants_filtered <- merge(participants_filtered, motion, by="ID")

# Ensure variables are treated as numeric

participants_filtered$ID <- as.factor(participants_filtered$ID)
participants_filtered$Age <- as.numeric(participants_filtered$Age)
participants_filtered$MeanFD <- as.numeric(participants_filtered$MeanFD)
participants_filtered$Gender <- as.factor(participants_filtered$Gender)

# Create IQ variable

participants_filtered[participants_filtered == "n/a"] <- NA
participants_filtered$raw_IQ <- coalesce(participants_filtered$"WPPSI BD raw", participants_filtered$"KBIT_raw")
participants_filtered$raw_IQ <- as.numeric(participants_filtered$raw_IQ)
participants_filtered$scaled_IQ <- coalesce(participants_filtered$"WPPSI BD scaled", participants_filtered$"KBIT_standard")
participants_filtered$scaled_IQ <- as.numeric(participants_filtered$scaled_IQ)

```


## Section II: Demographic characteristics

### General sample

#### Number of participants per age group

```{r}

# Create a frequency table for the 'AgeGroup' column

age_group_frequency <- table(participants_filtered$AgeGroup)

# Print the frequency table

print(age_group_frequency)

```

#### Check data distribution for reporting

```{r}

shapiro.test(participants_filtered$Age)
hist(participants_filtered$Age) 
shapiro.test(participants_filtered$MeanFD)
hist(participants_filtered$MeanFD) 
shapiro.test(participants_filtered$raw_IQ)
hist(participants_filtered$raw_IQ) 
shapiro.test(participants_filtered$scaled_IQ)
hist(participants_filtered$scaled_IQ) 

```

#### Create table

```{r}

# Filter child participants

children_filtered <- participants_filtered %>%
  filter(ID %in% child_list)

targetdata <- children_filtered[,c(2,3,5,6,24, 29, 30)]
table_dem <- tbl_summary(
  data      = targetdata,
  by        = AgeGroup,
  statistic = list(
    c("Age", "MeanFD", "raw_IQ", "scaled_IQ") ~ "{median} ({min}-{max}; {mean} ({sd}))"
  ),
  digits    = all_continuous() ~ 2,
  missing   = "no",               # hide missing row entirely
  include   = everything()
)
table_dem

```

#### Correlation between motion and metrics

```{r}

# Function to create formatted correlation text

create_motion_text <- function(variable1, variable2, label) {
  
  cor_result <- cor.test(
    children_filtered[[variable1]],
    children_filtered[[variable2]],
    method = "spearman",
    use = "complete.obs"
  )
  
  n <- sum(
    complete.cases(
      children_filtered[[variable1]],
      children_filtered[[variable2]]
    )
  )
  
  rho <- round(cor_result$estimate, 2)
  
  p <- if (cor_result$p.value < 0.001) {
    format(cor_result$p.value, scientific = TRUE, digits = 4)
  } else {
    sprintf("%.3f", cor_result$p.value)
  }
  
  df <- n - 2
  
  paste0(
    label, " was not correlated with age in children ",
    "(Spearman correlation test (n = ", n, "): ",
    "r_s(", df, ") = ", rho, ", p = ", p, ")."
  )
}

# Create footnote text for both metrics

footnote_fd_age <- create_motion_text("Age", "MeanFD", "Mean FD and age")
footnote_dvars_age <- create_motion_text("Age", "MeanDVARS", "Mean DVARS and age")
footnote_fd_IQ <- create_motion_text("scaled_IQ", "MeanFD", "Mean FD and standard IQ")


# Combine into one footnote

footnote_text <- paste(footnote_fd_age, footnote_dvars_age, footnote_fd_IQ)

# Create footnote text, add and save table

## Convert gtsummary table to tibble

table_dem <- as_tibble(table_dem)

colnames(table_dem) <- c(
  "Characteristic",
  "Adults (N=33)",
  "Children (N=117)"
)

## Add footnote as final row
table_dem <- bind_rows(
  table_dem,
  tibble(
    Characteristic = footnote_text,
    `Adults (N=33)` = NA,
    `Children (N=117)` = NA
  )
)

print(table_dem)

## Save
write.csv(
  table_dem,
  here("results/demographics", "Sample_characteristics.csv"),
  row.names = FALSE
)

## Visualisation of MeanFD and MeanDVARS by age

### Create custom colours 

custom_colours <- c("#D34835", "#DDA86A", "#83AC66", "#87BACF", "#6989F3", "#652975")

### Format data to plot

data_plot_FD <- children_filtered %>%
  filter(!is.na(MeanFD), !is.na(AgeGroup)) %>%
  group_by(AgeGroup) %>%
  summarise(
    mean_value = mean(MeanFD, na.rm = TRUE),
    se_value   = sd(MeanFD, na.rm = TRUE) / sqrt(n()),
    .groups = "drop"
  )

data_plot_DVARS <- children_filtered %>%
  filter(!is.na(MeanDVARS), !is.na(AgeGroup)) %>%
  group_by(AgeGroup) %>%
  summarise(
    mean_value = mean(MeanDVARS, na.rm = TRUE),
    se_value   = sd(MeanDVARS, na.rm = TRUE) / sqrt(n()),
    .groups = "drop"
  )

### General plotting function

generate_plot <- function(data, feature, subtitle, show_legend = TRUE, y_label = NULL, legend_pos = "bottom") {
  ggplot(data, aes(x = as.factor(AgeGroup), y = mean_value, fill = as.factor(AgeGroup))) +
    geom_bar(stat = "identity", position = "stack", width = 1, alpha = 1) +
    geom_errorbar(aes(ymin = mean_value - se_value, ymax = mean_value + se_value), linewidth = 1, width = 0) +
    geom_hline(yintercept = 0, linetype = "solid", size = 1, color = "black") +
    scale_fill_manual(values = custom_colours) +
    labs(
      title = subtitle,
      x = "",
      y = y_label,
      fill = "Age Group"
    ) +
    theme_classic() +
    theme(
      strip.text      = element_text(size = 14, face = "bold"),
      strip.background= element_blank(),
      legend.position = ifelse(show_legend, legend_pos, "right"),
      legend.text     = element_text(size = 16),
      legend.title    = element_text(size = 14, face = "bold"),
      axis.title      = element_text(size = 14, face = "bold"),
      axis.text       = element_text(size = 12),
      axis.title.x    = element_blank(),
      axis.text.x     = element_blank(),
      axis.ticks.x    = element_blank(),
      axis.line.x     = element_blank(),
      plot.title      = element_text(hjust = 0.5, size = 14, face = "bold"),
      axis.line.y     = element_line(size = 0.8, color = "black")
    )
}

## Generate plots with one reusable function

plot_FD <- generate_plot(data_plot_FD, "Mean FD", "", show_legend = TRUE, y_label = "Mean FD")
plot_DVARS <- generate_plot(data_plot_DVARS, "Mean DVARS", "", show_legend = TRUE, y_label = "Mean DVARS")

## Combine plots with a common centered title and shared legend

final_plot <- (plot_FD | plot_DVARS ) +  
  plot_layout(ncol = 2, guides = "collect") +
  plot_annotation(
    title = ""
  ) &
  theme(
    legend.position = "bottom",
    legend.text = element_text(size = 12),
    legend.title = element_text(size = 12),
    plot.title = element_text(size = 14, hjust = 0.5, face = "bold")
  )
print(final_plot)

### Save

ggsave(
  here("results/figures", "FD_DVARS_by_agegroup.png"),
  final_plot,
  width = 8,
  height = 4
)

```

### Lateralisation analyses samples

#### p<0.05

##### Tidy up data

```{r}

children_filtered <- participants_filtered %>%
  filter(ID %in% child_list) %>%
  left_join(
    child_MRIvariables %>%
      select(ID, lateralisation_index_0.05 = colnames(child_MRIvariables)[230]),
    by = "ID"
  ) %>%
  filter(!is.na(lateralisation_index_0.05))

```

##### Create table

```{r}

targetdata <- children_filtered[,c(2,5,24)]
table_dem <- tbl_summary(
  data      = targetdata,
  statistic = list(
    c("Age", "MeanFD") ~ "{mean} ({sd}); {median} ({min}, {max})"
  ),
  digits    = all_continuous() ~ 3,
  missing   = "no",               # hide missing row entirely
  include   = everything()
)
table_dem

```

##### Save table

```{r}

table_dem <- as_tibble(table_dem)
write.csv(table_dem, here("results/demographics", "Sample_characteristics_LI_0.05.csv"), row.names=FALSE)

```

#### p<0.10

##### Tidy up data

```{r}

children_filtered <- participants_filtered %>%
  filter(ID %in% child_list) %>%
  left_join(
    child_MRIvariables %>%
      select(ID, lateralisation_index_0.10 = colnames(child_MRIvariables)[231]),
    by = "ID"
  ) %>%
  filter(!is.na(lateralisation_index_0.10))

```

##### Create table

```{r}

targetdata <- children_filtered[,c(2,5,24)]
table_dem <- tbl_summary(
  data      = targetdata,
  statistic = list(
    c("Age", "MeanFD") ~ "{mean} ({sd}); {median} ({min}, {max})"
  ),
  digits    = all_continuous() ~ 3,
  missing   = "no",               # hide missing row entirely
  include   = everything()
)
table_dem

```

##### Save table

```{r}

table_dem <- as_tibble(table_dem)
write.csv(table_dem, here("results/demographics", "Sample_characteristics_LI_0.10.csv"), row.names=FALSE)

```


```{r}

markdownToHTML("FRIC_BaselineCharacteristics.Rmd",output ="FRIC_BaselineCharacteristics.html")

```

